### 2015-03-10 ms.tex
First commit: skeleton draft, preliminary abstract
Initial commit:
==============

Initial commit with skeleton draft and preliminary abstract

In ms.tex,

(*) Skeleton structure contains abstract, introduction, wide-field
effects in delay spectrum, MWA observations, results and summary

%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%% \documentclass[10pt,manuscript]{aastex}

%% preprint2 produces a double-column, single-spaced document:
\documentclass[preprint2,apjl,numberedappendix,twocolappendix,appendixfloats]{emulateapj}
%% \documentclass[preprint2,iop]{aastex}

%% \documentclass[preprint2,longabstract]{aastex}

%% \usepackage{ccaption}
%% \captionstyle{\raggedright}
\usepackage[caption=false]{subfig}
\usepackage{amsmath}
\usepackage{footnote}
\bibpunct{(}{)}{;}{a}{}{,} 
\captionsetup{belowskip=12pt,aboveskip=4pt}
\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\newcommand{\dif}{\mathrm{d}}
%% \renewcommand*{\thefootnote}{\fnsymbol{footnote}}

\def\nar{{New~A~Rev.}}          % New Astronomy Review
\def\pasa{{PASA}}               % Publications of the Astron. Soc. of Australia

%% \bibliographystyle{mn2e}
%% \bibliographystyle{apj}

\shorttitle{Wide--field Effects in EoR Power Spectra}
\shortauthors{Thyagarajan et~al.}

\def\ASU{\altaffilmark{1}}
\def\ASUtxt{\altaffiltext{1}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}}

\def\myemail{\altaffilmark{*}}
\def\myemailtxt{\altaffiltext{*}{e-mail: t\_nithyanandan@asu.edu}}

\def\UW{\altaffilmark{2}}
\def\UWtxt{\altaffiltext{2}{University of Washington, Department of Physics, Seattle, WA 98195, USA}}

\def\SKASA{\altaffilmark{3}}
\def\SKASAtxt{\altaffiltext{3}{Square Kilometre Array South Africa (SKA SA), Park Road, Pinelands 7405, South Africa}}

\def\RU{\altaffilmark{4}}
\def\RUtxt{\altaffiltext{4}{Department of Physics and Electronics, Rhodes University, Grahamstown 6140, South Africa}}

\def\CfA{\altaffilmark{5}}
\def\CfAtxt{\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}}

\def\ANU{\altaffilmark{6}}
\def\ANUtxt{\altaffiltext{6}{Australian National University, Research School of Astronomy and Astrophysics, Canberra, ACT 2611, Australia}}

\def\CAASTRO{\altaffilmark{7}}
\def\CAASTROtxt{\altaffiltext{7}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}}

\def\Haystack{\altaffilmark{8}}
\def\Haystacktxt{\altaffiltext{8}{MIT Haystack Observatory, Westford, MA 01886, USA}}

\def\MIT{\altaffilmark{9}}
\def\MITtxt{\altaffiltext{9}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}

\def\Curtin{\altaffilmark{10}}
\def\Curtintxt{\altaffiltext{10}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}

\def\Victoria{\altaffilmark{11}}
\def\Victoriatxt{\altaffiltext{11}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}

\def\UWisc{\altaffilmark{12}}
\def\UWisctxt{\altaffiltext{12}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}

\def\UMichigan{\altaffilmark{13}}
\def\UMichigantxt{\altaffiltext{13}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}}

\def\UMelbourne{\altaffilmark{14}}
\def\UMelbournetxt{\altaffiltext{14}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}

\def\USydney{\altaffilmark{15}}
\def\USydneytxt{\altaffiltext{15}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}

\def\CASS{\altaffilmark{16}}
\def\CASStxt{\altaffiltext{16}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}}

\def\Tata{\altaffilmark{17}}
\def\Tatatxt{\altaffiltext{17}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}}

\def\RRI{\altaffilmark{18}}
\def\RRItxt{\altaffiltext{18}{Raman Research Institute, Bangalore 560080, India}}

\def\NRAO{\altaffilmark{19}}
\def\NRAOtxt{\altaffiltext{19}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}

\def\UWA{\altaffilmark{20}}
\def\UWAtxt{\altaffiltext{20}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}}

%% \definenote[thanks][conversion=set 2]

\begin{document}

\title{Wide--Field Effects in Redshifted 21~cm Power Spectra}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU,
N.~Barry\UW,
A.~P.~Beardsley\UW,
G.~Bernardi\SKASA$^,$\RU$^,$\CfA,
F.~Briggs\ANU$^,$\CAASTRO,
R.~J.~Cappallo\Haystack, 
P.~Carroll\UW,
B.~E.~Corey\Haystack, 
% A.~A.~Deshpande\RRI, 
A.~de~Oliveira-Costa\MIT,
Joshua~S.~Dillon\MIT,
D.~Emrich\Curtin,
% B.~M.~Gaensler\USydney$^,$\CAASTRO, 
A.~Ewall-Wice\MIT,
L.~Feng\MIT,
R.~Goeke\MIT,
L.~J.~Greenhill\CfA,
B.~J.~Hazelton\UW, 
J.~N.~Hewitt\MIT,
N.~Hurley-Walker\Curtin,
M.~Johnston-Hollitt\Victoria,
D.~L.~Kaplan\UWisc, 
J.~C.~Kasper\UMichigan$^,$\CfA, 
Han-Seek Kim\UMelbourne$^,$\CAASTRO,
P.~Kittiwisit\ASU,
E.~Kratzenberg\Haystack, 
E.~Lenc\USydney$^,$\CAASTRO,
J.~Line\UMelbourne$^,$\CAASTRO,
A.~Loeb\CfA,
C.~J.~Lonsdale\Haystack, 
M.~J.~Lynch\Curtin, 
B.~McKinley\UMelbourne$^,$\CAASTRO,
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
A.~R.~Neben\MIT,
D.~Oberoi\Tata, 
A.~R.~Offringa\ANU$^,$\CAASTRO, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
Sourabh Paul\RRI,
B.~Pindor\UMelbourne$^,$\CAASTRO,
J.~C.~Pober\UW,
T.~Prabu\RRI, 
P.~Procopio\UMelbourne$^,$\CAASTRO,
J.~Riding\UMelbourne$^,$\CAASTRO,
A.~E.~E.~Rogers\Haystack, 
A.~Roshi\NRAO, 
N.~Udaya~Shankar\RRI, 
Shiv~K.~Sethi\RRI,
K.~S.~Srivani\RRI, 
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
I.~S.~Sullivan\UW,
M.~Tegmark\MIT,
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
C.~M.~Trott\Curtin$^,$\CAASTRO,
M.~Waterson\Curtin$^,$\ANU,
R.~B.~Wayth\Curtin$^,$\CAASTRO, 
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
C.~Wu\UWA,
J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
\UWtxt
\SKASAtxt
\RUtxt
\CfAtxt
\ANUtxt
\CAASTROtxt
\Haystacktxt
\MITtxt
\Curtintxt
\Victoriatxt
\UWisctxt
\UMichigantxt
\UMelbournetxt
\USydneytxt
\CASStxt
\Tatatxt
\RRItxt
\NRAOtxt
\UWAtxt
\myemailtxt

%% \email{t\_nithyanandan@rri.res.in}

%% \clearpage

\begin{abstract}

Foreground emission is currently the primary limitation to detection of redshifted H{\sc i} emission from the epoch of reionization. Modern radio telescopes that target this cosmological signal are typically wide--field instruments. Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide--field measurements imprint a characteristic {\it pitchfork}--shaped signature in this Fourier domain. It is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal. With MWA data sensitivity improved by coherently averaging snapshots aligned in local sidereal time across different observing nights, we confirm the prediction from modeling at $>5\sigma$ level.

\end{abstract}

\keywords{cosmology: observations --- dark ages, reionization, first stars --- large-scale structure of universe --- methods: statistical --- radio continuum: galaxies --- techniques: interferometric}

\section{Introduction}\label{sec:intro}

\section{Wide--Field Effects in Delay Spectrum}\label{sec:wide-field}

\citet{thy15} have described in detail the effects of wide--field measurements as seen in the baseline--based delay spectra. The most prominent signature resembles a {\it pitchfork}--shape where the

Throughout the paper, we follow the conventions used in \citet{thy15}.

\section{The Murchison Widefield Array Observations}\label{sec:MWA}

\section{Results}\label{sec:results}

\section{Summary}\label{sec:summary}

\acknowledgments

This work was supported by the U. S. National Science Foundation (NSF) through award AST--1109257. DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST--1401708. JCP is supported by an NSF Astronomy and Astrophysics Fellowship under award AST-1302774. This work makes use of the Murchison Radio-astronomy Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site. Support for the MWA comes from the NSF (awards: AST-0457585, PHY-0835713, CAREER-0847753, and AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), the U.S. Air Force Office of Scientific Research (grant FA9550-0510247), and the Centre for All-sky Astrophysics (an Australian Research Council Centre of Excellence funded by grant CE110001020). Support is also provided by the Smithsonian Astrophysical Observatory, the MIT School of Science, the Raman Research Institute, the Australian National University, and the Victoria University of Wellington (via grant MED-E1799 from the New Zealand Ministry of Economic Development and an IBM Shared University Research Grant). The Australian Federal government provides additional support via the Commonwealth Scientific and Industrial Research Organisation (CSIRO), National Collaborative Research Infrastructure Strategy, Education Investment Fund, and the Australia India Strategic Research Fund, and Astronomy Australia Limited, under contract to Curtin University. We acknowledge the iVEC Petabyte Data Store, the Initiative in Innovative Computing and the CUDA Center for Excellence sponsored by NVIDIA at Harvard University, and the International Centre for Radio Astronomy Research (ICRAR), a Joint Venture of Curtin University and The University of Western Australia, funded by the Western Australian State government.

% \par\bigskip
\bibliographystyle{apj}
\bibliography{eor}

\end{document}

### 2015-03-11 ms.tex
Add preliminary section on pitchfork overview
From d17d6b2:
============

In ms.tex,

(*) Add preliminary section 2 "Wide-field effects in delay spectrum"

@@
 
-\citet{thy15} have described in detail the effects of wide--field measurements as seen in the baseline--based delay spectra. The most prominent signature resembles a {\it pitchfork}--shape where the
+\citet{thy15} have described in detail the effects of wide--field measurements as seen in the delay spectra of interferometer {\it visibilities}.
+Here, we give a brief overview of the wide--field signature predicted therein.
 
-Throughout the paper, we follow the conventions used in \citet{thy15}.
+The delay spectrum for a baseline vector, $\boldsymbol{b}$, is given by \citep{par12a,par12b,thy13,thy15}: 
+\begin{align}
+  \tilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
+\end{align}
+with interferometer visibilities, $V_b(f)$, given by \citep{van34,zer38,tho01}:
+\begin{align} 
+  V_b(f) &= \iint\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,W_\textrm{i}(f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega \\
+         &= \iint\limits_\textrm{sky} \frac{A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)}{\sqrt{1-l^2-m^2}}\,W_\textrm{i}(f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif l\,\dif m,
+\end{align}
+where, $I(\hat{\boldsymbol{s}},f)$ and $A(\hat{\boldsymbol{s}},f)$ are the sky brightness and antenna's directional power pattern, respectively, as a function of frequency ($f$) and direction on the sky denoted by the unit vector $\hat{\boldsymbol{s}}\equiv (l,m,n)$, $W_\textrm{i}(f)$ denotes instrumental bandpass weights, $W(f)$ is a spectral weighting function that controls the transfer function in the delay transform, $\dif\Omega=(1-l^2-m^2)^{-1/2}\,\dif l\,\dif m$ is the solid angle element to which $\hat{\boldsymbol{s}}$ is the unit normal vector, and $c$ is the speed of light.
+$\tau=\boldsymbol{b}\cdot\hat{\boldsymbol{s}}/c$ is the geometric delay between antenna pairs measured relative to the zenith and provides a mapping to position on the sky.
+
+In wide--field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits.
+This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
+
+Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide--field effects results in a characteristic ``pitchfork'' signature in the delay spectrum.
+
+Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot presented in \citet{thy15}, the high level of thermal noise prevented a robust confirmation.
+In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.
 

### 2015-03-11 ms.tex
Add preliminary section 3 "MWA Observations"
From b8d7b84:
============

In ms.tex,

(*) Add preliminary section 3 "MWA Observations"

@@
 
+The MWA observations and data analysis used in this study are already described in \citet{thy15}.
+In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings.
+Hence, we select a subset of MWA snapshots each of duration 112~seconds obtained over different nights which are aligned to within 72~seconds of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hours with the MWA tile beam pointed at zenith.
+The database contains 14 snapshots satisfying these criteria.
+Two of these snapshots were found to contain amplitude and phase artifacts for a significant duration across different baselines.
+Hence, they have been excluded from our analysis.
+
+The delay spectra of the rest of the snapshots were verified to be coherent in their amplitudes and phases.
+These complex valued delay spectra from independent snapshots are averaged together to lower thermal fluctuations without losing coherence from foreground contributions.
+The results are discussed below.
+
 \section{Results}\label{sec:results}

### 2015-03-12 ms.tex
Add preliminary section 4 "Results"
From d121706:
============

In ms.tex,

(*) Add preliminary section 4 "Results"

In eor.bib,

(*) Update Offringa et al.(2015) reference

Update figures 1 and 2

@@
 S.~M.~Ord\Curtin$^,$\CAASTRO,
-Sourabh Paul\RRI,
+Sourabh~Paul\RRI,
 B.~Pindor\UMelbourne$^,$\CAASTRO,
@@
 It is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal.
-With MWA data sensitivity improved by coherently averaging snapshots aligned in local sidereal time across different observing nights, we confirm the prediction from modeling at $>5\sigma$ level.
+With MWA data sensitivity improved by coherently averaging snapshots aligned in local sidereal time across different observing nights, we confirm the prediction from modeling at $>10\sigma$ level.
 
@@
 
-The MWA observations and data analysis used in this study are already described in \citet{thy15}.
+The MWA instrument configuration, EoR observations, and data analysis used in this study are already described in \citet{thy15}.
 In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings.
@@
 \section{Results}\label{sec:results}
+
+Figure~\ref{fig:avg-fhd-delay-spectra} shows the delay spectra obtained by averaging LST aligned delay spectra from individual snapshots from different nights.
+The dynamic range (in power spectrum units) in the averaged data is $\gtrsim 10$ higher compared to that in the {\it zenith} snapshot used in \citet{thy15}, and is consistent with the improvement expected in averaging 12 independent snapshots.
+With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) has become $\gtrsim 10$ times more prominent.
+We also note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which were not seen earlier in the individual snapshots presented in \citet{thy15}, thus confirming effective lowering of thermal fluctuations.
+We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\linewidth]{multi_baseline_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
+\caption{Amplitudes of delay power spectra obtained by averaging 12 snapshots of LST aligned MWA data.
+The $x$--axis, denoted by $|\boldsymbol{b}|$ (and $k_\perp$), represents angular (and spatial) scales in the plane of the sky while the $y$--axis, shown in $\tau$ and $k_\parallel$, denotes the spatial scales along the line of sight.
+White dotted lines are the horizon delay limits.
+Power near the horizon limits caused by wide--field effects are prominent.
+Faint horizontal features at $\tau=\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz.
+\label{fig:avg-fhd-delay-spectra}}
+\end{figure}
+
+Figure~\ref{fig:3-baseline-comparison-delay-spectra} shows the amplitudes of averaged delay spectra on three selected baseline vectors oriented northward.
+Data and noiseless simulations (using foreground and instrument models described in \citet{thy15}) are shown in black and red respectively.
+The horizontal dotted black line denotes {\it rms} of thermal fluctuations estimated from data.
+The vertical dashed line denotes horizon delay limits, and the vertical dot--dashed lines denote delays at which the responses to coarse band edge flagging are expected.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\linewidth]{3_baseline_comparison_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
+\caption{Delay power spectra amplitudes on three antenna spacings oriented northward obtained by coherent averaging of 12 snapshots aligned in LST.
+The data and models are shown in black and red respectively.
+The antenna spacings are 83.5~m ({\it top}), 104.2~m ({\it middle}), and 171~m ({\it bottom}).
+The horizontal dotted line is the {\it rms} of thermal fluctuations.
+The vertical dashed lines denote the horizon delay limits.
+The vertical dot--dashed lines at $\tau=\pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz.
+The dynamic range has increased by a factor $\sim 10$ as a result of coherent averaging relative to that in \citet{thy15}.
+The peaks close to the horizon delay limits are distinctly visible at $\sim 10$--1000~$\sigma$ levels.
+Differences between model and data are primarily attributed to uncertainties in the foreground model and the MWA tile power pattern.
+\label{fig:3-baseline-comparison-delay-spectra}}
+\end{figure}
+
+The delay power spectra morphologies from data and modeling are remarkably similar even while ignoring any differences in the amplitude scales.
+We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in \citet{thy15}.
+
+We focus on the level of foreground power near the horizon limits in the data.
+Typically, the power near the negative horizon limit is seen with a signal--noise ratio (SNR) $\sim$~10--100, while that around the positive horizon limit is $\sim$~100--1000.
+The models of \citet{thy15} have noted that the foreground power near the horizon limits is due to the nature of wide--field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m.
+Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in \citet{thy15}.
 

### 2015-03-12 ms.tex
Add preliminary section 5 "Summary"
From aacb3ef:
============

In ms.tex,

(*) Add preliminary section 5 "Summary"
(*) Make minor changes to abstract

Git rename changelot.txt to changelog.txt

@@
 Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide--field measurements imprint a characteristic {\it pitchfork}--shaped signature in this Fourier domain.
-It is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal.
-With MWA data sensitivity improved by coherently averaging snapshots aligned in local sidereal time across different observing nights, we confirm the prediction from modeling at $>10\sigma$ level.
+This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal.
+With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal--noise ratio $>10$.
 
@@
 
+Fluctuations of redshifted H{\sc i} from the reionization epoch are extremely faint relative to the radio continuum emission from foreground objects.
+This poses perhaps the greatest challenge to EoR experiments and therefore merits a detailed characterization of foreground signatures in order to separate them from the desired signal.
+
+In a recent study, through the use of models for an all--sky foreground and the instrument, the role of wide--field nature of modern radio interferometric measurements, hitherto unpredicted, has emerged.
+It is referred to as the {\it pitchfork} signature in the delay spectral domain, and is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon.
+The latter is due to the highly non--linear mapping between geometric delays and subtended solid angles besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions.
+This feature could not be confirmed in individual MWA snapshot observations due to the high level of thermal fluctuations.
+
+By averaging 12 independent snapshots tightly aligned in LST from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the coherency of the observed {\it visibilities}.
+Foreground power in delay bins near the horizon is distinctly visible with a signal--noise ratio $>10$.
+In addition, there is a close resemblance in the morphologies of delay power spectra from data and models.
+Together, they allow us to make a robust confirmation of the nature of wide--field measurements in EoR experiments.
+
 \acknowledgments

### 2015-03-12 ms.tex
Add preliminary section 1 "Introduction"
From 85866d7:
============

In ms.tex,

(*) Add preliminary section 1 "Introduction"
(*) Make minor changes to "Rseults" section
(*) Make minor changes to "MWA Observations" section

@@
 
+The epoch of reionization (EoR) commenced following the formation of the first stars and galaxies.
+It is characterized by a period of non--linear growth of matter density perturbations and astrophysical evolution in the Universe's history.
+Detection of redshifted 21~cm radiation of H{\sc i} from this epoch is one of the most promising probes of the non--linear evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
+
+While sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H{\sc i} become operational, numerous pathfinders and precursors such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, and the planned Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA) have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14} and most of these are already operational.
+
+The primary challenge to detection of cosmological redshifted H{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}.
+Since the foregrounds and the signal have inherent differences in spatial isotropy and spectral smoothness \citep{mor04,mor06,bow09,liu11,par12b,dil13,pob13}, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,tro12,pob13,dil14,liu14a,liu14b,thy13,thy15}.
+
+A recent study by \citet{thy15} using instrument and all--sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide--field measurements, typical of most modern EoR experiments.
+This paper presents a follow--up analysis of that study.
+By using a larger volume of MWA data obtained independently over different nights pointed at the same region of sky, we confirm with high significance the presence of certain key characteristics (referred to as the {\it pitchfork} signature) of wide--field measurements predicted in the preceding study.
+
+\S\ref{sec:wide-field} gives an overview of the role of wide--field measurements in the delay spectral domain and the predicted {\it pitchfork} signature.
+In \S\ref{sec:MWA}, we describe the data analysis procedure used to improve the dynamic range of delay spectra of MWA data.
+We describe the results and confirm the presence of the predicted wide--field effects in \S\ref{sec:results}.
+\S\ref{sec:summary} summarizes our findings.
+
 \section{Wide--Field Effects in Delay Spectrum}\label{sec:wide-field}
@@
 
-Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide--field effects results in a characteristic ``pitchfork'' signature in the delay spectrum.
+Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide--field effects results in a characteristic {\it pitchfork} signature in the delay spectrum.
 
@@
 
-The MWA instrument configuration, EoR observations, and data analysis used in this study are already described in \citet{thy15}.
+The MWA instrument configuration, EoR observations, and data analysis used in this study are already described in \citet{thy15} and references therein.
 In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings.
@@
 
-We focus on the level of foreground power near the horizon limits in the data.
+We focus on the peaks near the horizon limits in the data.
 Typically, the power near the negative horizon limit is seen with a signal--noise ratio (SNR) $\sim$~10--100, while that around the positive horizon limit is $\sim$~100--1000.

### 2015-03-15 ms.tex
Modify figure 1, minor changes
From 25a1e5d:
============

Add new figure to git version control

In ms.tex,

(*) Modify figure 1
(*) Change text and caption accordingly
(*) Change double hyphens to single hyphens
(*) Make minor changes

@@
 
-\shorttitle{Wide--field Effects in EoR Power Spectra}
+\shorttitle{Wide-field Effects in EoR Power Spectra}
 \shortauthors{Thyagarajan et~al.}
@@
 
-\title{Wide--Field Effects in Redshifted 21~cm Power Spectra}
+\title{Wide-Field Effects in Redshifted 21~cm Power Spectra}
 
@@
 Foreground emission is currently the primary limitation to detection of redshifted H{\sc i} emission from the epoch of reionization.
-Modern radio telescopes that target this cosmological signal are typically wide--field instruments.
-Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide--field measurements imprint a characteristic {\it pitchfork}--shaped signature in this Fourier domain.
+Modern radio telescopes that target this cosmological signal are typically wide-field instruments.
+Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain.
 This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal.
-With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal--noise ratio $>10$.
+With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.
 
@@
 The epoch of reionization (EoR) commenced following the formation of the first stars and galaxies.
-It is characterized by a period of non--linear growth of matter density perturbations and astrophysical evolution in the Universe's history.
-Detection of redshifted 21~cm radiation of H{\sc i} from this epoch is one of the most promising probes of the non--linear evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
+It is characterized by a period of non-linear growth of matter density perturbations and astrophysical evolution in the Universe's history.
+Detection of redshifted 21~cm radiation of H{\sc i} from this epoch is one of the most promising probes of the non-linear evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
 
@@
 
-A recent study by \citet{thy15} using instrument and all--sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide--field measurements, typical of most modern EoR experiments.
-This paper presents a follow--up analysis of that study.
-By using a larger volume of MWA data obtained independently over different nights pointed at the same region of sky, we confirm with high significance the presence of certain key characteristics (referred to as the {\it pitchfork} signature) of wide--field measurements predicted in the preceding study.
+A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments.
+This paper presents a follow-up analysis of that study.
+By using a larger volume of MWA data obtained independently over different nights pointed at the same region of sky, we confirm with high significance the presence of certain key characteristics (referred to as the {\it pitchfork} signature) of wide-field measurements predicted in the preceding study.
 
-\S\ref{sec:wide-field} gives an overview of the role of wide--field measurements in the delay spectral domain and the predicted {\it pitchfork} signature.
+\S\ref{sec:wide-field} gives an overview of the role of wide-field measurements in the delay spectral domain and the predicted {\it pitchfork} signature.
 In \S\ref{sec:MWA}, we describe the data analysis procedure used to improve the dynamic range of delay spectra of MWA data.
-We describe the results and confirm the presence of the predicted wide--field effects in \S\ref{sec:results}.
+We describe the results and confirm the presence of the predicted wide-field effects in \S\ref{sec:results}.
 \S\ref{sec:summary} summarizes our findings.
 
-\section{Wide--Field Effects in Delay Spectrum}\label{sec:wide-field}
+\section{Wide-Field Effects in Delay Spectrum}\label{sec:wide-field}
 
-\citet{thy15} have described in detail the effects of wide--field measurements as seen in the delay spectra of interferometer {\it visibilities}.
-Here, we give a brief overview of the wide--field signature predicted therein.
+\citet{thy15} have described in detail the effects of wide-field measurements as seen in the delay spectra of interferometer {\it visibilities}.
+Here, we give a brief overview of the wide-field signature predicted therein.
 
@@
 
-In wide--field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits.
+In wide-field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits.
 This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
 
-Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide--field effects results in a characteristic {\it pitchfork} signature in the delay spectrum.
+Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide-field effects results in a characteristic {\it pitchfork} signature in the delay spectrum.
 
@@
 
-Figure~\ref{fig:avg-fhd-delay-spectra} shows the delay spectra obtained by averaging LST aligned delay spectra from individual snapshots from different nights.
-The dynamic range (in power spectrum units) in the averaged data is $\gtrsim 10$ higher compared to that in the {\it zenith} snapshot used in \citet{thy15}, and is consistent with the improvement expected in averaging 12 independent snapshots.
+Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling \citep{thy15} with no thermal noise added (bottom), for reference.
+The dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top) similar to the one used in \citet{thy15}, and is consistent with the improvement expected from averaging 12 independent snapshots.
 With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) has become $\gtrsim 10$ times more prominent.
-We also note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which were not seen earlier in the individual snapshots presented in \citet{thy15}, thus confirming effective lowering of thermal fluctuations.
+We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations.
 We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.
@@
 \centering
-\includegraphics[width=\linewidth]{multi_baseline_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
-\caption{Amplitudes of delay power spectra obtained by averaging 12 snapshots of LST aligned MWA data.
-The $x$--axis, denoted by $|\boldsymbol{b}|$ (and $k_\perp$), represents angular (and spatial) scales in the plane of the sky while the $y$--axis, shown in $\tau$ and $k_\parallel$, denotes the spatial scales along the line of sight.
+% \includegraphics[width=\linewidth]{multi_baseline_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
+\includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
+\caption{Delay power spectra obtained from a single snapshot ({\it top}), by averaging 12 snapshots of LST aligned MWA data ({\it middle}), and from modeling with no thermal noise added ({\it bottom}) shown for reference.
+The $x$-axis, denoted by $|\boldsymbol{b}|$ (and $k_\perp$), represents angular (and spatial) scales in the plane of the sky while the $y$-axis, shown in $\tau$ and $k_\parallel$, denotes the spatial scales along the line of sight.
 White dotted lines are the horizon delay limits.
-Power near the horizon limits caused by wide--field effects are prominent.
+Dynamic range in the delay power spectra of MWA data has increased by a factor $\sim 10$ after averaging (middle) relative to that in a single snapshot (top).
+Power near the horizon limits caused by wide-field effects are prominent.
 Faint horizontal features at $\tau=\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz.
-\label{fig:avg-fhd-delay-spectra}}
+\label{fig:delay-spectra}}
 \end{figure}
@@
 Figure~\ref{fig:3-baseline-comparison-delay-spectra} shows the amplitudes of averaged delay spectra on three selected baseline vectors oriented northward.
-Data and noiseless simulations (using foreground and instrument models described in \citet{thy15}) are shown in black and red respectively.
+Data and noiseless models are shown in black and red respectively.
 The horizontal dotted black line denotes {\it rms} of thermal fluctuations estimated from data.
-The vertical dashed line denotes horizon delay limits, and the vertical dot--dashed lines denote delays at which the responses to coarse band edge flagging are expected.
+The vertical dashed line denotes horizon delay limits, and the vertical dot-dashed lines denote delays at which the responses to coarse band edge flagging are expected.
 
@@
 \includegraphics[width=\linewidth]{3_baseline_comparison_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
-\caption{Delay power spectra amplitudes on three antenna spacings oriented northward obtained by coherent averaging of 12 snapshots aligned in LST.
-The data and models are shown in black and red respectively.
+\caption{Delay power spectra on three antenna spacings oriented northward, obtained by coherent averaging of 12 snapshots aligned in LST.
+The averaged data and models are shown in black and red respectively.
 The antenna spacings are 83.5~m ({\it top}), 104.2~m ({\it middle}), and 171~m ({\it bottom}).
@@
 The vertical dashed lines denote the horizon delay limits.
-The vertical dot--dashed lines at $\tau=\pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz.
-The dynamic range has increased by a factor $\sim 10$ as a result of coherent averaging relative to that in \citet{thy15}.
-The peaks close to the horizon delay limits are distinctly visible at $\sim 10$--1000~$\sigma$ levels.
+The vertical dot-dashed lines at $\tau=\pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz.
+The peaks close to the horizon delay limits are distinctly visible at $\sim 10$-1000~$\sigma$ levels.
 Differences between model and data are primarily attributed to uncertainties in the foreground model and the MWA tile power pattern.
@@
 We focus on the peaks near the horizon limits in the data.
-Typically, the power near the negative horizon limit is seen with a signal--noise ratio (SNR) $\sim$~10--100, while that around the positive horizon limit is $\sim$~100--1000.
-The models of \citet{thy15} have noted that the foreground power near the horizon limits is due to the nature of wide--field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m.
+Typically, the power near the negative horizon limit is seen with a signal-noise ratio (SNR) $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000.
+The models of \citet{thy15} have noted that the foreground power near the horizon limits is due to the nature of wide-field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m.
 Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in \citet{thy15}.
@@
 
-In a recent study, through the use of models for an all--sky foreground and the instrument, the role of wide--field nature of modern radio interferometric measurements, hitherto unpredicted, has emerged.
+In a recent study, through the use of models for an all-sky foreground and the instrument, the role of wide-field nature of modern radio interferometric measurements, hitherto unpredicted, has emerged.
 It is referred to as the {\it pitchfork} signature in the delay spectral domain, and is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon.
-The latter is due to the highly non--linear mapping between geometric delays and subtended solid angles besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions.
+The latter is due to the highly non-linear mapping between geometric delays and subtended solid angles besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions.
 This feature could not be confirmed in individual MWA snapshot observations due to the high level of thermal fluctuations.
 
-By averaging 12 independent snapshots tightly aligned in LST from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the coherency of the observed {\it visibilities}.
-Foreground power in delay bins near the horizon is distinctly visible with a signal--noise ratio $>10$.
+By averaging 12 independent snapshots tightly aligned in LST from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the coherency of foreground contributions in the observed {\it visibilities}.
+Foreground power in delay bins near the horizon is distinctly visible with a signal-noise ratio $>10$.
 In addition, there is a close resemblance in the morphologies of delay power spectra from data and models.
-Together, they allow us to make a robust confirmation of the nature of wide--field measurements in EoR experiments.
+Together, they allow us to make a robust confirmation of the nature of wide-field measurements in EoR experiments.
 
@@
 S.
-National Science Foundation (NSF) through award AST--1109257.
-DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST--1401708.
+National Science Foundation (NSF) through award AST-1109257.
+DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-1401708.
 JCP is supported by an NSF Astronomy and Astrophysics Fellowship under award AST-1302774.

### 2015-03-18 ms.tex
Minor changes to text and bibtex file
From 61bf009:
============

In ms.tex,

(*) Change HI to H I

In eor.bib,

(*) Update bibtex reference to Taylor et al.(1999)

@@
 
-Foreground emission is currently the primary limitation to detection of redshifted H{\sc i} emission from the epoch of reionization.
+Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization.
 Modern radio telescopes that target this cosmological signal are typically wide-field instruments.
 Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain.
-This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal.
+This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H~{\sc i} signal.
 With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.
@@
 It is characterized by a period of non-linear growth of matter density perturbations and astrophysical evolution in the Universe's history.
-Detection of redshifted 21~cm radiation of H{\sc i} from this epoch is one of the most promising probes of the non-linear evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
+Detection of redshifted 21~cm radiation of H~{\sc i} from this epoch is one of the most promising probes of the non-linear evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
 
-While sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H{\sc i} become operational, numerous pathfinders and precursors such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, and the planned Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA) have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14} and most of these are already operational.
+While sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} become operational, numerous pathfinders and precursors such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, and the planned Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA) have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14} and most of these are already operational.
 
-The primary challenge to detection of cosmological redshifted H{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}.
+The primary challenge to detection of cosmological redshifted H~{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}.
 Since the foregrounds and the signal have inherent differences in spatial isotropy and spectral smoothness \citep{mor04,mor06,bow09,liu11,par12b,dil13,pob13}, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,tro12,pob13,dil14,liu14a,liu14b,thy13,thy15}.
@@
 
-Fluctuations of redshifted H{\sc i} from the reionization epoch are extremely faint relative to the radio continuum emission from foreground objects.
+Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio continuum emission from foreground objects.
 This poses perhaps the greatest challenge to EoR experiments and therefore merits a detailed characterization of foreground signatures in order to separate them from the desired signal.

### 2015-03-18 ms.tex
Modify abstract, adjust all sections accordingly
From ac1c778:
============

In ms.tex,

(*) Modify abstract and adjust all sections accordingly

@@
 
-Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization.
+While probing H~{\sc i} in the epoch of reionization (EoR), through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature.
+By improving MWA data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$.
+This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions.
+
+% Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization.
+Modern radio telescopes that target this cosmological signal are typically wide-field instruments.
+Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain.
+This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H~{\sc i} signal.
+With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.
+
+% Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization.
 Modern radio telescopes that target this cosmological signal are typically wide-field instruments.
@@
 
-The primary challenge to detection of cosmological redshifted H~{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}.
+The primary challenge to detection of cosmological H~{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}.
 Since the foregrounds and the signal have inherent differences in spatial isotropy and spectral smoothness \citep{mor04,mor06,bow09,liu11,par12b,dil13,pob13}, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,tro12,pob13,dil14,liu14a,liu14b,thy13,thy15}.
 
-A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments.
+A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments and was noted to cause significant contamination in Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal.
 This paper presents a follow-up analysis of that study.
@@
 
-\S\ref{sec:wide-field} gives an overview of the role of wide-field measurements in the delay spectral domain and the predicted {\it pitchfork} signature.
-In \S\ref{sec:MWA}, we describe the data analysis procedure used to improve the dynamic range of delay spectra of MWA data.
-We describe the results and confirm the presence of the predicted wide-field effects in \S\ref{sec:results}.
+\S\ref{sec:wide-field} is an overview of the role of wide-field measurements in the delay spectral domain and the predicted {\it pitchfork} signature.
+\S\ref{sec:MWA} describes the analysis of MWA data used to improve the dynamic range of the delay spectra.
+\S\ref{sec:results} describes the results and confirms the presence of the predicted wide-field effects.
 \S\ref{sec:summary} summarizes our findings.
@@
 This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
-
 Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide-field effects results in a characteristic {\it pitchfork} signature in the delay spectrum.
 
-Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot presented in \citet{thy15}, the high level of thermal noise prevented a robust confirmation.
+Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal.
+Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot presented in their study, the high level of thermal noise prevented a robust confirmation.
 In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.
@@
 The latter is due to the highly non-linear mapping between geometric delays and subtended solid angles besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions.
-This feature could not be confirmed in individual MWA snapshot observations due to the high level of thermal fluctuations.
+Owing to its localization in delay spectral domain, it is a leading cause of contamination in Fourier modes most sensitive to the cosmological H~{\sc i} signal.
+This feature could not be confirmed in individual MWA snapshot due to the high level of thermal fluctuations.
 
-By averaging 12 independent snapshots tightly aligned in LST from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the coherency of foreground contributions in the observed {\it visibilities}.
+By averaging 12 independent LST-aligned snapshots from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the foreground contributions in the observed {\it visibilities} coherent.
 Foreground power in delay bins near the horizon is distinctly visible with a signal-noise ratio $>10$.
-In addition, there is a close resemblance in the morphologies of delay power spectra from data and models.
+Further, there is a close resemblance in the morphologies of delay power spectra from data and models.
 Together, they allow us to make a robust confirmation of the nature of wide-field measurements in EoR experiments.

### 2015-03-18 ms.tex
Reorganize list of authors and affiliations
From af1b5c4:
============

In ms.tex,

(*) Reorganize list of authors and affiliations
(*) Minor changes in text

@@
 
-\def\MIT{\altaffilmark{9}}
-\def\MITtxt{\altaffiltext{9}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}
+\def\RRI{\altaffilmark{9}}
+\def\RRItxt{\altaffiltext{9}{Raman Research Institute, Bangalore 560080, India}}
 
-\def\Curtin{\altaffilmark{10}}
-\def\Curtintxt{\altaffiltext{10}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}
+\def\MIT{\altaffilmark{10}}
+\def\MITtxt{\altaffiltext{10}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}
 
-\def\Victoria{\altaffilmark{11}}
-\def\Victoriatxt{\altaffiltext{11}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}
+\def\USydney{\altaffilmark{11}}
+\def\USydneytxt{\altaffiltext{11}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}
 
-\def\UWisc{\altaffilmark{12}}
-\def\UWisctxt{\altaffiltext{12}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}
+\def\Curtin{\altaffilmark{12}}
+\def\Curtintxt{\altaffiltext{12}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}
 
-\def\UMichigan{\altaffilmark{13}}
-\def\UMichigantxt{\altaffiltext{13}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}}
+\def\Victoria{\altaffilmark{13}}
+\def\Victoriatxt{\altaffiltext{13}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}
 
-\def\UMelbourne{\altaffilmark{14}}
-\def\UMelbournetxt{\altaffiltext{14}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}
+\def\UWisc{\altaffilmark{14}}
+\def\UWisctxt{\altaffiltext{14}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}
 
-\def\USydney{\altaffilmark{15}}
-\def\USydneytxt{\altaffiltext{15}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}
+\def\UMelbourne{\altaffilmark{15}}
+\def\UMelbournetxt{\altaffiltext{15}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}
 
@@
 
-\def\RRI{\altaffilmark{18}}
-\def\RRItxt{\altaffiltext{18}{Raman Research Institute, Bangalore 560080, India}}
+% \def\NRAO{\altaffilmark{19}}
+% \def\NRAOtxt{\altaffiltext{19}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}
 
-\def\NRAO{\altaffilmark{19}}
-\def\NRAOtxt{\altaffiltext{19}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}
+% \def\UMichigan{\altaffilmark{13}}
+% \def\UMichigantxt{\altaffiltext{13}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}}
 
-\def\UWA{\altaffilmark{20}}
-\def\UWAtxt{\altaffiltext{20}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}}
+% \def\UWA{\altaffilmark{20}}
+% \def\UWAtxt{\altaffiltext{20}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}}
 
@@
 
-\title{Wide-Field Effects in Redshifted 21~cm Power Spectra}
+\title{Wide-Field Signatures in Redshifted 21~cm Power Spectra}
 
@@
 P.~Carroll\UW,
-B.~E.~Corey\Haystack, 
-% A.~A.~Deshpande\RRI, 
+% B.~E.~Corey\Haystack, 
+A.~A.~Deshpande\RRI, 
 A.~de~Oliveira-Costa\MIT,
 Joshua~S.~Dillon\MIT,
-D.~Emrich\Curtin,
-% B.~M.~Gaensler\USydney$^,$\CAASTRO, 
+% D.~Emrich\Curtin,
+B.~M.~Gaensler\USydney$^,$\CAASTRO, 
 A.~Ewall-Wice\MIT,
 L.~Feng\MIT,
-R.~Goeke\MIT,
+% R.~Goeke\MIT,
 L.~J.~Greenhill\CfA,
@@
 D.~L.~Kaplan\UWisc, 
-J.~C.~Kasper\UMichigan$^,$\CfA, 
+% J.~C.~Kasper\UMichigan$^,$\CfA, 
 Han-Seek Kim\UMelbourne$^,$\CAASTRO,
 P.~Kittiwisit\ASU,
-E.~Kratzenberg\Haystack, 
+% E.~Kratzenberg\Haystack, 
 E.~Lenc\USydney$^,$\CAASTRO,
@@
 C.~J.~Lonsdale\Haystack, 
-M.~J.~Lynch\Curtin, 
+% M.~J.~Lynch\Curtin, 
 B.~McKinley\UMelbourne$^,$\CAASTRO,
@@
 J.~Riding\UMelbourne$^,$\CAASTRO,
-A.~E.~E.~Rogers\Haystack, 
-A.~Roshi\NRAO, 
+% A.~E.~E.~Rogers\Haystack, 
+% A.~Roshi\NRAO, 
 N.~Udaya~Shankar\RRI, 
@@
 C.~M.~Trott\Curtin$^,$\CAASTRO,
-M.~Waterson\Curtin$^,$\ANU,
+% M.~Waterson\Curtin$^,$\ANU,
 R.~B.~Wayth\Curtin$^,$\CAASTRO, 
 R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
-A.~R.~Whitney\Haystack, 
+% A.~R.~Whitney\Haystack, 
 A.~Williams\Curtin, 
 C.~L.~Williams\MIT,
-C.~Wu\UWA,
+% C.~Wu\UWA,
 J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
@@
 \Haystacktxt
+\RRItxt
 \MITtxt
+\USydneytxt
 \Curtintxt
@@
 \UWisctxt
-\UMichigantxt
 \UMelbournetxt
-\USydneytxt
 \CASStxt
 \Tatatxt
-\RRItxt
-\NRAOtxt
-\UWAtxt
 \myemailtxt
+% \NRAOtxt
+% \UMichigantxt
+% \UWAtxt
 
@@
 
-While probing H~{\sc i} in the epoch of reionization (EoR), through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature.
+While probing H~{\sc i} in the epoch of reionization (EoR) through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature.
 By improving MWA data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$.
@@
 
-Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio continuum emission from foreground objects.
-This poses perhaps the greatest challenge to EoR experiments and therefore merits a detailed characterization of foreground signatures in order to separate them from the desired signal.
+Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio foregrounds.
+This poses perhaps the greatest challenge to EoR experiments and thus merits a detailed characterization in order to separate them from the desired cosmological H~{\sc i} signal.
 
-In a recent study, through the use of models for an all-sky foreground and the instrument, the role of wide-field nature of modern radio interferometric measurements, hitherto unpredicted, has emerged.
-It is referred to as the {\it pitchfork} signature in the delay spectral domain, and is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon.
-The latter is due to the highly non-linear mapping between geometric delays and subtended solid angles besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions.
-Owing to its localization in delay spectral domain, it is a leading cause of contamination in Fourier modes most sensitive to the cosmological H~{\sc i} signal.
-This feature could not be confirmed in individual MWA snapshot due to the high level of thermal fluctuations.
+In a recent study, through the use of all-sky foreground and instrument models, the role of wide-field nature of radio interferometric measurements, hitherto unpredicted, has emerged.
+Referred to as the {\it pitchfork} signature in the delay spectral domain, it is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon.
+The latter is due to the highly nonlinear mapping between geometric delays and subtended solid angles, besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions.
+Owing to its localization in the delay domain, it is a leading cause of contamination in Fourier modes most sensitive to the EoR H~{\sc i} signal.
+This feature could not be confirmed in single MWA snapshots due to large thermal fluctuations.
 

### 2015-03-20 ms.tex
Add Lars Hernquist as author
From 6d0e4e6:
============

In ms.tex,

(*) Add Lars Hernquist as author
Change title, abstract, define delay power spectra
From 4b4904d:
============

In ms.tex,

(*) Change title
(*) Reorder sentences in abstract
(*) Add formula for delay power spectrum in section 2

@@
 
-\shorttitle{Wide-field Effects in EoR Power Spectra}
+\shorttitle{MWA Observations of Wide-field Effects in EoR Power Spectra}
 \shortauthors{Thyagarajan et~al.}
@@
 
-\title{Wide-Field Signatures in Redshifted 21~cm Power Spectra}
+\title{Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra
+using Murchison Widefield Array Observations}
 
@@
 B.~J.~Hazelton\UW,
+L.~Hernquist\CfA, 
 J.~N.~Hewitt\MIT,
@@
 % J.~C.~Kasper\UMichigan$^,$\CfA, 
-Han-Seek Kim\UMelbourne$^,$\CAASTRO,
+Han-Seek~Kim\UMelbourne$^,$\CAASTRO,
 P.~Kittiwisit\ASU,
@@
 While probing H~{\sc i} in the epoch of reionization (EoR) through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature.
+This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions.
 By improving MWA data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$.
-This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions.
 
@@
 $\tau=\boldsymbol{b}\cdot\hat{\boldsymbol{s}}/c$ is the geometric delay between antenna pairs measured relative to the zenith and provides a mapping to position on the sky.
+
+The delay power spectrum is defined as:
+\begin{align}\label{eqn:delay-power-spectrum}
+  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{A_\textrm{e}}{\lambda^2\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
+\end{align}
+with
+\begin{align}
+  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \\
+  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
+\end{align}
+where, $A_\textrm{e}$ is the effective area of the antenna, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $f_{21}$ is the rest frequency of the 21~cm radiation of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard cosmology terms.
+In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, and $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$.
+$P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2$(Mpc/$h$)$^3$.
 

### 2015-04-01 ms.tex
Remove author Bryan Gaensler, reorder affiliations
From 9ecd795:
============

In ms.tex,

(*) Remove Bryan Gaensler as co-author and reorder affiliations

@@
 
-\def\USydney{\altaffilmark{11}}
-\def\USydneytxt{\altaffiltext{11}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}
+\def\Curtin{\altaffilmark{11}}
+\def\Curtintxt{\altaffiltext{11}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}
 
-\def\Curtin{\altaffilmark{12}}
-\def\Curtintxt{\altaffiltext{12}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}
+\def\Victoria{\altaffilmark{12}}
+\def\Victoriatxt{\altaffiltext{12}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}
 
-\def\Victoria{\altaffilmark{13}}
-\def\Victoriatxt{\altaffiltext{13}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}
+\def\UWisc{\altaffilmark{13}}
+\def\UWisctxt{\altaffiltext{13}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}
 
-\def\UWisc{\altaffilmark{14}}
-\def\UWisctxt{\altaffiltext{14}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}
+\def\UMelbourne{\altaffilmark{14}}
+\def\UMelbournetxt{\altaffiltext{14}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}
 
-\def\UMelbourne{\altaffilmark{15}}
-\def\UMelbournetxt{\altaffiltext{15}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}
+\def\USydney{\altaffilmark{15}}
+\def\USydneytxt{\altaffiltext{15}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}
 
@@
 % D.~Emrich\Curtin,
-B.~M.~Gaensler\USydney$^,$\CAASTRO, 
+% B.~M.~Gaensler\USydney$^,$\CAASTRO, 
 A.~Ewall-Wice\MIT,
@@
 \MITtxt
-\USydneytxt
 \Curtintxt
@@
 \UMelbournetxt
+\USydneytxt
 \CASStxt

### 2015-04-01 ms.tex
Modify abstract
From ed26e72:
============

In ms.tex,

(*) Add a sentence at the beginning of the Abstract
Add more emphasis in the Abstract
From 097d9e5:
============

In ms.tex,

(*) Add emphasis on critical input for HERA and SKA in the Abstract

@@
 
+This analysis confirms recent predictions of certain key signatures in the delay spectra of wide-field radio interferometer measurements.
 While probing H~{\sc i} in the epoch of reionization (EoR) through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature.
 This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions.
-By improving MWA data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$.
-
-% Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization.
-Modern radio telescopes that target this cosmological signal are typically wide-field instruments.
-Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain.
-This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H~{\sc i} signal.
-With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.
-
-% Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization.
-Modern radio telescopes that target this cosmological signal are typically wide-field instruments.
-Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain.
-This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H~{\sc i} signal.
-With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.
+Thus it forms a critical input to design and analysis choices of future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array.
+By improving Murchison Widefield Array data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$.
 

### 2015-04-01 ms.tex
Add more emphasis in the Introduction
From 79304d5:
============

In ms.tex,

(*) Add emphasis on critical input for HERA and SKA in the Introduction

@@
 
-A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments and was noted to cause significant contamination in Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal.
+A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments.
+It was noted to cause significant contamination in Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal.
+It has been shown that a careful design of antenna aperture can significantly mitigate this contamination.
+And an optimal weighting of foreground-contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
+Thus, knowledge of such detailed foreground signatures becomes essential for design and analysis choices of future instruments such as HERA and SKA.
 This paper presents a follow-up analysis of that study.

### 2015-04-01 ms.tex
Mention best response from a dish antenna
From dbca120:
============

In ms.tex,

(*) Add a sentence on dish-shaped yielding best response in the section
on wide-field effects
(*) Minor change to a sentence in the Results section

@@
 \citet{thy15} have described in detail the effects of wide-field measurements as seen in the delay spectra of interferometer {\it visibilities}.
-Here, we give a brief overview of the wide-field signature predicted therein.
+Here, we list the relevant equations and give a brief overview of the wide-field signatures predicted therein.
 
@@
 Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal.
-Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot presented in their study, the high level of thermal noise prevented a robust confirmation.
+And a dish-shaped antenna is found to yield the most desirable response from a foreground contamination viewpoint.
+Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot used in their study, the high level of thermal noise prevented a robust confirmation.
 In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.
@@
 
-Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling \citep{thy15} with no thermal noise added (bottom), for reference.
+Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling \citep{thy15} with no thermal noise fluctuations (bottom), for reference.
 The dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top) similar to the one used in \citet{thy15}, and is consistent with the improvement expected from averaging 12 independent snapshots.

### 2015-04-01 ms.tex
Add more emphasis in the Summary section
From 14c8919:
============

In ms.tex,

(*) Modify Summary section to add more emphasis on the need to confirm
the pitchfork signature

@@
 
-The delay power spectra morphologies from data and modeling are remarkably similar even while ignoring any differences in the amplitude scales.
+The delay power spectra morphologies from data and modeling are remarkably similar despite some differences in the amplitude scales.
 We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in \citet{thy15}.
@@
 Owing to its localization in the delay domain, it is a leading cause of contamination in Fourier modes most sensitive to the EoR H~{\sc i} signal.
-This feature could not be confirmed in single MWA snapshots due to large thermal fluctuations.
 
-By averaging 12 independent LST-aligned snapshots from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the foreground contributions in the observed {\it visibilities} coherent.
+Knowledge of these characteristics weigh heavily on choices in instrument design like antenna aperture and in data analysis such as optimal weighting schemes for future instruments such as HERA and SKA.
+We report the first robust detection of the {\it pitchfork} signature (which could not be confirmed earlier in single MWA snapshots due to large thermal fluctuations) with a signal-noise ratio $>10$ made possible by coherent averaging of 12 independent LST-aligned snapshots from MWA observations.
+
+% By averaging 12 independent LST-aligned snapshots from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the foreground contributions in the observed {\it visibilities} coherent.
 Foreground power in delay bins near the horizon is distinctly visible with a signal-noise ratio $>10$.
 Further, there is a close resemblance in the morphologies of delay power spectra from data and models.
-Together, they allow us to make a robust confirmation of the nature of wide-field measurements in EoR experiments.
+Together, they allow us to make the first robust confirmation of the nature of wide-field measurements in EoR experiments.
 

### 2015-04-07 ms.tex
Modify Abstract
From e637668:
============

In ms.tex,

(*) Modify abstract

@@
 
-This analysis confirms recent predictions of certain key signatures in the delay spectra of wide-field radio interferometer measurements.
+Here we confirm a recently predicted and previously unknown foreground signature in the 3D power spectra of high redshift 21~cm measurements, wherein the interferometer is sensitive to large-scale structure on all baselines.
+This is due to the inherently chromatic nature of a wide-field instrument response and is characterized by enhanced power from foreground emission in Fourier modes adjacent to those considered to be most sensitive to the cosmological H~{\sc i} signal.
+Thus it is a critical input to design and analysis choices of future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array.
+The simulation which predicted this feature was recently validated against Murchison Widefield Array data but this key element was at or below the noise level.
+In this paper, we improve the Murchison Widefield Array data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, and provide the first confirmation of the prediction with a signal-noise ratio $>10$.
+
+% This analysis confirms recent predictions of certain key signatures in the delay spectra of wide-field radio interferometer measurements.
 While probing H~{\sc i} in the epoch of reionization (EoR) through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature.
@@
 It is characterized by a period of non-linear growth of matter density perturbations and astrophysical evolution in the Universe's history.
-Detection of redshifted 21~cm radiation of H~{\sc i} from this epoch is one of the most promising probes of the non-linear evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
+Detection of redshifted 21~cm radiation of H~{\sc i} from this epoch is one of the most promising probes of the evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
 

### 2015-04-07 ms.tex
Modify Introduction, add new references to eor.bib
From af1b5c4:
============

In ms.tex,

(*) Modify Introduction

In eor.bib,

(*) Add references to Di Matteo et al. 2004, Gnedin & Shaver 2004,
Santos et al. 2005, Wang et al. 2006, and Gleser et al. 2008.

@@
 
-While sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} become operational, numerous pathfinders and precursors such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, and the planned Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA) have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14} and most of these are already operational.
+Sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} are yet to become operational.
+In the meanwhile, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA) currently under construction will be much closer in its capability to detect and place definitive constraints on the reionization epoch relative to the SKA and far ahead of current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.
 
-The primary challenge to detection of cosmological H~{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}.
+% The primary challenge to detection of cosmological H~{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}.
 Since the foregrounds and the signal have inherent differences in spatial isotropy and spectral smoothness \citep{mor04,mor06,bow09,liu11,par12b,dil13,pob13}, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,tro12,pob13,dil14,liu14a,liu14b,thy13,thy15}.
 
-A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments.
+The primary challenge to detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker.
+But the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08,ali08,ber09,ber10,gho12}.
+Thus, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,par12b,tro12,pob13,dil13,dil14,liu14a,liu14b,thy13,thy15}.
+
+% A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments.
 It was noted to cause significant contamination in Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal.
@@
 By using a larger volume of MWA data obtained independently over different nights pointed at the same region of sky, we confirm with high significance the presence of certain key characteristics (referred to as the {\it pitchfork} signature) of wide-field measurements predicted in the preceding study.
+
+Our recent study \citep{thy15} used all-sky foreground and instrument models for the first time in order to simulate actual EoR experiments more accurately than previous studies.
+Surprisingly, we found that foreground emission outside the primary beam field of view caused the most significant contamination of the cosmological H~{\sc i} power spectrum Fourier modes that are considered most sensitive for detecting the signal in delay spectrum based analyses.
+This contamination is the result of the interplay between foreground emission, particularly diffuse Galactic emission, and the wide-field properties typical of EoR instruments.
+Our simulations predicted that delay spectra from the MWA and other experiments should exhibit a characteristic ``pitchfork'' appearance with local maxima near the horizon delay limits, in addition to at the primary lobe of the power pattern.
+
+A careful design of antenna aperture can significantly mitigate this contamination.
+Optimal weighting of foreground contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
+Thus, knowledge of such detailed foreground signatures becomes essential for design and analysis choices of future instruments such as HERA and SKA.
+
+In \citet{thy15}, we verified the general features of our simulations against MWA observations, but were unable to confirm the actual {\it pitchfork} prediction due to insufficient sensitivity in the small amount of data analyzed.
+Here, we use longer MWA integrations to confirm with high significance the presence of the key {\it pitchfork} characteristics of wide-field measurements predicted in the preceding study.
 

### 2015-04-08 ms.tex
Modify Section 2
From 7450235:
============

In ms.tex,

(*) Modify Section 2
(*) Minor rearrangement of citations in the Introduction

@@
 The primary challenge to detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker.
-But the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08,ali08,ber09,ber10,gho12}.
-Thus, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,par12b,tro12,pob13,dil13,dil14,liu14a,liu14b,thy13,thy15}.
+But the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08}.
+Thus, a detailed characterization of foreground emission has become essential \citep{ali08,bow09,liu09,ber09,ber10,dat10,liu11,gho12,mor12,par12b,tro12,pob13,dil13,dil14,liu14a,liu14b,thy13,thy15}.
 
@@
 
-In wide-field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits.
+The defining characteristics of the {\it pitchfork} signature are understood as follows.
+The steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits in wide-field measurements.
+This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
+
+Detailed modeling presented in our original study \citep{thy15} has indicated important implications for future instrument design and analysis algorithms:
+\begin{enumerate}
+\item positioned adjacent to the Fourier modes most sensitive to the cosmological signal, the {\it pitchfork} feature is a leading source of contamination in these modes, and 
+\item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity towards the horizon.
+\end{enumerate}
+
+In this paper, we confirm this key feature using deeper data from the MWA.
+
+% In wide-field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits.
 This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
@@
 
-Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal.
+% Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal.
 And a dish-shaped antenna is found to yield the most desirable response from a foreground contamination viewpoint.

### 2015-04-08 ms.tex
Modify Section 3
From 5b62b56:
============

In ms.tex,

(*) Modify Section 3

@@
 
-% In wide-field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits.
-This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
-Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide-field effects results in a characteristic {\it pitchfork} signature in the delay spectrum.
-
-% Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal.
-And a dish-shaped antenna is found to yield the most desirable response from a foreground contamination viewpoint.
-Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot used in their study, the high level of thermal noise prevented a robust confirmation.
-In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.
-
 \section{The Murchison Widefield Array Observations}\label{sec:MWA}
 
-The MWA instrument configuration, EoR observations, and data analysis used in this study are already described in \citet{thy15} and references therein.
+The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in \citet{thy15} and references therein.
 In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings.

### 2015-04-08 ms.tex
Modify Section 4
From 38453eb:
============

In ms.tex,

(*) Modify Section 4

@@
 
-Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling \citep{thy15} with no thermal noise fluctuations (bottom), for reference.
-The dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top) similar to the one used in \citet{thy15}, and is consistent with the improvement expected from averaging 12 independent snapshots.
-With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) has become $\gtrsim 10$ times more prominent.
-We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations.
-We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.
+Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling (bottom) with no thermal noise fluctuations \citep{thy15}, for reference.
+In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent.
+The bright branch of power at $\tau=0$ corresponds to foreground emission from the main lobe of the power pattern pointed at the zenith.
 
@@
 \includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
-\caption{Delay power spectra obtained from a single snapshot ({\it top}), by averaging 12 snapshots of LST aligned MWA data ({\it middle}), and from modeling with no thermal noise added ({\it bottom}) shown for reference.
+\caption{Delay power spectra obtained from a single snapshot ({\it top}), by averaging 12 snapshots of LST aligned MWA data ({\it middle}), and from modeling with no thermal noise added ({\it bottom}).
 The $x$-axis, denoted by $|\boldsymbol{b}|$ (and $k_\perp$), represents angular (and spatial) scales in the plane of the sky while the $y$-axis, shown in $\tau$ and $k_\parallel$, denotes the spatial scales along the line of sight.
@@
 \end{figure}
+
+The key defining feature of the {\it pitchfork} signature is an enhancement in foreground power near the horizon limits.
+In the individual snapshot, similar to the one used in our original study, faint features are visible near the horizon limits.
+But the high level of thermal fluctuations makes their significance marginal.
+In contrast, the dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top), and is consistent with the improvement expected from averaging 12 independent snapshots.
+With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) appears $\gtrsim 10$ times more prominent.
+We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations.
+We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.
 
@@
 
-The delay power spectra morphologies from data and modeling are remarkably similar despite some differences in the amplitude scales.
+The delay power spectra morphologies from data and modeling are remarkably similar in broad shape although they exhibit some differences in the amplitude scales.
 We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in \citet{thy15}.
@@
 Typically, the power near the negative horizon limit is seen with a signal-noise ratio (SNR) $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000.
-The models of \citet{thy15} have noted that the foreground power near the horizon limits is due to the nature of wide-field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m.
-Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in \citet{thy15}.
+% The models of \citet{thy15} have noted that the foreground power near the horizon limits is due to the nature of wide-field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m.
+Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in our earlier study.
 

### 2015-04-08 ms.tex
Modify Section 5
From e2e1f01:
============

In ms.tex,

(*) Modify Section 5

@@
 Sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} are yet to become operational.
-In the meanwhile, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA) currently under construction will be much closer in its capability to detect and place definitive constraints on the reionization epoch relative to the SKA and far ahead of current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.
+In the meanwhile, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA), currently under construction, will be much closer in its capability to detect and place definitive constraints on the reionization epoch relative to the SKA and far ahead of current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.
 
@@
 
-Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio foregrounds.
+Using deeper MWA data, we have confirmed with high significance the earlier prediction that wide-field EoR measurements suffer significant foreground contamination from near the horizon.
+This has important implications for instrument design and data analysis of future instruments such as HERA and SKA.
+
+Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.
+All-sky surveys matching the frequency and angular resolution of observation, and a detailed model of the instrument will further improve the accuracy of our models.
+In our earlier study, we proposed a selective flagging of data on different antenna spacings that can potentially mitigate foreground contamination by two orders of magnitude.
+Efforts are underway to incorporate this proposed foreground mitigation technique into the MWA data analysis algorithms.
+
+For future work, we plan to extend our analysis to the upcoming instrument, HERA, which is currently under construction.
+It is a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings.
+Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint.
+One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the observing strategy to maximize sensitivity to the cosmological signal.
+
+% Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio foregrounds.
 This poses perhaps the greatest challenge to EoR experiments and thus merits a detailed characterization in order to separate them from the desired cosmological H~{\sc i} signal.
 
-In a recent study, through the use of all-sky foreground and instrument models, the role of wide-field nature of radio interferometric measurements, hitherto unpredicted, has emerged.
+% In a recent study, through the use of all-sky foreground and instrument models, the role of wide-field nature of radio interferometric measurements, hitherto unpredicted, has emerged.
 Referred to as the {\it pitchfork} signature in the delay spectral domain, it is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon.
@@
 
-Knowledge of these characteristics weigh heavily on choices in instrument design like antenna aperture and in data analysis such as optimal weighting schemes for future instruments such as HERA and SKA.
+% Knowledge of these characteristics weigh heavily on choices in instrument design like antenna aperture and in data analysis such as optimal weighting schemes for future instruments such as HERA and SKA.
 We report the first robust detection of the {\it pitchfork} signature (which could not be confirmed earlier in single MWA snapshots due to large thermal fluctuations) with a signal-noise ratio $>10$ made possible by coherent averaging of 12 independent LST-aligned snapshots from MWA observations.
-
-% By averaging 12 independent LST-aligned snapshots from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the foreground contributions in the observed {\it visibilities} coherent.
-Foreground power in delay bins near the horizon is distinctly visible with a signal-noise ratio $>10$.
-Further, there is a close resemblance in the morphologies of delay power spectra from data and models.
-Together, they allow us to make the first robust confirmation of the nature of wide-field measurements in EoR experiments.
 

### 2015-04-09 ms.tex
Make minor modifications throughout
From 7094fca:
============

In ms.tex,

(*) Make minor modifications throughout

@@
 This contamination is the result of the interplay between foreground emission, particularly diffuse Galactic emission, and the wide-field properties typical of EoR instruments.
-Our simulations predicted that delay spectra from the MWA and other experiments should exhibit a characteristic ``pitchfork'' appearance with local maxima near the horizon delay limits, in addition to at the primary lobe of the power pattern.
+Our simulations predicted that delay spectra from the MWA and other experiments should exhibit a characteristic ``pitchfork'' appearance with local maxima near the horizon delay limits, in addition to at the primary lobe region.
 
@@
 In \citet{thy15}, we verified the general features of our simulations against MWA observations, but were unable to confirm the actual {\it pitchfork} prediction due to insufficient sensitivity in the small amount of data analyzed.
-Here, we use longer MWA integrations to confirm with high significance the presence of the key {\it pitchfork} characteristics of wide-field measurements predicted in the preceding study.
+Here, we use longer MWA integrations to confirm with high significance the presence of key {\it pitchfork} characteristics of wide-field measurements predicted in the preceding study.
 
@@
 
-The delay power spectrum is defined as:
+The delay power spectrum is defined as \citep{par12a,thy15}:
 \begin{align}\label{eqn:delay-power-spectrum}
@@
 
-Detailed modeling presented in our original study \citep{thy15} has indicated important implications for future instrument design and analysis algorithms:
+Detailed modeling presented in our original study \citep{thy15} has important implications for future instrument design and analysis algorithms:
 \begin{enumerate}
 \item positioned adjacent to the Fourier modes most sensitive to the cosmological signal, the {\it pitchfork} feature is a leading source of contamination in these modes, and 
-\item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity towards the horizon.
+\item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity away from the primary field of view.
 \end{enumerate}
@@
 
-Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling (bottom) with no thermal noise fluctuations \citep{thy15}, for reference.
+Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling (bottom) with no thermal noise fluctuations \citep{thy15} shown for reference.
 In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent.
@@
 
-Figure~\ref{fig:3-baseline-comparison-delay-spectra} shows the amplitudes of averaged delay spectra on three selected baseline vectors oriented northward.
+Figure~\ref{fig:3-baseline-comparison-delay-spectra} shows the averaged delay power spectra on three selected baseline vectors oriented northward.
 Data and noiseless models are shown in black and red respectively.
@@
 Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint.
-One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the observing strategy to maximize sensitivity to the cosmological signal.
+One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the observing strategy and data analysis to maximize sensitivity to the EoR signal.
 

### 2015-04-09 ms.tex
Minor change in Summary
From e188012:
============

In ms.tex,

(*) Minor change in Summary

@@
 Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint.
-One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the observing strategy and data analysis to maximize sensitivity to the EoR signal.
+One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.
 

### 2015-04-11 ms.tex
Make minor changes to Introduction
From 758a6e2:
============

In ms.tex,

(*) Make minor changes to Introduction

@@
 Sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} are yet to become operational.
-In the meanwhile, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA), currently under construction, will be much closer in its capability to detect and place definitive constraints on the reionization epoch relative to the SKA and far ahead of current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.
+In the meanwhile, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA), currently under development, will be much more advanced in its capability to detect and place definitive constraints on the reionization epoch relative to current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have only enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.
 
@@
 
+% \begin{thebibliography}{}
+% \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+% \bibitem[{{Ali} {et~al.}(2008){Ali}, {Bharadwaj}, \& {Chengalur}}]{ali08}
+% {Ali}, S.~S., {Bharadwaj}, S., \& {Chengalur}, J.~N. 2008, \mnras, 385, 2166
+
+% \bibitem[{{Beardsley} {et~al.}(2013){Beardsley}, {Hazelton}, {Morales},
+%   {Arcus}, {Barnes}, {Bernardi}, {Bowman}, {Briggs}, {Bunton}, {Cappallo},
+%   {Corey}, {Deshpande}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
+%   {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid},
+%   {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell},
+%   {Morgan}, {Oberoi}, {Ord}, {Pathikulangara}, {Prabu}, {Remillard}, {Rogers},
+%   {Roshi}, {Salah}, {Sault}, {Udaya}, {Srivani}, {Stevens}, {Subrahmanyan},
+%   {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams},
+%   \& {Wyithe}}]{bea13}
+% {Beardsley}, A.~P., {Hazelton}, B.~J., {Morales}, M.~F., {et~al.} 2013, \mnras,
+%   429, L5
+
+% \bibitem[{{Bernardi} {et~al.}(2009){Bernardi}, {de Bruyn}, {Brentjens},
+%   {Ciardi}, {Harker}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
+%   {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber09}
+% {Bernardi}, G., {de Bruyn}, A.~G., {Brentjens}, M.~A., {et~al.} 2009, \aap,
+%   500, 965
+
+% \bibitem[{{Bernardi} {et~al.}(2010){Bernardi}, {de Bruyn}, {Harker},
+%   {Brentjens}, {Ciardi}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
+%   {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber10}
+% {Bernardi}, G., {de Bruyn}, A.~G., {Harker}, G., {et~al.} 2010, \aap, 522, A67
+
+% \bibitem[{{Bowman} {et~al.}(2006){Bowman}, {Morales}, \& {Hewitt}}]{bow06}
+% {Bowman}, J.~D., {Morales}, M.~F., \& {Hewitt}, J.~N. 2006, \apj, 638, 20
+
+% \bibitem[{{Bowman} {et~al.}(2009){Bowman}, {Morales}, \& {Hewitt}}]{bow09}
+% ---. 2009, \apj, 695, 183
+
+% \bibitem[{{Bowman} {et~al.}(2013){Bowman}, {Cairns}, {Kaplan}, {Murphy},
+%   {Oberoi}, {Staveley-Smith}, {Arcus}, {Barnes}, {Bernardi}, {Briggs}, {Brown},
+%   {Bunton}, {Burgasser}, {Cappallo}, {Chatterjee}, {Corey}, {Coster},
+%   {Deshpande}, {deSouza}, {Emrich}, {Erickson}, {Goeke}, {Gaensler},
+%   {Greenhill}, {Harvey-Smith}, {Hazelton}, {Herne}, {Hewitt},
+%   {Johnston-Hollitt}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale},
+%   {Lynch}, {Matthews}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Ord},
+%   {Pathikulangara}, {Prabu}, {Remillard}, {Robishaw}, {Rogers}, {Roshi},
+%   {Salah}, {Sault}, {Shankar}, {Srivani}, {Stevens}, {Subrahmanyan}, {Tingay},
+%   {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams}, \&
+%   {Wyithe}}]{bow13}
+% {Bowman}, J.~D., {Cairns}, I., {Kaplan}, D.~L., {et~al.} 2013, \pasa, 30, 31
+
+% \bibitem[{{Datta} {et~al.}(2010){Datta}, {Bowman}, \& {Carilli}}]{dat10}
+% {Datta}, A., {Bowman}, J.~D., \& {Carilli}, C.~L. 2010, \apj, 724, 526
+
+% \bibitem[{{Di Matteo} {et~al.}(2004){Di Matteo}, {Ciardi}, \&
+%   {Miniati}}]{dim04}
+% {Di Matteo}, T., {Ciardi}, B., \& {Miniati}, F. 2004, \mnras, 355, 1053
+
+% \bibitem[{{Di Matteo} {et~al.}(2002){Di Matteo}, {Perna}, {Abel}, \&
+%   {Rees}}]{dim02}
+% {Di Matteo}, T., {Perna}, R., {Abel}, T., \& {Rees}, M.~J. 2002, \apj, 564, 576
+
+% \bibitem[{Dillon {et~al.}(2013)Dillon, Liu, \& Tegmark}]{dil13}
+% Dillon, J.~S., Liu, A., \& Tegmark, M. 2013, Phys. Rev. D, 87, 043005
+
+% \bibitem[{{Dillon} {et~al.}(2014){Dillon}, {Liu}, {Williams}, {Hewitt},
+%   {Tegmark}, {Morgan}, {Levine}, {Morales}, {Tingay}, {Bernardi}, {Bowman},
+%   {Briggs}, {Cappallo}, {Emrich}, {Mitchell}, {Oberoi}, {Prabu}, {Wayth}, \&
+%   {Webster}}]{dil14}
+% {Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002
+
+% \bibitem[{{Furlanetto} \& {Briggs}(2004)}]{fur04}
+% {Furlanetto}, S.~R., \& {Briggs}, F.~H. 2004, \nar, 48, 1039
+
+% \bibitem[{{Furlanetto} {et~al.}(2006){Furlanetto}, {Oh}, \& {Briggs}}]{fur06}
+% {Furlanetto}, S.~R., {Oh}, S.~P., \& {Briggs}, F.~H. 2006, \physrep, 433, 181
+
+% \bibitem[{{Ghosh} {et~al.}(2012){Ghosh}, {Prasad}, {Bharadwaj}, {Ali}, \&
+%   {Chengalur}}]{gho12}
+% {Ghosh}, A., {Prasad}, J., {Bharadwaj}, S., {Ali}, S.~S., \& {Chengalur}, J.~N.
+%   2012, \mnras, 426, 3295
+
+% \bibitem[{{Gleser} {et~al.}(2008){Gleser}, {Nusser}, \& {Benson}}]{gle08}
+% {Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383
+
+% \bibitem[{{Iliev} {et~al.}(2002){Iliev}, {Shapiro}, {Ferrara}, \&
+%   {Martel}}]{ili02}
+% {Iliev}, I.~T., {Shapiro}, P.~R., {Ferrara}, A., \& {Martel}, H. 2002, \apjl,
+%   572, L123
+
+% \bibitem[{{Liu} {et~al.}(2014{\natexlab{a}}){Liu}, {Parsons}, \&
+%   {Trott}}]{liu14a}
+% {Liu}, A., {Parsons}, A.~R., \& {Trott}, C.~M. 2014{\natexlab{a}}, \prd, 90,
+%   023018
+
+% \bibitem[{{Liu} {et~al.}(2014{\natexlab{b}}){Liu}, {Parsons}, \&
+%   {Trott}}]{liu14b}
+% ---. 2014{\natexlab{b}}, \prd, 90, 023019
+
+% \bibitem[{{Liu} \& {Tegmark}(2011)}]{liu11}
+% {Liu}, A., \& {Tegmark}, M. 2011, \prd, 83, 103006
+
+% \bibitem[{{Liu} {et~al.}(2009){Liu}, {Tegmark}, {Bowman}, {Hewitt}, \&
+%   {Zaldarriaga}}]{liu09}
+% {Liu}, A., {Tegmark}, M., {Bowman}, J., {Hewitt}, J., \& {Zaldarriaga}, M.
+%   2009, \mnras, 398, 401
+
+% \bibitem[{{Lonsdale} {et~al.}(2009){Lonsdale}, {Cappallo}, {Morales}, {Briggs},
+%   {Benkevitch}, {Bowman}, {Bunton}, {Burns}, {Corey}, {Desouza}, {Doeleman},
+%   {Derome}, {Deshpande}, {Gopala}, {Greenhill}, {Herne}, {Hewitt}, {Kamini},
+%   {Kasper}, {Kincaid}, {Kocz}, {Kowald}, {Kratzenberg}, {Kumar}, {Lynch},
+%   {Madhavi}, {Matejek}, {Mitchell}, {Morgan}, {Oberoi}, {Ord},
+%   {Pathikulangara}, {Prabu}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Shankar},
+%   {Srivani}, {Stevens}, {Tingay}, {Vaccarella}, {Waterson}, {Wayth}, {Webster},
+%   {Whitney}, {Williams}, \& {Williams}}]{lon09}
+% {Lonsdale}, C.~J., {Cappallo}, R.~J., {Morales}, M.~F., {et~al.} 2009, IEEE
+%   Proceedings, 97, 1497
+
+% \bibitem[{{Madau} {et~al.}(1997){Madau}, {Meiksin}, \& {Rees}}]{mad97}
+% {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 1997, \apj, 475, 429
+
+% \bibitem[{{McQuinn} {et~al.}(2006){McQuinn}, {Zahn}, {Zaldarriaga},
+%   {Hernquist}, \& {Furlanetto}}]{mcq06}
+% {McQuinn}, M., {Zahn}, O., {Zaldarriaga}, M., {Hernquist}, L., \& {Furlanetto},
+%   S.~R. 2006, \apj, 653, 815
+
+% \bibitem[{{Morales} {et~al.}(2006){Morales}, {Bowman}, \& {Hewitt}}]{mor06}
+% {Morales}, M.~F., {Bowman}, J.~D., \& {Hewitt}, J.~N. 2006, \apj, 648, 767
+
+% \bibitem[{{Morales} {et~al.}(2012){Morales}, {Hazelton}, {Sullivan}, \&
+%   {Beardsley}}]{mor12}
+% {Morales}, M.~F., {Hazelton}, B., {Sullivan}, I., \& {Beardsley}, A. 2012,
+%   \apj, 752, 137
+
+% \bibitem[{{Morales} \& {Hewitt}(2004)}]{mor04}
+% {Morales}, M.~F., \& {Hewitt}, J. 2004, \apj, 615, 7
+
+% \bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
+%   {Jacobs}, \& {Aguirre}}]{par12a}
+% {Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J.
+%   2012{\natexlab{a}}, \apj, 753, 81
+
+% \bibitem[{{Parsons} {et~al.}(2012{\natexlab{b}}){Parsons}, {Pober}, {Aguirre},
+%   {Carilli}, {Jacobs}, \& {Moore}}]{par12b}
+% {Parsons}, A.~R., {Pober}, J.~C., {Aguirre}, J.~E., {et~al.}
+%   2012{\natexlab{b}}, \apj, 756, 165
+
+% \bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
+%   {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
+%   {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{par10}
+% {Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
+%   1468
+
+% \bibitem[{{Pober} {et~al.}(2013){Pober}, {Parsons}, {Aguirre}, {Ali},
+%   {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
+%   {MacMahon}, {Manley}, {Moore}, {Stefan}, \& {Walbrugh}}]{pob13}
+% {Pober}, J.~C., {Parsons}, A.~R., {Aguirre}, J.~E., {et~al.} 2013, \apjl, 768,
+%   L36
+
+% \bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
+%   {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
+%   {Parsons}, {Tegmark}, \& {Werthimer}}]{pob14}
+% {Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66
+
+% \bibitem[{{Santos} {et~al.}(2005){Santos}, {Cooray}, \& {Knox}}]{san05}
+% {Santos}, M.~G., {Cooray}, A., \& {Knox}, L. 2005, \apj, 625, 575
+
+% \bibitem[{{Scott} \& {Rees}(1990)}]{sco90}
+% {Scott}, D., \& {Rees}, M.~J. 1990, \mnras, 247, 510
+
+% \bibitem[{{Sunyaev} \& {Zeldovich}(1972)}]{sun72}
+% {Sunyaev}, R.~A., \& {Zeldovich}, Y.~B. 1972, \aap, 20, 189
+
+% \bibitem[{{Thompson} {et~al.}(2001){Thompson}, {Moran}, \& {Swenson}}]{tho01}
+% {Thompson}, A.~R., {Moran}, J.~M., \& {Swenson}, Jr., G.~W. 2001,
+%   {Interferometry and Synthesis in Radio Astronomy, 2nd Edition} (Wiley)
+
+% \bibitem[{{Thyagarajan} {et~al.}(2013){Thyagarajan}, {Udaya Shankar},
+%   {Subrahmanyan}, {Arcus}, {Bernardi}, {Bowman}, {Briggs}, {Bunton},
+%   {Cappallo}, {Corey}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
+%   {Hazelton}, {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper},
+%   {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter},
+%   {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Pathikulangara},
+%   {Remillard}, {Rogers}, {Anish Roshi}, {Salah}, {Sault}, {Srivani}, {Stevens},
+%   {Thiagaraj}, {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams},
+%   {Williams}, \& {Wyithe}}]{thy13}
+% {Thyagarajan}, N., {Udaya Shankar}, N., {Subrahmanyan}, R., {et~al.} 2013,
+%   \apj, 776, 6
+
+% \bibitem[{{Thyagarajan} {et~al.}(2015){Thyagarajan}, {Jacobs}, {Bowman},
+%   {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll}, {Corey},
+%   {de Oliveira-Costa}, {Dillon}, {Emrich}, {Ewall-Wice}, {Feng}, {Goeke},
+%   {Greenhill}, {Hazelton}, {Hewitt}, {Hurley-Walker}, {Johnston-Hollitt},
+%   {Kaplan}, {Kasper}, {Kim}, {Kittiwisit}, {Kratzenberg}, {Lenc}, {Line},
+%   {Loeb}, {Lonsdale}, {Lynch}, {McKinley}, {McWhirter}, {Mitchell}, {Morales},
+%   {Morgan}, {Neben}, {Oberoi}, {Offringa}, {Ord}, {Paul}, {Pindor}, {Pober},
+%   {Prabu}, {Procopio}, {Riding}, {Rogers}, {Roshi}, {Udaya Shankar}, {Sethi},
+%   {Srivani}, {Subrahmanyan}, {Sullivan}, {Tegmark}, {Tingay}, {Trott},
+%   {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams}, {Williams}, {Wu}, \&
+%   {Wyithe}}]{thy15}
+% {Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.} 2015, ArXiv
+%   e-prints, arXiv:1502.07596
+
+% \bibitem[{{Tingay} {et~al.}(2013){Tingay}, {Goeke}, {Bowman}, {Emrich}, {Ord},
+%   {Mitchell}, {Morales}, {Booler}, {Crosse}, {Wayth}, {Lonsdale}, {Tremblay},
+%   {Pallot}, {Colegate}, {Wicenec}, {Kudryavtseva}, {Arcus}, {Barnes},
+%   {Bernardi}, {Briggs}, {Burns}, {Bunton}, {Cappallo}, {Corey}, {Deshpande},
+%   {Desouza}, {Gaensler}, {Greenhill}, {Hall}, {Hazelton}, {Herne}, {Hewitt},
+%   {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg},
+%   {Lynch}, {Mckinley}, {Mcwhirter}, {Morgan}, {Oberoi}, {Pathikulangara},
+%   {Prabu}, {Remillard}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Udaya-Shankar},
+%   {Schlagenhaufer}, {Srivani}, {Stevens}, {Subrahmanyan}, {Waterson},
+%   {Webster}, {Whitney}, {Williams}, {Williams}, \& {Wyithe}}]{tin13}
+% {Tingay}, S.~J., {Goeke}, R., {Bowman}, J.~D., {et~al.} 2013, \pasa, 30, 7
+
+% \bibitem[{{Tozzi} {et~al.}(2000){Tozzi}, {Madau}, {Meiksin}, \& {Rees}}]{toz00}
+% {Tozzi}, P., {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 2000, \apj, 528, 597
+
+% \bibitem[{{Trott} {et~al.}(2012){Trott}, {Wayth}, \& {Tingay}}]{tro12}
+% {Trott}, C.~M., {Wayth}, R.~B., \& {Tingay}, S.~J. 2012, \apj, 757, 101
+
+% \bibitem[{{van Cittert}(1934)}]{van34}
+% {van Cittert}, P.~H. 1934, Physica, 1, 201
+
+% \bibitem[{{van Haarlem} {et~al.}(2013){van Haarlem}, {Wise}, {Gunst}, {Heald},
+%   {McKean}, {Hessels}, {de Bruyn}, {Nijboer}, {Swinbank}, {Fallows},
+%   {Brentjens}, {Nelles}, {Beck}, {Falcke}, {Fender}, {H{\"o}randel},
+%   {Koopmans}, {Mann}, {Miley}, {R{\"o}ttgering}, {Stappers}, {Wijers},
+%   {Zaroubi}, {van den Akker}, {Alexov}, {Anderson}, {Anderson}, {van Ardenne},
+%   {Arts}, {Asgekar}, {Avruch}, {Batejat}, {B{\"a}hren}, {Bell}, {Bell}, {van
+%   Bemmel}, {Bennema}, {Bentum}, {Bernardi}, {Best}, {B{\^i}rzan}, {Bonafede},
+%   {Boonstra}, {Braun}, {Bregman}, {Breitling}, {van de Brink}, {Broderick},
+%   {Broekema}, {Brouw}, {Br{\"u}ggen}, {Butcher}, {van Cappellen}, {Ciardi},
+%   {Coenen}, {Conway}, {Coolen}, {Corstanje}, {Damstra}, {Davies}, {Deller},
+%   {Dettmar}, {van Diepen}, {Dijkstra}, {Donker}, {Doorduin}, {Dromer}, {Drost},
+%   {van Duin}, {Eisl{\"o}ffel}, {van Enst}, {Ferrari}, {Frieswijk}, {Gankema},
+%   {Garrett}, {de Gasparin}, {Gerbers}, {de Geus}, {Grie{\ss}meier}, {Grit},
+%   {Gruppen}, {Hamaker}, {Hassall}, {Hoeft}, {Holties}, {Horneffer}, {van der
+%   Horst}, {van Houwelingen}, {Huijgen}, {Iacobelli}, {Intema}, {Jackson},
+%   {Jelic}, {de Jong}, {Kant}, {Karastergiou}, {Koers}, {Kollen}, {Kondratiev},
+%   {Kooistra}, {Koopman}, {Koster}, {Kuniyoshi}, {Kramer}, {Kuper},
+%   {Lambropoulos}, {Law}, {van Leeuwen}, {Lemaitre}, {Loose}, {Maat}, {Macario},
+%   {Markoff}, {Masters}, {McFadden}, {McKay-Bukowski}, {Meijering}, {Meulman},
+%   {Mevius}, {Millenaar}, {Miller-Jones}, {Mohan}, {Mol}, {Morawietz},
+%   {Morganti}, {Mulcahy}, {Mulder}, {Munk}, {Nieuwenhuis}, {van Nieuwpoort},
+%   {Noordam}, {Norden}, {Noutsos}, {Offringa}, {Olofsson}, {Omar}, {Orr{\'u}},
+%   {Overeem}, {Paas}, {Pandey-Pommier}, {Pandey}, {Pizzo}, {Polatidis},
+%   {Rafferty}, {Rawlings}, {Reich}, {de Reijer}, {Reitsma}, {Renting},
+%   {Riemers}, {Rol}, {Romein}, {Roosjen}, {Ruiter}, {Scaife}, {van der Schaaf},
+%   {Scheers}, {Schellart}, {Schoenmakers}, {Schoonderbeek}, {Serylak},
+%   {Shulevski}, {Sluman}, {Smirnov}, {Sobey}, {Spreeuw}, {Steinmetz}, {Sterks},
+%   {Stiepel}, {Stuurwold}, {Tagger}, {Tang}, {Tasse}, {Thomas}, {Thoudam},
+%   {Toribio}, {van der Tol}, {Usov}, {van Veelen}, {van der Veen}, {ter Veen},
+%   {Verbiest}, {Vermeulen}, {Vermaas}, {Vocks}, {Vogt}, {de Vos}, {van der Wal},
+%   {van Weeren}, {Weggemans}, {Weltevrede}, {White}, {Wijnholds}, {Wilhelmsson},
+%   {Wucknitz}, {Yatawatta}, {Zarka}, {Zensus}, \& {van Zwieten}}]{van13}
+% {van Haarlem}, M.~P., {Wise}, M.~W., {Gunst}, A.~W., {et~al.} 2013, \aap, 556,
+%   A2
+
+% \bibitem[{{Wang} {et~al.}(2006){Wang}, {Tegmark}, {Santos}, \& {Knox}}]{wan06}
+% {Wang}, X., {Tegmark}, M., {Santos}, M.~G., \& {Knox}, L. 2006, \apj, 650, 529
+
+% \bibitem[{{Zaldarriaga} {et~al.}(2004){Zaldarriaga}, {Furlanetto}, \&
+%   {Hernquist}}]{zal04}
+% {Zaldarriaga}, M., {Furlanetto}, S.~R., \& {Hernquist}, L. 2004, \apj, 608, 622
+
+% \bibitem[{{Zernike}(1938)}]{zer38}
+% {Zernike}, F. 1938, Physica, 5, 785
+
+% \end{thebibliography}
+
 \end{document}

### 2015-04-11 ms.tex
Use Paper I instead of Thyagarajan et al.(2015)
From 5b99dfd:
============

In ms.tex,

(*) Change repeated references to Thyagarajan et al. (2015) to Paper I

@@
 
-Our recent study \citep{thy15} used all-sky foreground and instrument models for the first time in order to simulate actual EoR experiments more accurately than previous studies.
+Our recent study \citep[][hereafter referred to as Paper~I]{thy15} used all-sky foreground and instrument models for the first time in order to simulate actual EoR experiments more accurately than previous studies.
 Surprisingly, we found that foreground emission outside the primary beam field of view caused the most significant contamination of the cosmological H~{\sc i} power spectrum Fourier modes that are considered most sensitive for detecting the signal in delay spectrum based analyses.
@@
 
-In \citet{thy15}, we verified the general features of our simulations against MWA observations, but were unable to confirm the actual {\it pitchfork} prediction due to insufficient sensitivity in the small amount of data analyzed.
+In Paper~I, we verified the general features of our simulations against MWA observations, but were unable to confirm the actual {\it pitchfork} prediction due to insufficient sensitivity in the small amount of data analyzed.
 Here, we use longer MWA integrations to confirm with high significance the presence of key {\it pitchfork} characteristics of wide-field measurements predicted in the preceding study.
@@
 
-\citet{thy15} have described in detail the effects of wide-field measurements as seen in the delay spectra of interferometer {\it visibilities}.
+Paper~I describes in detail the effects of wide-field measurements as seen in the delay spectra of interferometer {\it visibilities}.
 Here, we list the relevant equations and give a brief overview of the wide-field signatures predicted therein.
 
-The delay spectrum for a baseline vector, $\boldsymbol{b}$, is given by \citep{par12a,par12b,thy13,thy15}: 
+The delay spectrum for a baseline vector, $\boldsymbol{b}$, is given by \citep[][Paper~I]{par12a,par12b,thy13}: 
 \begin{align}
@@
 
-The delay power spectrum is defined as \citep{par12a,thy15}:
+The delay power spectrum is defined as \citep[][Paper~I]{par12a}:
 \begin{align}\label{eqn:delay-power-spectrum}
@@
 
-Detailed modeling presented in our original study \citep{thy15} has important implications for future instrument design and analysis algorithms:
+Detailed modeling presented in Paper~I has important implications for future instrument design and analysis algorithms:
 \begin{enumerate}
@@
 
-The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in \citet{thy15} and references therein.
+The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in Paper~I and references therein.
 In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings.
@@
 
-Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling (bottom) with no thermal noise fluctuations \citep{thy15} shown for reference.
+Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling (bottom) with no thermal noise fluctuations (Paper~I) shown for reference.
 In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent.
@@
 The delay power spectra morphologies from data and modeling are remarkably similar in broad shape although they exhibit some differences in the amplitude scales.
-We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in \citet{thy15}.
+We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in Paper~I.
 
@@
 Typically, the power near the negative horizon limit is seen with a signal-noise ratio (SNR) $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000.
-% The models of \citet{thy15} have noted that the foreground power near the horizon limits is due to the nature of wide-field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m.
+% The models of Paper~I have noted that the foreground power near the horizon limits is due to the nature of wide-field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m.
 Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in our earlier study.

### 2015-04-11 ms.tex
Modify Section 2
From 2e7b1a2:
============

In ms.tex,

(*) Modify Section 2

@@
 This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
+In this paper, we confirm this key feature using deeper data from the MWA.
 
-Detailed modeling presented in Paper~I has important implications for future instrument design and analysis algorithms:
-\begin{enumerate}
-\item positioned adjacent to the Fourier modes most sensitive to the cosmological signal, the {\it pitchfork} feature is a leading source of contamination in these modes, and 
-\item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity away from the primary field of view.
-\end{enumerate}
-
-In this paper, we confirm this key feature using deeper data from the MWA.
+% Detailed modeling presented in Paper~I has important implications for future instrument design and analysis algorithms:
+% \begin{enumerate}
+% \item positioned adjacent to the Fourier modes most sensitive to the cosmological signal, the {\it pitchfork} feature is a leading source of contamination in these modes, and 
+% \item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity away from the primary field of view.
+% \end{enumerate}
 

### 2015-04-11 ms.tex
Update Section 4
From 03449a2:
============

In ms.tex,

(*) Update Section 4

@@
 
-Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling (bottom) with no thermal noise fluctuations (Paper~I) shown for reference.
+Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling with no thermal noise fluctuations shown for reference (bottom).
 In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent.
-The bright branch of power at $\tau=0$ corresponds to foreground emission from the main lobe of the power pattern pointed at the zenith.
+The bright branch of power at $\tau=0$ corresponds to foreground emission from the main lobe of the antenna power pattern pointed at the zenith.
 
@@
 But the high level of thermal fluctuations makes their significance marginal.
-In contrast, the dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top), and is consistent with the improvement expected from averaging 12 independent snapshots.
+In contrast, the dynamic range in the averaged data (middle) is a factor $\gtrsim 10$ higher (in delay power spectrum) relative to that in a single snapshot (top), and is consistent with the improvement expected from averaging 12 independent snapshots.
 With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) appears $\gtrsim 10$ times more prominent.
-We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations.
+Faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations.
 We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.

### 2015-04-11 ms.tex
Update Section 5 and MWACS paper reference
From 1d3cd47:
============

In ms.tex,

(*) Update Section 5

In eor.bib,

(*) Update reference to MWACS paper

@@
 This has important implications for instrument design and data analysis of future instruments such as HERA and SKA.
+For instance, SKA plans to use vertical log-periodic dipole arrays while HERA will use dishes that limit response near the horizon.
+Details of both telescopes are being finalized.
 
 Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.
-All-sky surveys matching the frequency and angular resolution of observation, and a detailed model of the instrument will further improve the accuracy of our models.
+Extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Hurley-Walker et al.
+in prep.) to cover the entire hemisphere, and a detailed model of the instrument will further improve the accuracy of our models.
 In our earlier study, we proposed a selective flagging of data on different antenna spacings that can potentially mitigate foreground contamination by two orders of magnitude.
-Efforts are underway to incorporate this proposed foreground mitigation technique into the MWA data analysis algorithms.
+Following the confirmation presented here, efforts are underway to incorporate this proposed foreground mitigation technique into the MWA data analysis algorithms.
 
-For future work, we plan to extend our analysis to the upcoming instrument, HERA, which is currently under construction.
+For future work, we plan to extend our analysis to HERA.
 It is a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings.

### 2015-04-11 ms.tex
Minor changes to Introduction
From 68b5475:
============

In ms.tex,

(*) Minor changes to Introduction

@@
 
-In Paper~I, we verified the general features of our simulations against MWA observations, but were unable to confirm the actual {\it pitchfork} prediction due to insufficient sensitivity in the small amount of data analyzed.
-Here, we use longer MWA integrations to confirm with high significance the presence of key {\it pitchfork} characteristics of wide-field measurements predicted in the preceding study.
+In Paper~I, we verified the general features of our simulations against MWA observations, but were unable to confirm the {\it pitchfork} prediction due to insufficient sensitivity in the small amount of data analyzed.
+Here, we use deeper MWA data to confirm with high significance the presence of key {\it pitchfork} characteristics of wide-field measurements predicted in the preceding study.
 

### 2015-04-25 ms.tex
Update ms.bbl included in ms.tex
From 03f54dc:
============

In ms.tex,

(*) Update ms.bbl included in ms.tex
Make changes suggested by Melanie
From 6501829:
============

In ms.tex,

(*) Make changes suggested by Melanie
(*) Minor changes in Introduction
(*) Chnage GLEAM author to Wayth

@@
 
-% This analysis confirms recent predictions of certain key signatures in the delay spectra of wide-field radio interferometer measurements.
-While probing H~{\sc i} in the epoch of reionization (EoR) through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature.
-This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions.
-Thus it forms a critical input to design and analysis choices of future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array.
-By improving Murchison Widefield Array data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$.
-
 \end{abstract}
@@
 
-% The primary challenge to detection of cosmological H~{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}.
-Since the foregrounds and the signal have inherent differences in spatial isotropy and spectral smoothness \citep{mor04,mor06,bow09,liu11,par12b,dil13,pob13}, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,tro12,pob13,dil14,liu14a,liu14b,thy13,thy15}.
-
 The primary challenge to detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker.
-But the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08}.
+However, the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08}.
 Thus, a detailed characterization of foreground emission has become essential \citep{ali08,bow09,liu09,ber09,ber10,dat10,liu11,gho12,mor12,par12b,tro12,pob13,dil13,dil14,liu14a,liu14b,thy13,thy15}.
 
-% A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments.
-It was noted to cause significant contamination in Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal.
-It has been shown that a careful design of antenna aperture can significantly mitigate this contamination.
-And an optimal weighting of foreground-contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
-Thus, knowledge of such detailed foreground signatures becomes essential for design and analysis choices of future instruments such as HERA and SKA.
-This paper presents a follow-up analysis of that study.
-By using a larger volume of MWA data obtained independently over different nights pointed at the same region of sky, we confirm with high significance the presence of certain key characteristics (referred to as the {\it pitchfork} signature) of wide-field measurements predicted in the preceding study.
-
 Our recent study \citep[][hereafter referred to as Paper~I]{thy15} used all-sky foreground and instrument models for the first time in order to simulate actual EoR experiments more accurately than previous studies.
-Surprisingly, we found that foreground emission outside the primary beam field of view caused the most significant contamination of the cosmological H~{\sc i} power spectrum Fourier modes that are considered most sensitive for detecting the signal in delay spectrum based analyses.
+Surprisingly, we found that foreground emission outside the primary beam field of view caused the most significant contamination of Fourier modes considered most sensitive for detecting the cosmological H~{\sc i} signal in delay spectrum based analyses.
 This contamination is the result of the interplay between foreground emission, particularly diffuse Galactic emission, and the wide-field properties typical of EoR instruments.
@@
 
-% Detailed modeling presented in Paper~I has important implications for future instrument design and analysis algorithms:
-% \begin{enumerate}
-% \item positioned adjacent to the Fourier modes most sensitive to the cosmological signal, the {\it pitchfork} feature is a leading source of contamination in these modes, and 
-% \item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity away from the primary field of view.
-% \end{enumerate}
-
 \section{The Murchison Widefield Array Observations}\label{sec:MWA}
@@
 \centering
-% \includegraphics[width=\linewidth]{multi_baseline_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
 \includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
@@
 Typically, the power near the negative horizon limit is seen with a signal-noise ratio (SNR) $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000.
-% The models of Paper~I have noted that the foreground power near the horizon limits is due to the nature of wide-field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m.
 Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in our earlier study.
@@
 Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.
-Extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Hurley-Walker et al.
-in prep.) to cover the entire hemisphere, and a detailed model of the instrument will further improve the accuracy of our models.
+Extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Wayth et al.
+submitted) to cover the entire hemisphere, and a detailed model of the instrument will further improve the accuracy of our models.
 In our earlier study, we proposed a selective flagging of data on different antenna spacings that can potentially mitigate foreground contamination by two orders of magnitude.
@@
 One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.
-
-% Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio foregrounds.
-This poses perhaps the greatest challenge to EoR experiments and thus merits a detailed characterization in order to separate them from the desired cosmological H~{\sc i} signal.
-
-% In a recent study, through the use of all-sky foreground and instrument models, the role of wide-field nature of radio interferometric measurements, hitherto unpredicted, has emerged.
-Referred to as the {\it pitchfork} signature in the delay spectral domain, it is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon.
-The latter is due to the highly nonlinear mapping between geometric delays and subtended solid angles, besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions.
-Owing to its localization in the delay domain, it is a leading cause of contamination in Fourier modes most sensitive to the EoR H~{\sc i} signal.
-
-% Knowledge of these characteristics weigh heavily on choices in instrument design like antenna aperture and in data analysis such as optimal weighting schemes for future instruments such as HERA and SKA.
-We report the first robust detection of the {\it pitchfork} signature (which could not be confirmed earlier in single MWA snapshots due to large thermal fluctuations) with a signal-noise ratio $>10$ made possible by coherent averaging of 12 independent LST-aligned snapshots from MWA observations.
 
@@
 % {Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383
+
+% \bibitem[{{Hurley-Walker} {et~al.}(2014){Hurley-Walker}, {Morgan}, {Wayth},
+%   {Hancock}, {Bell}, {Bernardi}, {Bhat}, {Briggs}, {Deshpande}, {Ewall-Wice},
+%   {Feng}, {Hazelton}, {Hindson}, {Jacobs}, {Kaplan}, {Kudryavtseva}, {Lenc},
+%   {McKinley}, {Mitchell}, {Pindor}, {Procopio}, {Oberoi}, {Offringa}, {Ord},
+%   {Riding}, {Bowman}, {Cappallo}, {Corey}, {Emrich}, {Gaensler}, {Goeke},
+%   {Greenhill}, {Hewitt}, {Johnston-Hollitt}, {Kasper}, {Kratzenberg},
+%   {Lonsdale}, {Lynch}, {McWhirter}, {Morales}, {Morgan}, {Prabu}, {Rogers},
+%   {Roshi}, {Shankar}, {Srivani}, {Subrahmanyan}, {Tingay}, {Waterson},
+%   {Webster}, {Whitney}, {Williams}, \& {Williams}}]{hur14}
+% {Hurley-Walker}, N., {Morgan}, J., {Wayth}, R.~B., {et~al.} 2014, \pasa, 31, 45
 

### 2015-04-29 ms.tex
Add a couple of justifications, changes in wording
From 02433ee:
============

In ms.tex,

(*) Add justification for using northward baselines for pitchfork demo
(*) Add justification for stopping short of a full quantitative
comparison between data and model
(*) Changes in wording throughout

@@
 
-Here we confirm a recently predicted and previously unknown foreground signature in the 3D power spectra of high redshift 21~cm measurements, wherein the interferometer is sensitive to large-scale structure on all baselines.
+Here we confirm a recently predicted and previously unknown foreground signature in the 3D power spectra of high-redshift 21~cm measurements, wherein the interferometer is sensitive to large-scale structure on all baselines.
 This is due to the inherently chromatic nature of a wide-field instrument response and is characterized by enhanced power from foreground emission in Fourier modes adjacent to those considered to be most sensitive to the cosmological H~{\sc i} signal.
@@
 It is characterized by a period of non-linear growth of matter density perturbations and astrophysical evolution in the Universe's history.
-Detection of redshifted 21~cm radiation of H~{\sc i} from this epoch is one of the most promising probes of the evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
+Detection of redshifted 21~cm radiation of H~{\sc i} from this epoch is one of the most promising probes of the evolution of large scale structure during this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
 
@@
 
-The primary challenge to detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker.
+The primary challenge to detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, which is $\sim 10^4$ stronger than the desired signal.
 However, the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08}.
@@
 Optimal weighting of foreground contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
-Thus, knowledge of such detailed foreground signatures becomes essential for design and analysis choices of future instruments such as HERA and SKA.
+Thus, knowledge of such detailed foreground signatures is key for design and analysis choices of future instruments such as HERA and SKA.
 
@@
 Paper~I describes in detail the effects of wide-field measurements as seen in the delay spectra of interferometer {\it visibilities}.
-Here, we list the relevant equations and give a brief overview of the wide-field signatures predicted therein.
+We list the relevant equations and give a brief overview of the wide-field signatures predicted therein.
 
-The delay spectrum for a baseline vector, $\boldsymbol{b}$, is given by \citep[][Paper~I]{par12a,par12b,thy13}: 
+The delay spectrum for a baseline vector, $\boldsymbol{b}$, is \citep[][Paper~I]{par12a,par12b,thy13}: 
 \begin{align}
-  \tilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
+  \widetilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
 \end{align}
@@
 \begin{align}\label{eqn:delay-power-spectrum}
-  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{A_\textrm{e}}{\lambda^2\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
+  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\widetilde{V}_b(\tau)|^2\left(\frac{A_\textrm{e}}{\lambda^2\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
 \end{align}
@@
 This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
-In this paper, we confirm this key feature using deeper data from the MWA.
+We confirm this key feature using deeper MWA data.
 
-\section{The Murchison Widefield Array Observations}\label{sec:MWA}
+\section{MWA Observations}\label{sec:MWA}
 
@@
 The database contains 14 snapshots satisfying these criteria.
-Two of these snapshots were found to contain amplitude and phase artifacts for a significant duration across different baselines.
-Hence, they have been excluded from our analysis.
+Two of these snapshots, which contained amplitude and phase artifacts for a significant duration across different baselines, are excluded from our analysis.
 
-The delay spectra of the rest of the snapshots were verified to be coherent in their amplitudes and phases.
-These complex valued delay spectra from independent snapshots are averaged together to lower thermal fluctuations without losing coherence from foreground contributions.
-The results are discussed below.
+The delay spectra of the rest of the snapshots were verified to be coherent in their amplitudes and phases. Results from this coherent averaging are discussed below.
 
@@
 In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent.
-The bright branch of power at $\tau=0$ corresponds to foreground emission from the main lobe of the antenna power pattern pointed at the zenith.
+The bright horizontal branch of power at $\tau\simeq 0$ corresponds to foreground emission from the main lobe of the antenna power pattern pointed at the zenith.
 
@@
 Power near the horizon limits caused by wide-field effects are prominent.
-Faint horizontal features at $\tau=\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz.
+Faint horizontal features at $\tau\simeq\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz.
 \label{fig:delay-spectra}}
@@
 
-The key defining feature of the {\it pitchfork} signature is an enhancement in foreground power near the horizon limits.
-In the individual snapshot, similar to the one used in our original study, faint features are visible near the horizon limits.
+In the single snapshot (top), similar to the one used in our earlier study, faint features associated with the {\it pitchfork} signature are visible near the horizon limits.
 But the high level of thermal fluctuations makes their significance marginal.
-In contrast, the dynamic range in the averaged data (middle) is a factor $\gtrsim 10$ higher (in delay power spectrum) relative to that in a single snapshot (top), and is consistent with the improvement expected from averaging 12 independent snapshots.
-With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) appears $\gtrsim 10$ times more prominent.
-Faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations.
-We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.
+In contrast, the dynamic range in the averaged data (middle) is a factor $\gtrsim 10$ higher (in delay power spectrum) relative to that in a single snapshot, and is consistent with the improvement expected from averaging 12 independent snapshots.
+Hence, the foreground power near the horizon limits appears $\gtrsim 10$ times more prominent.
+Also, faint horizontal features, not seen in the single snapshot, appear at $\tau \simeq \pm 0.78\,\mu$s thus confirming the improvement in sensitivity.
+We identify these faint features as the response of the MWA coarse band edges flagged periodically every 1.28~MHz.
 
+In order to show that low-level ubiquitous diffuse emission is a significant contributor to the {\it pitchfork} signature, contribution from any strong emission from near the Galactic center needs to be minimized.
+This is best illustrated with northward antenna spacings which map any residual emission from this region (even though the Galactic center has just set over the western horizon) to $\tau\simeq 0$ and thus reduce the impact on higher delay modes (Paper~I).
 Figure~\ref{fig:3-baseline-comparison-delay-spectra} shows the averaged delay power spectra on three selected baseline vectors oriented northward.
@@
 The horizontal dotted black line denotes {\it rms} of thermal fluctuations estimated from data.
-The vertical dashed line denotes horizon delay limits, and the vertical dot-dashed lines denote delays at which the responses to coarse band edge flagging are expected.
+The vertical dashed line denotes horizon delay limits, and the vertical dotted-dashed lines denote delays at which the responses to coarse band edge flagging are expected.
 
@@
 The vertical dashed lines denote the horizon delay limits.
-The vertical dot-dashed lines at $\tau=\pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz.
+The vertical dotted-dashed lines at $\tau = \pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz.
 The peaks close to the horizon delay limits are distinctly visible at $\sim 10$-1000~$\sigma$ levels.
@@
 
-The delay power spectra morphologies from data and modeling are remarkably similar in broad shape although they exhibit some differences in the amplitude scales.
+We focus on the prominent peaks in data near the horizon limits.
+Typically, the power near the negative horizon limit is seen with a signal-noise ratio $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000.
+
+There is a remarkable agreement in broad morphology between the data and the model.
+However, some differences in the amplitude scales are noted.
 We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in Paper~I.
+At present, these uncertainties prevent a more thorough quantitative comparison between the model and the data.
+Extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Wayth et al.
+submitted) to cover the entire hemisphere, and a detailed model of the instrument will improve the accuracy of our model.
 
-We focus on the peaks near the horizon limits in the data.
-Typically, the power near the negative horizon limit is seen with a signal-noise ratio (SNR) $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000.
-Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in our earlier study.
+We note that reducing uncertainties will only change the relative strength of the {\it pitchfork} signature in our model.
+However, the effects giving rise to this signature are generic to all wide-field measurements.
+Thus, the extremely high significance detection of foreground emission near the horizon limits is a robust confirmation of the predicted wide-field measurement phenomenon.
 
@@
 This has important implications for instrument design and data analysis of future instruments such as HERA and SKA.
-For instance, SKA plans to use vertical log-periodic dipole arrays while HERA will use dishes that limit response near the horizon.
+For instance, SKA plans to use ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of pseudo-randomly placed vertical log-periodic dipole arrays.
+The ``station beam'' will be obtained by a phased addition of the dipole responses.
+The typical horizon response of these station beams is $\gtrsim$~30~dB lower than at the zenith.
+HERA will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA.
 Details of both telescopes are being finalized.
+Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.
 
-Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.
-Extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Wayth et al.
-submitted) to cover the entire hemisphere, and a detailed model of the instrument will further improve the accuracy of our models.
-In our earlier study, we proposed a selective flagging of data on different antenna spacings that can potentially mitigate foreground contamination by two orders of magnitude.
-Following the confirmation presented here, efforts are underway to incorporate this proposed foreground mitigation technique into the MWA data analysis algorithms.
+In our earlier study, we proposed a selective flagging of data on different baselines that can potentially mitigate foreground contamination by two orders of magnitude.
+Following the confirmation presented here, efforts are underway to incorporate this proposed foreground mitigation technique into the MWA data analysis.
 

### 2015-04-29 ms.tex
Replace figures with journal compatible names
From faebaa2:
============

Add renamed figures f1.eps, f2.eps to git repo

In ms.tex,

(*) Replace first figure to f1.eps
(*) Replace second figure to f2.eps
Cite private communication from Randall Wayth
From 1a02743:
============

In ms.tex,

(*) Cite private communication from Randall Wayth
(*) Update the included ms.bbl info

@@
 \centering
-\includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
+% \includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
+\includegraphics[width=\linewidth]{f1.eps}
 \caption{Delay power spectra obtained from a single snapshot ({\it top}), by averaging 12 snapshots of LST aligned MWA data ({\it middle}), and from modeling with no thermal noise added ({\it bottom}).
@@
 \centering
-\includegraphics[width=\linewidth]{3_baseline_comparison_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
+% \includegraphics[width=\linewidth]{3_baseline_comparison_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
+\includegraphics[width=\linewidth]{f2.eps}
 \caption{Delay power spectra on three antenna spacings oriented northward, obtained by coherent averaging of 12 snapshots aligned in LST.
@@
 The ``station beam'' will be obtained by a phased addition of the dipole responses.
-The typical horizon response of these station beams is $\gtrsim$~30~dB lower than at the zenith.
+The typical horizon response of these station beams is $\gtrsim$~30~dB lower than at the zenith (private communication from R.~Wayth).
 HERA will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA.

### 2015-04-29 ms.tex
Switch from using eor.bib to included bbl info
From ddeba41:
============

In ms.tex,

(*) Switch from using eor.bib to included bbl info

@@
 \bibliographystyle{apj}
-\bibliography{eor}
+% \bibliography{eor}
 
-% \begin{thebibliography}{}
-% \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
 
-% \bibitem[{{Ali} {et~al.}(2008){Ali}, {Bharadwaj}, \& {Chengalur}}]{ali08}
-% {Ali}, S.~S., {Bharadwaj}, S., \& {Chengalur}, J.~N. 2008, \mnras, 385, 2166
+\bibitem[{{Ali} {et~al.}(2008){Ali}, {Bharadwaj}, \& {Chengalur}}]{ali08}
+{Ali}, S.~S., {Bharadwaj}, S., \& {Chengalur}, J.~N. 2008, \mnras, 385, 2166
 
-% \bibitem[{{Beardsley} {et~al.}(2013){Beardsley}, {Hazelton}, {Morales},
-%   {Arcus}, {Barnes}, {Bernardi}, {Bowman}, {Briggs}, {Bunton}, {Cappallo},
-%   {Corey}, {Deshpande}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
-%   {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid},
-%   {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell},
-%   {Morgan}, {Oberoi}, {Ord}, {Pathikulangara}, {Prabu}, {Remillard}, {Rogers},
-%   {Roshi}, {Salah}, {Sault}, {Udaya}, {Srivani}, {Stevens}, {Subrahmanyan},
-%   {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams},
-%   \& {Wyithe}}]{bea13}
-% {Beardsley}, A.~P., {Hazelton}, B.~J., {Morales}, M.~F., {et~al.} 2013, \mnras,
-%   429, L5
+\bibitem[{{Beardsley} {et~al.}(2013){Beardsley}, {Hazelton}, {Morales},
+  {Arcus}, {Barnes}, {Bernardi}, {Bowman}, {Briggs}, {Bunton}, {Cappallo},
+  {Corey}, {Deshpande}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
+  {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid},
+  {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell},
+  {Morgan}, {Oberoi}, {Ord}, {Pathikulangara}, {Prabu}, {Remillard}, {Rogers},
+  {Roshi}, {Salah}, {Sault}, {Udaya}, {Srivani}, {Stevens}, {Subrahmanyan},
+  {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams},
+  \& {Wyithe}}]{bea13}
+{Beardsley}, A.~P., {Hazelton}, B.~J., {Morales}, M.~F., {et~al.} 2013, \mnras,
+  429, L5
 
-% \bibitem[{{Bernardi} {et~al.}(2009){Bernardi}, {de Bruyn}, {Brentjens},
-%   {Ciardi}, {Harker}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
-%   {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber09}
-% {Bernardi}, G., {de Bruyn}, A.~G., {Brentjens}, M.~A., {et~al.} 2009, \aap,
-%   500, 965
+\bibitem[{{Bernardi} {et~al.}(2009){Bernardi}, {de Bruyn}, {Brentjens},
+  {Ciardi}, {Harker}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
+  {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber09}
+{Bernardi}, G., {de Bruyn}, A.~G., {Brentjens}, M.~A., {et~al.} 2009, \aap,
+  500, 965
 
-% \bibitem[{{Bernardi} {et~al.}(2010){Bernardi}, {de Bruyn}, {Harker},
-%   {Brentjens}, {Ciardi}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
-%   {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber10}
-% {Bernardi}, G., {de Bruyn}, A.~G., {Harker}, G., {et~al.} 2010, \aap, 522, A67
+\bibitem[{{Bernardi} {et~al.}(2010){Bernardi}, {de Bruyn}, {Harker},
+  {Brentjens}, {Ciardi}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
+  {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber10}
+{Bernardi}, G., {de Bruyn}, A.~G., {Harker}, G., {et~al.} 2010, \aap, 522, A67
 
-% \bibitem[{{Bowman} {et~al.}(2006){Bowman}, {Morales}, \& {Hewitt}}]{bow06}
-% {Bowman}, J.~D., {Morales}, M.~F., \& {Hewitt}, J.~N. 2006, \apj, 638, 20
+\bibitem[{{Bowman} {et~al.}(2006){Bowman}, {Morales}, \& {Hewitt}}]{bow06}
+{Bowman}, J.~D., {Morales}, M.~F., \& {Hewitt}, J.~N. 2006, \apj, 638, 20
 
-% \bibitem[{{Bowman} {et~al.}(2009){Bowman}, {Morales}, \& {Hewitt}}]{bow09}
-% ---. 2009, \apj, 695, 183
+\bibitem[{{Bowman} {et~al.}(2009){Bowman}, {Morales}, \& {Hewitt}}]{bow09}
+---. 2009, \apj, 695, 183
 
-% \bibitem[{{Bowman} {et~al.}(2013){Bowman}, {Cairns}, {Kaplan}, {Murphy},
-%   {Oberoi}, {Staveley-Smith}, {Arcus}, {Barnes}, {Bernardi}, {Briggs}, {Brown},
-%   {Bunton}, {Burgasser}, {Cappallo}, {Chatterjee}, {Corey}, {Coster},
-%   {Deshpande}, {deSouza}, {Emrich}, {Erickson}, {Goeke}, {Gaensler},
-%   {Greenhill}, {Harvey-Smith}, {Hazelton}, {Herne}, {Hewitt},
-%   {Johnston-Hollitt}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale},
-%   {Lynch}, {Matthews}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Ord},
-%   {Pathikulangara}, {Prabu}, {Remillard}, {Robishaw}, {Rogers}, {Roshi},
-%   {Salah}, {Sault}, {Shankar}, {Srivani}, {Stevens}, {Subrahmanyan}, {Tingay},
-%   {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams}, \&
-%   {Wyithe}}]{bow13}
-% {Bowman}, J.~D., {Cairns}, I., {Kaplan}, D.~L., {et~al.} 2013, \pasa, 30, 31
+\bibitem[{{Bowman} {et~al.}(2013){Bowman}, {Cairns}, {Kaplan}, {Murphy},
+  {Oberoi}, {Staveley-Smith}, {Arcus}, {Barnes}, {Bernardi}, {Briggs}, {Brown},
+  {Bunton}, {Burgasser}, {Cappallo}, {Chatterjee}, {Corey}, {Coster},
+  {Deshpande}, {deSouza}, {Emrich}, {Erickson}, {Goeke}, {Gaensler},
+  {Greenhill}, {Harvey-Smith}, {Hazelton}, {Herne}, {Hewitt},
+  {Johnston-Hollitt}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale},
+  {Lynch}, {Matthews}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Ord},
+  {Pathikulangara}, {Prabu}, {Remillard}, {Robishaw}, {Rogers}, {Roshi},
+  {Salah}, {Sault}, {Shankar}, {Srivani}, {Stevens}, {Subrahmanyan}, {Tingay},
+  {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams}, \&
+  {Wyithe}}]{bow13}
+{Bowman}, J.~D., {Cairns}, I., {Kaplan}, D.~L., {et~al.} 2013, \pasa, 30, 31
 
-% \bibitem[{{Datta} {et~al.}(2010){Datta}, {Bowman}, \& {Carilli}}]{dat10}
-% {Datta}, A., {Bowman}, J.~D., \& {Carilli}, C.~L. 2010, \apj, 724, 526
+\bibitem[{{Datta} {et~al.}(2010){Datta}, {Bowman}, \& {Carilli}}]{dat10}
+{Datta}, A., {Bowman}, J.~D., \& {Carilli}, C.~L. 2010, \apj, 724, 526
 
-% \bibitem[{{Di Matteo} {et~al.}(2004){Di Matteo}, {Ciardi}, \&
-%   {Miniati}}]{dim04}
-% {Di Matteo}, T., {Ciardi}, B., \& {Miniati}, F. 2004, \mnras, 355, 1053
+\bibitem[{{Di Matteo} {et~al.}(2004){Di Matteo}, {Ciardi}, \&
+  {Miniati}}]{dim04}
+{Di Matteo}, T., {Ciardi}, B., \& {Miniati}, F. 2004, \mnras, 355, 1053
 
-% \bibitem[{{Di Matteo} {et~al.}(2002){Di Matteo}, {Perna}, {Abel}, \&
-%   {Rees}}]{dim02}
-% {Di Matteo}, T., {Perna}, R., {Abel}, T., \& {Rees}, M.~J. 2002, \apj, 564, 576
+\bibitem[{{Di Matteo} {et~al.}(2002){Di Matteo}, {Perna}, {Abel}, \&
+  {Rees}}]{dim02}
+{Di Matteo}, T., {Perna}, R., {Abel}, T., \& {Rees}, M.~J. 2002, \apj, 564, 576
 
-% \bibitem[{Dillon {et~al.}(2013)Dillon, Liu, \& Tegmark}]{dil13}
-% Dillon, J.~S., Liu, A., \& Tegmark, M. 2013, Phys. Rev. D, 87, 043005
+\bibitem[{Dillon {et~al.}(2013)Dillon, Liu, \& Tegmark}]{dil13}
+Dillon, J.~S., Liu, A., \& Tegmark, M. 2013, Phys. Rev. D, 87, 043005
 
-% \bibitem[{{Dillon} {et~al.}(2014){Dillon}, {Liu}, {Williams}, {Hewitt},
-%   {Tegmark}, {Morgan}, {Levine}, {Morales}, {Tingay}, {Bernardi}, {Bowman},
-%   {Briggs}, {Cappallo}, {Emrich}, {Mitchell}, {Oberoi}, {Prabu}, {Wayth}, \&
-%   {Webster}}]{dil14}
-% {Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002
+\bibitem[{{Dillon} {et~al.}(2014){Dillon}, {Liu}, {Williams}, {Hewitt},
+  {Tegmark}, {Morgan}, {Levine}, {Morales}, {Tingay}, {Bernardi}, {Bowman},
+  {Briggs}, {Cappallo}, {Emrich}, {Mitchell}, {Oberoi}, {Prabu}, {Wayth}, \&
+  {Webster}}]{dil14}
+{Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002
 
-% \bibitem[{{Furlanetto} \& {Briggs}(2004)}]{fur04}
-% {Furlanetto}, S.~R., \& {Briggs}, F.~H. 2004, \nar, 48, 1039
+\bibitem[{{Furlanetto} \& {Briggs}(2004)}]{fur04}
+{Furlanetto}, S.~R., \& {Briggs}, F.~H. 2004, \nar, 48, 1039
 
-% \bibitem[{{Furlanetto} {et~al.}(2006){Furlanetto}, {Oh}, \& {Briggs}}]{fur06}
-% {Furlanetto}, S.~R., {Oh}, S.~P., \& {Briggs}, F.~H. 2006, \physrep, 433, 181
+\bibitem[{{Furlanetto} {et~al.}(2006){Furlanetto}, {Oh}, \& {Briggs}}]{fur06}
+{Furlanetto}, S.~R., {Oh}, S.~P., \& {Briggs}, F.~H. 2006, \physrep, 433, 181
 
-% \bibitem[{{Ghosh} {et~al.}(2012){Ghosh}, {Prasad}, {Bharadwaj}, {Ali}, \&
-%   {Chengalur}}]{gho12}
-% {Ghosh}, A., {Prasad}, J., {Bharadwaj}, S., {Ali}, S.~S., \& {Chengalur}, J.~N.
-%   2012, \mnras, 426, 3295
+\bibitem[{{Ghosh} {et~al.}(2012){Ghosh}, {Prasad}, {Bharadwaj}, {Ali}, \&
+  {Chengalur}}]{gho12}
+{Ghosh}, A., {Prasad}, J., {Bharadwaj}, S., {Ali}, S.~S., \& {Chengalur}, J.~N.
+  2012, \mnras, 426, 3295
 
-% \bibitem[{{Gleser} {et~al.}(2008){Gleser}, {Nusser}, \& {Benson}}]{gle08}
-% {Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383
+\bibitem[{{Gleser} {et~al.}(2008){Gleser}, {Nusser}, \& {Benson}}]{gle08}
+{Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383
 
-% \bibitem[{{Hurley-Walker} {et~al.}(2014){Hurley-Walker}, {Morgan}, {Wayth},
-%   {Hancock}, {Bell}, {Bernardi}, {Bhat}, {Briggs}, {Deshpande}, {Ewall-Wice},
-%   {Feng}, {Hazelton}, {Hindson}, {Jacobs}, {Kaplan}, {Kudryavtseva}, {Lenc},
-%   {McKinley}, {Mitchell}, {Pindor}, {Procopio}, {Oberoi}, {Offringa}, {Ord},
-%   {Riding}, {Bowman}, {Cappallo}, {Corey}, {Emrich}, {Gaensler}, {Goeke},
-%   {Greenhill}, {Hewitt}, {Johnston-Hollitt}, {Kasper}, {Kratzenberg},
-%   {Lonsdale}, {Lynch}, {McWhirter}, {Morales}, {Morgan}, {Prabu}, {Rogers},
-%   {Roshi}, {Shankar}, {Srivani}, {Subrahmanyan}, {Tingay}, {Waterson},
-%   {Webster}, {Whitney}, {Williams}, \& {Williams}}]{hur14}
-% {Hurley-Walker}, N., {Morgan}, J., {Wayth}, R.~B., {et~al.} 2014, \pasa, 31, 45
+\bibitem[{{Hurley-Walker} {et~al.}(2014){Hurley-Walker}, {Morgan}, {Wayth},
+  {Hancock}, {Bell}, {Bernardi}, {Bhat}, {Briggs}, {Deshpande}, {Ewall-Wice},
+  {Feng}, {Hazelton}, {Hindson}, {Jacobs}, {Kaplan}, {Kudryavtseva}, {Lenc},
+  {McKinley}, {Mitchell}, {Pindor}, {Procopio}, {Oberoi}, {Offringa}, {Ord},
+  {Riding}, {Bowman}, {Cappallo}, {Corey}, {Emrich}, {Gaensler}, {Goeke},
+  {Greenhill}, {Hewitt}, {Johnston-Hollitt}, {Kasper}, {Kratzenberg},
+  {Lonsdale}, {Lynch}, {McWhirter}, {Morales}, {Morgan}, {Prabu}, {Rogers},
+  {Roshi}, {Shankar}, {Srivani}, {Subrahmanyan}, {Tingay}, {Waterson},
+  {Webster}, {Whitney}, {Williams}, \& {Williams}}]{hur14}
+{Hurley-Walker}, N., {Morgan}, J., {Wayth}, R.~B., {et~al.} 2014, \pasa, 31, 45
 
-% \bibitem[{{Iliev} {et~al.}(2002){Iliev}, {Shapiro}, {Ferrara}, \&
-%   {Martel}}]{ili02}
-% {Iliev}, I.~T., {Shapiro}, P.~R., {Ferrara}, A., \& {Martel}, H. 2002, \apjl,
-%   572, L123
+\bibitem[{{Iliev} {et~al.}(2002){Iliev}, {Shapiro}, {Ferrara}, \&
+  {Martel}}]{ili02}
+{Iliev}, I.~T., {Shapiro}, P.~R., {Ferrara}, A., \& {Martel}, H. 2002, \apjl,
+  572, L123
 
-% \bibitem[{{Liu} {et~al.}(2014{\natexlab{a}}){Liu}, {Parsons}, \&
-%   {Trott}}]{liu14a}
-% {Liu}, A., {Parsons}, A.~R., \& {Trott}, C.~M. 2014{\natexlab{a}}, \prd, 90,
-%   023018
+\bibitem[{{Liu} {et~al.}(2014{\natexlab{a}}){Liu}, {Parsons}, \&
+  {Trott}}]{liu14a}
+{Liu}, A., {Parsons}, A.~R., \& {Trott}, C.~M. 2014{\natexlab{a}}, \prd, 90,
+  023018
 
-% \bibitem[{{Liu} {et~al.}(2014{\natexlab{b}}){Liu}, {Parsons}, \&
-%   {Trott}}]{liu14b}
-% ---. 2014{\natexlab{b}}, \prd, 90, 023019
+\bibitem[{{Liu} {et~al.}(2014{\natexlab{b}}){Liu}, {Parsons}, \&
+  {Trott}}]{liu14b}
+---. 2014{\natexlab{b}}, \prd, 90, 023019
 
-% \bibitem[{{Liu} \& {Tegmark}(2011)}]{liu11}
-% {Liu}, A., \& {Tegmark}, M. 2011, \prd, 83, 103006
+\bibitem[{{Liu} \& {Tegmark}(2011)}]{liu11}
+{Liu}, A., \& {Tegmark}, M. 2011, \prd, 83, 103006
 
-% \bibitem[{{Liu} {et~al.}(2009){Liu}, {Tegmark}, {Bowman}, {Hewitt}, \&
-%   {Zaldarriaga}}]{liu09}
-% {Liu}, A., {Tegmark}, M., {Bowman}, J., {Hewitt}, J., \& {Zaldarriaga}, M.
-%   2009, \mnras, 398, 401
+\bibitem[{{Liu} {et~al.}(2009){Liu}, {Tegmark}, {Bowman}, {Hewitt}, \&
+  {Zaldarriaga}}]{liu09}
+{Liu}, A., {Tegmark}, M., {Bowman}, J., {Hewitt}, J., \& {Zaldarriaga}, M.
+  2009, \mnras, 398, 401
 
-% \bibitem[{{Lonsdale} {et~al.}(2009){Lonsdale}, {Cappallo}, {Morales}, {Briggs},
-%   {Benkevitch}, {Bowman}, {Bunton}, {Burns}, {Corey}, {Desouza}, {Doeleman},
-%   {Derome}, {Deshpande}, {Gopala}, {Greenhill}, {Herne}, {Hewitt}, {Kamini},
-%   {Kasper}, {Kincaid}, {Kocz}, {Kowald}, {Kratzenberg}, {Kumar}, {Lynch},
-%   {Madhavi}, {Matejek}, {Mitchell}, {Morgan}, {Oberoi}, {Ord},
-%   {Pathikulangara}, {Prabu}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Shankar},
-%   {Srivani}, {Stevens}, {Tingay}, {Vaccarella}, {Waterson}, {Wayth}, {Webster},
-%   {Whitney}, {Williams}, \& {Williams}}]{lon09}
-% {Lonsdale}, C.~J., {Cappallo}, R.~J., {Morales}, M.~F., {et~al.} 2009, IEEE
-%   Proceedings, 97, 1497
+\bibitem[{{Lonsdale} {et~al.}(2009){Lonsdale}, {Cappallo}, {Morales}, {Briggs},
+  {Benkevitch}, {Bowman}, {Bunton}, {Burns}, {Corey}, {Desouza}, {Doeleman},
+  {Derome}, {Deshpande}, {Gopala}, {Greenhill}, {Herne}, {Hewitt}, {Kamini},
+  {Kasper}, {Kincaid}, {Kocz}, {Kowald}, {Kratzenberg}, {Kumar}, {Lynch},
+  {Madhavi}, {Matejek}, {Mitchell}, {Morgan}, {Oberoi}, {Ord},
+  {Pathikulangara}, {Prabu}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Shankar},
+  {Srivani}, {Stevens}, {Tingay}, {Vaccarella}, {Waterson}, {Wayth}, {Webster},
+  {Whitney}, {Williams}, \& {Williams}}]{lon09}
+{Lonsdale}, C.~J., {Cappallo}, R.~J., {Morales}, M.~F., {et~al.} 2009, IEEE
+  Proceedings, 97, 1497
 
-% \bibitem[{{Madau} {et~al.}(1997){Madau}, {Meiksin}, \& {Rees}}]{mad97}
-% {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 1997, \apj, 475, 429
+\bibitem[{{Madau} {et~al.}(1997){Madau}, {Meiksin}, \& {Rees}}]{mad97}
+{Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 1997, \apj, 475, 429
 
-% \bibitem[{{McQuinn} {et~al.}(2006){McQuinn}, {Zahn}, {Zaldarriaga},
-%   {Hernquist}, \& {Furlanetto}}]{mcq06}
-% {McQuinn}, M., {Zahn}, O., {Zaldarriaga}, M., {Hernquist}, L., \& {Furlanetto},
-%   S.~R. 2006, \apj, 653, 815
+\bibitem[{{McQuinn} {et~al.}(2006){McQuinn}, {Zahn}, {Zaldarriaga},
+  {Hernquist}, \& {Furlanetto}}]{mcq06}
+{McQuinn}, M., {Zahn}, O., {Zaldarriaga}, M., {Hernquist}, L., \& {Furlanetto},
+  S.~R. 2006, \apj, 653, 815
 
-% \bibitem[{{Morales} {et~al.}(2006){Morales}, {Bowman}, \& {Hewitt}}]{mor06}
-% {Morales}, M.~F., {Bowman}, J.~D., \& {Hewitt}, J.~N. 2006, \apj, 648, 767
+\bibitem[{{Morales} {et~al.}(2006){Morales}, {Bowman}, \& {Hewitt}}]{mor06}
+{Morales}, M.~F., {Bowman}, J.~D., \& {Hewitt}, J.~N. 2006, \apj, 648, 767
 
-% \bibitem[{{Morales} {et~al.}(2012){Morales}, {Hazelton}, {Sullivan}, \&
-%   {Beardsley}}]{mor12}
-% {Morales}, M.~F., {Hazelton}, B., {Sullivan}, I., \& {Beardsley}, A. 2012,
-%   \apj, 752, 137
+\bibitem[{{Morales} {et~al.}(2012){Morales}, {Hazelton}, {Sullivan}, \&
+  {Beardsley}}]{mor12}
+{Morales}, M.~F., {Hazelton}, B., {Sullivan}, I., \& {Beardsley}, A. 2012,
+  \apj, 752, 137
 
-% \bibitem[{{Morales} \& {Hewitt}(2004)}]{mor04}
-% {Morales}, M.~F., \& {Hewitt}, J. 2004, \apj, 615, 7
+\bibitem[{{Morales} \& {Hewitt}(2004)}]{mor04}
+{Morales}, M.~F., \& {Hewitt}, J. 2004, \apj, 615, 7
 
-% \bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
-%   {Jacobs}, \& {Aguirre}}]{par12a}
-% {Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J.
-%   2012{\natexlab{a}}, \apj, 753, 81
+\bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
+  {Jacobs}, \& {Aguirre}}]{par12a}
+{Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J.
+  2012{\natexlab{a}}, \apj, 753, 81
 
-% \bibitem[{{Parsons} {et~al.}(2012{\natexlab{b}}){Parsons}, {Pober}, {Aguirre},
-%   {Carilli}, {Jacobs}, \& {Moore}}]{par12b}
-% {Parsons}, A.~R., {Pober}, J.~C., {Aguirre}, J.~E., {et~al.}
-%   2012{\natexlab{b}}, \apj, 756, 165
+\bibitem[{{Parsons} {et~al.}(2012{\natexlab{b}}){Parsons}, {Pober}, {Aguirre},
+  {Carilli}, {Jacobs}, \& {Moore}}]{par12b}
+{Parsons}, A.~R., {Pober}, J.~C., {Aguirre}, J.~E., {et~al.}
+  2012{\natexlab{b}}, \apj, 756, 165
 
-% \bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
-%   {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
-%   {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{par10}
-% {Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
-%   1468
+\bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
+  {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
+  {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{par10}
+{Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
+  1468
 
-% \bibitem[{{Pober} {et~al.}(2013){Pober}, {Parsons}, {Aguirre}, {Ali},
-%   {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
-%   {MacMahon}, {Manley}, {Moore}, {Stefan}, \& {Walbrugh}}]{pob13}
-% {Pober}, J.~C., {Parsons}, A.~R., {Aguirre}, J.~E., {et~al.} 2013, \apjl, 768,
-%   L36
+\bibitem[{{Pober} {et~al.}(2013){Pober}, {Parsons}, {Aguirre}, {Ali},
+  {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
+  {MacMahon}, {Manley}, {Moore}, {Stefan}, \& {Walbrugh}}]{pob13}
+{Pober}, J.~C., {Parsons}, A.~R., {Aguirre}, J.~E., {et~al.} 2013, \apjl, 768,
+  L36
 
-% \bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
-%   {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
-%   {Parsons}, {Tegmark}, \& {Werthimer}}]{pob14}
-% {Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66
+\bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
+  {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
+  {Parsons}, {Tegmark}, \& {Werthimer}}]{pob14}
+{Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66
 
-% \bibitem[{{Santos} {et~al.}(2005){Santos}, {Cooray}, \& {Knox}}]{san05}
-% {Santos}, M.~G., {Cooray}, A., \& {Knox}, L. 2005, \apj, 625, 575
+\bibitem[{{Santos} {et~al.}(2005){Santos}, {Cooray}, \& {Knox}}]{san05}
+{Santos}, M.~G., {Cooray}, A., \& {Knox}, L. 2005, \apj, 625, 575
 
-% \bibitem[{{Scott} \& {Rees}(1990)}]{sco90}
-% {Scott}, D., \& {Rees}, M.~J. 1990, \mnras, 247, 510
+\bibitem[{{Scott} \& {Rees}(1990)}]{sco90}
+{Scott}, D., \& {Rees}, M.~J. 1990, \mnras, 247, 510
 
-% \bibitem[{{Sunyaev} \& {Zeldovich}(1972)}]{sun72}
-% {Sunyaev}, R.~A., \& {Zeldovich}, Y.~B. 1972, \aap, 20, 189
+\bibitem[{{Sunyaev} \& {Zeldovich}(1972)}]{sun72}
+{Sunyaev}, R.~A., \& {Zeldovich}, Y.~B. 1972, \aap, 20, 189
 
-% \bibitem[{{Thompson} {et~al.}(2001){Thompson}, {Moran}, \& {Swenson}}]{tho01}
-% {Thompson}, A.~R., {Moran}, J.~M., \& {Swenson}, Jr., G.~W. 2001,
-%   {Interferometry and Synthesis in Radio Astronomy, 2nd Edition} (Wiley)
+\bibitem[{{Thompson} {et~al.}(2001){Thompson}, {Moran}, \& {Swenson}}]{tho01}
+{Thompson}, A.~R., {Moran}, J.~M., \& {Swenson}, Jr., G.~W. 2001,
+  {Interferometry and Synthesis in Radio Astronomy, 2nd Edition} (Wiley)
 
-% \bibitem[{{Thyagarajan} {et~al.}(2013){Thyagarajan}, {Udaya Shankar},
-%   {Subrahmanyan}, {Arcus}, {Bernardi}, {Bowman}, {Briggs}, {Bunton},
-%   {Cappallo}, {Corey}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
-%   {Hazelton}, {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper},
-%   {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter},
-%   {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Pathikulangara},
-%   {Remillard}, {Rogers}, {Anish Roshi}, {Salah}, {Sault}, {Srivani}, {Stevens},
-%   {Thiagaraj}, {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams},
-%   {Williams}, \& {Wyithe}}]{thy13}
-% {Thyagarajan}, N., {Udaya Shankar}, N., {Subrahmanyan}, R., {et~al.} 2013,
-%   \apj, 776, 6
+\bibitem[{{Thyagarajan} {et~al.}(2013){Thyagarajan}, {Udaya Shankar},
+  {Subrahmanyan}, {Arcus}, {Bernardi}, {Bowman}, {Briggs}, {Bunton},
+  {Cappallo}, {Corey}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
+  {Hazelton}, {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper},
+  {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter},
+  {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Pathikulangara},
+  {Remillard}, {Rogers}, {Anish Roshi}, {Salah}, {Sault}, {Srivani}, {Stevens},
+  {Thiagaraj}, {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams},
+  {Williams}, \& {Wyithe}}]{thy13}
+{Thyagarajan}, N., {Udaya Shankar}, N., {Subrahmanyan}, R., {et~al.} 2013,
+  \apj, 776, 6
 
-% \bibitem[{{Thyagarajan} {et~al.}(2015){Thyagarajan}, {Jacobs}, {Bowman},
-%   {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll}, {Corey},
-%   {de Oliveira-Costa}, {Dillon}, {Emrich}, {Ewall-Wice}, {Feng}, {Goeke},
-%   {Greenhill}, {Hazelton}, {Hewitt}, {Hurley-Walker}, {Johnston-Hollitt},
-%   {Kaplan}, {Kasper}, {Kim}, {Kittiwisit}, {Kratzenberg}, {Lenc}, {Line},
-%   {Loeb}, {Lonsdale}, {Lynch}, {McKinley}, {McWhirter}, {Mitchell}, {Morales},
-%   {Morgan}, {Neben}, {Oberoi}, {Offringa}, {Ord}, {Paul}, {Pindor}, {Pober},
-%   {Prabu}, {Procopio}, {Riding}, {Rogers}, {Roshi}, {Udaya Shankar}, {Sethi},
-%   {Srivani}, {Subrahmanyan}, {Sullivan}, {Tegmark}, {Tingay}, {Trott},
-%   {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams}, {Williams}, {Wu}, \&
-%   {Wyithe}}]{thy15}
-% {Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.} 2015, ArXiv
-%   e-prints, arXiv:1502.07596
+\bibitem[{{Thyagarajan} {et~al.}(2015){Thyagarajan}, {Jacobs}, {Bowman},
+  {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll}, {Corey},
+  {de Oliveira-Costa}, {Dillon}, {Emrich}, {Ewall-Wice}, {Feng}, {Goeke},
+  {Greenhill}, {Hazelton}, {Hewitt}, {Hurley-Walker}, {Johnston-Hollitt},
+  {Kaplan}, {Kasper}, {Kim}, {Kittiwisit}, {Kratzenberg}, {Lenc}, {Line},
+  {Loeb}, {Lonsdale}, {Lynch}, {McKinley}, {McWhirter}, {Mitchell}, {Morales},
+  {Morgan}, {Neben}, {Oberoi}, {Offringa}, {Ord}, {Paul}, {Pindor}, {Pober},
+  {Prabu}, {Procopio}, {Riding}, {Rogers}, {Roshi}, {Udaya Shankar}, {Sethi},
+  {Srivani}, {Subrahmanyan}, {Sullivan}, {Tegmark}, {Tingay}, {Trott},
+  {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams}, {Williams}, {Wu}, \&
+  {Wyithe}}]{thy15}
+{Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.} 2015, ArXiv
+  e-prints, arXiv:1502.07596
 
-% \bibitem[{{Tingay} {et~al.}(2013){Tingay}, {Goeke}, {Bowman}, {Emrich}, {Ord},
-%   {Mitchell}, {Morales}, {Booler}, {Crosse}, {Wayth}, {Lonsdale}, {Tremblay},
-%   {Pallot}, {Colegate}, {Wicenec}, {Kudryavtseva}, {Arcus}, {Barnes},
-%   {Bernardi}, {Briggs}, {Burns}, {Bunton}, {Cappallo}, {Corey}, {Deshpande},
-%   {Desouza}, {Gaensler}, {Greenhill}, {Hall}, {Hazelton}, {Herne}, {Hewitt},
-%   {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg},
-%   {Lynch}, {Mckinley}, {Mcwhirter}, {Morgan}, {Oberoi}, {Pathikulangara},
-%   {Prabu}, {Remillard}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Udaya-Shankar},
-%   {Schlagenhaufer}, {Srivani}, {Stevens}, {Subrahmanyan}, {Waterson},
-%   {Webster}, {Whitney}, {Williams}, {Williams}, \& {Wyithe}}]{tin13}
-% {Tingay}, S.~J., {Goeke}, R., {Bowman}, J.~D., {et~al.} 2013, \pasa, 30, 7
+\bibitem[{{Tingay} {et~al.}(2013){Tingay}, {Goeke}, {Bowman}, {Emrich}, {Ord},
+  {Mitchell}, {Morales}, {Booler}, {Crosse}, {Wayth}, {Lonsdale}, {Tremblay},
+  {Pallot}, {Colegate}, {Wicenec}, {Kudryavtseva}, {Arcus}, {Barnes},
+  {Bernardi}, {Briggs}, {Burns}, {Bunton}, {Cappallo}, {Corey}, {Deshpande},
+  {Desouza}, {Gaensler}, {Greenhill}, {Hall}, {Hazelton}, {Herne}, {Hewitt},
+  {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg},
+  {Lynch}, {Mckinley}, {Mcwhirter}, {Morgan}, {Oberoi}, {Pathikulangara},
+  {Prabu}, {Remillard}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Udaya-Shankar},
+  {Schlagenhaufer}, {Srivani}, {Stevens}, {Subrahmanyan}, {Waterson},
+  {Webster}, {Whitney}, {Williams}, {Williams}, \& {Wyithe}}]{tin13}
+{Tingay}, S.~J., {Goeke}, R., {Bowman}, J.~D., {et~al.} 2013, \pasa, 30, 7
 
-% \bibitem[{{Tozzi} {et~al.}(2000){Tozzi}, {Madau}, {Meiksin}, \& {Rees}}]{toz00}
-% {Tozzi}, P., {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 2000, \apj, 528, 597
+\bibitem[{{Tozzi} {et~al.}(2000){Tozzi}, {Madau}, {Meiksin}, \& {Rees}}]{toz00}
+{Tozzi}, P., {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 2000, \apj, 528, 597
 
-% \bibitem[{{Trott} {et~al.}(2012){Trott}, {Wayth}, \& {Tingay}}]{tro12}
-% {Trott}, C.~M., {Wayth}, R.~B., \& {Tingay}, S.~J. 2012, \apj, 757, 101
+\bibitem[{{Trott} {et~al.}(2012){Trott}, {Wayth}, \& {Tingay}}]{tro12}
+{Trott}, C.~M., {Wayth}, R.~B., \& {Tingay}, S.~J. 2012, \apj, 757, 101
 
-% \bibitem[{{van Cittert}(1934)}]{van34}
-% {van Cittert}, P.~H. 1934, Physica, 1, 201
+\bibitem[{{van Cittert}(1934)}]{van34}
+{van Cittert}, P.~H. 1934, Physica, 1, 201
 
-% \bibitem[{{van Haarlem} {et~al.}(2013){van Haarlem}, {Wise}, {Gunst}, {Heald},
-%   {McKean}, {Hessels}, {de Bruyn}, {Nijboer}, {Swinbank}, {Fallows},
-%   {Brentjens}, {Nelles}, {Beck}, {Falcke}, {Fender}, {H{\"o}randel},
-%   {Koopmans}, {Mann}, {Miley}, {R{\"o}ttgering}, {Stappers}, {Wijers},
-%   {Zaroubi}, {van den Akker}, {Alexov}, {Anderson}, {Anderson}, {van Ardenne},
-%   {Arts}, {Asgekar}, {Avruch}, {Batejat}, {B{\"a}hren}, {Bell}, {Bell}, {van
-%   Bemmel}, {Bennema}, {Bentum}, {Bernardi}, {Best}, {B{\^i}rzan}, {Bonafede},
-%   {Boonstra}, {Braun}, {Bregman}, {Breitling}, {van de Brink}, {Broderick},
-%   {Broekema}, {Brouw}, {Br{\"u}ggen}, {Butcher}, {van Cappellen}, {Ciardi},
-%   {Coenen}, {Conway}, {Coolen}, {Corstanje}, {Damstra}, {Davies}, {Deller},
-%   {Dettmar}, {van Diepen}, {Dijkstra}, {Donker}, {Doorduin}, {Dromer}, {Drost},
-%   {van Duin}, {Eisl{\"o}ffel}, {van Enst}, {Ferrari}, {Frieswijk}, {Gankema},
-%   {Garrett}, {de Gasparin}, {Gerbers}, {de Geus}, {Grie{\ss}meier}, {Grit},
-%   {Gruppen}, {Hamaker}, {Hassall}, {Hoeft}, {Holties}, {Horneffer}, {van der
-%   Horst}, {van Houwelingen}, {Huijgen}, {Iacobelli}, {Intema}, {Jackson},
-%   {Jelic}, {de Jong}, {Kant}, {Karastergiou}, {Koers}, {Kollen}, {Kondratiev},
-%   {Kooistra}, {Koopman}, {Koster}, {Kuniyoshi}, {Kramer}, {Kuper},
-%   {Lambropoulos}, {Law}, {van Leeuwen}, {Lemaitre}, {Loose}, {Maat}, {Macario},
-%   {Markoff}, {Masters}, {McFadden}, {McKay-Bukowski}, {Meijering}, {Meulman},
-%   {Mevius}, {Millenaar}, {Miller-Jones}, {Mohan}, {Mol}, {Morawietz},
-%   {Morganti}, {Mulcahy}, {Mulder}, {Munk}, {Nieuwenhuis}, {van Nieuwpoort},
-%   {Noordam}, {Norden}, {Noutsos}, {Offringa}, {Olofsson}, {Omar}, {Orr{\'u}},
-%   {Overeem}, {Paas}, {Pandey-Pommier}, {Pandey}, {Pizzo}, {Polatidis},
-%   {Rafferty}, {Rawlings}, {Reich}, {de Reijer}, {Reitsma}, {Renting},
-%   {Riemers}, {Rol}, {Romein}, {Roosjen}, {Ruiter}, {Scaife}, {van der Schaaf},
-%   {Scheers}, {Schellart}, {Schoenmakers}, {Schoonderbeek}, {Serylak},
-%   {Shulevski}, {Sluman}, {Smirnov}, {Sobey}, {Spreeuw}, {Steinmetz}, {Sterks},
-%   {Stiepel}, {Stuurwold}, {Tagger}, {Tang}, {Tasse}, {Thomas}, {Thoudam},
-%   {Toribio}, {van der Tol}, {Usov}, {van Veelen}, {van der Veen}, {ter Veen},
-%   {Verbiest}, {Vermeulen}, {Vermaas}, {Vocks}, {Vogt}, {de Vos}, {van der Wal},
-%   {van Weeren}, {Weggemans}, {Weltevrede}, {White}, {Wijnholds}, {Wilhelmsson},
-%   {Wucknitz}, {Yatawatta}, {Zarka}, {Zensus}, \& {van Zwieten}}]{van13}
-% {van Haarlem}, M.~P., {Wise}, M.~W., {Gunst}, A.~W., {et~al.} 2013, \aap, 556,
-%   A2
+\bibitem[{{van Haarlem} {et~al.}(2013){van Haarlem}, {Wise}, {Gunst}, {Heald},
+  {McKean}, {Hessels}, {de Bruyn}, {Nijboer}, {Swinbank}, {Fallows},
+  {Brentjens}, {Nelles}, {Beck}, {Falcke}, {Fender}, {H{\"o}randel},
+  {Koopmans}, {Mann}, {Miley}, {R{\"o}ttgering}, {Stappers}, {Wijers},
+  {Zaroubi}, {van den Akker}, {Alexov}, {Anderson}, {Anderson}, {van Ardenne},
+  {Arts}, {Asgekar}, {Avruch}, {Batejat}, {B{\"a}hren}, {Bell}, {Bell}, {van
+  Bemmel}, {Bennema}, {Bentum}, {Bernardi}, {Best}, {B{\^i}rzan}, {Bonafede},
+  {Boonstra}, {Braun}, {Bregman}, {Breitling}, {van de Brink}, {Broderick},
+  {Broekema}, {Brouw}, {Br{\"u}ggen}, {Butcher}, {van Cappellen}, {Ciardi},
+  {Coenen}, {Conway}, {Coolen}, {Corstanje}, {Damstra}, {Davies}, {Deller},
+  {Dettmar}, {van Diepen}, {Dijkstra}, {Donker}, {Doorduin}, {Dromer}, {Drost},
+  {van Duin}, {Eisl{\"o}ffel}, {van Enst}, {Ferrari}, {Frieswijk}, {Gankema},
+  {Garrett}, {de Gasparin}, {Gerbers}, {de Geus}, {Grie{\ss}meier}, {Grit},
+  {Gruppen}, {Hamaker}, {Hassall}, {Hoeft}, {Holties}, {Horneffer}, {van der
+  Horst}, {van Houwelingen}, {Huijgen}, {Iacobelli}, {Intema}, {Jackson},
+  {Jelic}, {de Jong}, {Kant}, {Karastergiou}, {Koers}, {Kollen}, {Kondratiev},
+  {Kooistra}, {Koopman}, {Koster}, {Kuniyoshi}, {Kramer}, {Kuper},
+  {Lambropoulos}, {Law}, {van Leeuwen}, {Lemaitre}, {Loose}, {Maat}, {Macario},
+  {Markoff}, {Masters}, {McFadden}, {McKay-Bukowski}, {Meijering}, {Meulman},
+  {Mevius}, {Millenaar}, {Miller-Jones}, {Mohan}, {Mol}, {Morawietz},
+  {Morganti}, {Mulcahy}, {Mulder}, {Munk}, {Nieuwenhuis}, {van Nieuwpoort},
+  {Noordam}, {Norden}, {Noutsos}, {Offringa}, {Olofsson}, {Omar}, {Orr{\'u}},
+  {Overeem}, {Paas}, {Pandey-Pommier}, {Pandey}, {Pizzo}, {Polatidis},
+  {Rafferty}, {Rawlings}, {Reich}, {de Reijer}, {Reitsma}, {Renting},
+  {Riemers}, {Rol}, {Romein}, {Roosjen}, {Ruiter}, {Scaife}, {van der Schaaf},
+  {Scheers}, {Schellart}, {Schoenmakers}, {Schoonderbeek}, {Serylak},
+  {Shulevski}, {Sluman}, {Smirnov}, {Sobey}, {Spreeuw}, {Steinmetz}, {Sterks},
+  {Stiepel}, {Stuurwold}, {Tagger}, {Tang}, {Tasse}, {Thomas}, {Thoudam},
+  {Toribio}, {van der Tol}, {Usov}, {van Veelen}, {van der Veen}, {ter Veen},
+  {Verbiest}, {Vermeulen}, {Vermaas}, {Vocks}, {Vogt}, {de Vos}, {van der Wal},
+  {van Weeren}, {Weggemans}, {Weltevrede}, {White}, {Wijnholds}, {Wilhelmsson},
+  {Wucknitz}, {Yatawatta}, {Zarka}, {Zensus}, \& {van Zwieten}}]{van13}
+{van Haarlem}, M.~P., {Wise}, M.~W., {Gunst}, A.~W., {et~al.} 2013, \aap, 556,
+  A2
 
-% \bibitem[{{Wang} {et~al.}(2006){Wang}, {Tegmark}, {Santos}, \& {Knox}}]{wan06}
-% {Wang}, X., {Tegmark}, M., {Santos}, M.~G., \& {Knox}, L. 2006, \apj, 650, 529
+\bibitem[{{Wang} {et~al.}(2006){Wang}, {Tegmark}, {Santos}, \& {Knox}}]{wan06}
+{Wang}, X., {Tegmark}, M., {Santos}, M.~G., \& {Knox}, L. 2006, \apj, 650, 529
 
-% \bibitem[{{Zaldarriaga} {et~al.}(2004){Zaldarriaga}, {Furlanetto}, \&
-%   {Hernquist}}]{zal04}
-% {Zaldarriaga}, M., {Furlanetto}, S.~R., \& {Hernquist}, L. 2004, \apj, 608, 622
+\bibitem[{{Zaldarriaga} {et~al.}(2004){Zaldarriaga}, {Furlanetto}, \&
+  {Hernquist}}]{zal04}
+{Zaldarriaga}, M., {Furlanetto}, S.~R., \& {Hernquist}, L. 2004, \apj, 608, 622
 
-% \bibitem[{{Zernike}(1938)}]{zer38}
-% {Zernike}, F. 1938, Physica, 5, 785
+\bibitem[{{Zernike}(1938)}]{zer38}
+{Zernike}, F. 1938, Physica, 5, 785
 
-% \end{thebibliography}
+\end{thebibliography}
 

### 2015-05-08 ms.tex
Update reference Thyagarajan et al.(2015)
From 84ebc81:
============

In eor.bib,

(*) Update bibliography entry of Thyagarajan et al.(2015)

In ms.tex,

(*) Update bibliography entry of Thyagarajan et al.(2015)

@@
   {Wyithe}}]{thy15}
-{Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.} 2015, ArXiv
-  e-prints, arXiv:1502.07596
+{Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.} 2015, \apj, 804,
+  14
 

### 2015-05-21 ms.tex
Address ApJL referee comments
From 44209c8:
============

In ms.tex,

(*) Address ApJL referee comments
(*) Add new section "Impact on Instrument Design"

@@
 Thus it is a critical input to design and analysis choices of future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array.
-The simulation which predicted this feature was recently validated against Murchison Widefield Array data but this key element was at or below the noise level.
+The simulation in our recent paper which predicted this feature was validated against Murchison Widefield Array data but this key element was at or below the noise level.
 In this paper, we improve the Murchison Widefield Array data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, and provide the first confirmation of the prediction with a signal-noise ratio $>10$.
@@
 A careful design of antenna aperture can significantly mitigate this contamination.
-Optimal weighting of foreground contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
+Optimal weighting of foreground-contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
 Thus, knowledge of such detailed foreground signatures is key for design and analysis choices of future instruments such as HERA and SKA.
@@
 \S\ref{sec:results} describes the results and confirms the presence of the predicted wide-field effects.
+\S\ref{sec:impact} underscores their impact on aperture design.
 \S\ref{sec:summary} summarizes our findings.
@@
   \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \\
-  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
+  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c\,(1+z)^2}, 
 \end{align}
@@
 The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in Paper~I and references therein.
-In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings.
+{\it Off-zenith} data containing the Galactic center in Paper~I was useful in demonstrating the mapping between delay spectra and sky locations, establishing primary causes of foreground contamination, and devising a technique for mitigating foreground contamination.
+{\it Pitchfork} signatures which result from low-level ubiquitous diffuse emission are fainter.
+Since Galactic plane emission, even from directions far away from the primary field of view, can potentially swamp the fainter {\it pitchfork} signatures, zenith pointings which have a maximum avoidance of the Galactic plane are preferred for this study.
+
+To reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical instrument settings.
 Hence, we select a subset of MWA snapshots each of duration 112~seconds obtained over different nights which are aligned to within 72~seconds of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hours with the MWA tile beam pointed at zenith.
@@
 Two of these snapshots, which contained amplitude and phase artifacts for a significant duration across different baselines, are excluded from our analysis.
-
-The delay spectra of the rest of the snapshots were verified to be coherent in their amplitudes and phases. Results from this coherent averaging are discussed below.
+Results of this coherent averaging are discussed below.
 
@@
 
+In these observations, the Galactic center is just about to set in the west.
+Its signature on eastward baselines is seen in the modeled delay spectra (bottom panel) as a marginal brightening of the arm near the negative horizon limit for $|\boldsymbol{b}| < 125$~m, consistent with our findings in Paper~I.
+This spills over into higher delay modes resulting in the faint ($\lesssim 10^2$~K$^2$~$($Mpc$/h)^3$) vertical stripes at $|\boldsymbol{b}| < 50$~m.
+The corresponding vertical feature is identified in the averaged data as well.
+
 In order to show that low-level ubiquitous diffuse emission is a significant contributor to the {\it pitchfork} signature, contribution from any strong emission from near the Galactic center needs to be minimized.
-This is best illustrated with northward antenna spacings which map any residual emission from this region (even though the Galactic center has just set over the western horizon) to $\tau\simeq 0$ and thus reduce the impact on higher delay modes (Paper~I).
+This is best illustrated with northward antenna spacings which map any residual emission from this region to $\tau\simeq 0$ and thus reduce the impact on higher delay modes (Paper~I).
 Figure~\ref{fig:3-baseline-comparison-delay-spectra} shows the averaged delay power spectra on three selected baseline vectors oriented northward.
@@
 However, some differences in the amplitude scales are noted.
-We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in Paper~I.
-At present, these uncertainties prevent a more thorough quantitative comparison between the model and the data.
-Extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Wayth et al.
-submitted) to cover the entire hemisphere, and a detailed model of the instrument will improve the accuracy of our model.
+For instance, the emission near the positive horizon limit is higher in the data than in the model in both figures.
+We attribute such differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in Paper~I which limit a more thorough quantitative comparison between the model and the data.
+In fact, this lays further emphasis on the need for extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Wayth et al.
+submitted) to cover the entire hemisphere, and a detailed characterization of the power pattern over the entire hemisphere.
 
@@
 
+\section{Impact on Instrument Design}\label{sec:impact}
+
+Delay spectrum maps the geometric delays to positions of foreground objects on the sky.
+Thus the directional power pattern of the antenna has a direct impact on the delay spectrum.
+Since the contamination in the {\it EoR window} is strongly dependent on sources of emission close to the horizon, design of antenna apertures that suppress their sensitivity towards the horizon is important.
+
+We approached this issue in Paper~I via simulations of different antenna apertures, namely, a dipole, a phased array, and a dish.
+The relative foreground contamination in the {\it EoR window} was found to be roughly $10^4:10^2:1$ respectively.
+In addition, the foreground contamination inside the {\it foreground wedge} was found to be suppressed by a factor $10^4$ for a dish relative to an MWA-like phased array thus raising the possibility of accessing the EoR signal in $k$-modes inside the {\it foreground wedge}.
+
+The response of new instruments such as SKA and HERA to foreground contamination has to be investigated thoroughly.
+With the SKA at low frequencies, plans to deploy ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of 256 pseudo-randomly placed vertical log-periodic dipole antennas are being considered.
+The ``station beam'' will be obtained by a phased addition of the dipole responses.
+The typical horizon response of these beams is $\gtrsim$~30~dB lower than at zenith\footnote{SKA memo ``Station Response and Imaging Performance of LFAA: 100 MHz to 600 MHz'' by Razavi-Ghods et al.} but the randomness across different stations in the placement of dipoles is expected to reduce the response significantly further as pairs of station voltage beams are multiplied with each other.
+HERA will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA.
+Their precise beam responses and the resulting foreground contamination, especially near the horizon, will prove to be critical and timely inputs to their aperture designs which are in their final stages.
+
 \section{Summary}\label{sec:summary}
@@
 This has important implications for instrument design and data analysis of future instruments such as HERA and SKA.
-For instance, SKA plans to use ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of pseudo-randomly placed vertical log-periodic dipole arrays.
-The ``station beam'' will be obtained by a phased addition of the dipole responses.
-The typical horizon response of these station beams is $\gtrsim$~30~dB lower than at the zenith (private communication from R.~Wayth).
-HERA will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA.
-Details of both telescopes are being finalized.
 Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.

### 2015-05-26 ms.tex
Modify Title and Abstract
From 3349de2:
============

In ms.tex,

(*) Modify Abstract
(*) Modify Title

@@
 
-\shorttitle{MWA Observations of Wide-field Effects in EoR Power Spectra}
+\shorttitle{Observations of Wide-field Effects in EoR Power Spectra}
 \shortauthors{Thyagarajan et~al.}
@@
 
-\title{Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra
-using Murchison Widefield Array Observations}
+\title{Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra}
 
@@
 
-Here we confirm a recently predicted and previously unknown foreground signature in the 3D power spectra of high-redshift 21~cm measurements, wherein the interferometer is sensitive to large-scale structure on all baselines.
-This is due to the inherently chromatic nature of a wide-field instrument response and is characterized by enhanced power from foreground emission in Fourier modes adjacent to those considered to be most sensitive to the cosmological H~{\sc i} signal.
-Thus it is a critical input to design and analysis choices of future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array.
-The simulation in our recent paper which predicted this feature was validated against Murchison Widefield Array data but this key element was at or below the noise level.
-In this paper, we improve the Murchison Widefield Array data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, and provide the first confirmation of the prediction with a signal-noise ratio $>10$.
+We confirm the recently predicted ``pitchfork'' foreground signature in power spectra of high-redshift 21~cm measurements, wherein the interferometer is sensitive to large-scale structure on all baselines.
+This is due to the inherent response of a wide-field instrument and is characterized by enhanced power from foreground emission in Fourier modes adjacent to those considered to be most sensitive to the cosmological H~{\sc i} signal.
+In our recent paper, many signatures in the simulation which predicted this feature were validated against Murchison Widefield Array data but this key element was at or below the noise level.
+In this paper, we improve the data sensitivity through coherent averaging of 12 independent snapshots with identical instrument settings, and provide the first confirmation of the prediction with a signal-noise ratio $>10$.
+This wide-field effect can by mitigated by careful antenna design which suppresses sensitivity towards the horizon.
+With future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array, based on simple scaling relations, we estimate a suppression of $\gtrsim 40$~dB is required near the horizon for signal detection in cosmological H~{\sc i} modes in analyses that deploy the {\it foreground avoidance} technique.
 

### 2015-05-26 ms.tex
Modify usage of off-zenith pointing in Section 3
From b9b3559:
============

In ms.tex,

(*) Modify comment on usage of off-zenith pointing in Section 3

@@
 The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in Paper~I and references therein.
-{\it Off-zenith} data containing the Galactic center in Paper~I was useful in demonstrating the mapping between delay spectra and sky locations, establishing primary causes of foreground contamination, and devising a technique for mitigating foreground contamination.
+In that paper, we analyzed two observations -- an {\it off-zenith} pointing that included significant Galactic plane contributions and a {\it zenith} pointing in which the Galactic plane was significantly absent.
+The {\it off-zenith} snapshot was useful in demonstrating the mapping between delay spectra and sky locations, establishing primary causes of foreground contamination, and devising a technique for mitigating foreground contamination.
 {\it Pitchfork} signatures which result from low-level ubiquitous diffuse emission are fainter.

### 2015-05-26 ms.tex
Minor change to HERA info in Sections 5 and 6
From 38cd004:
============

In ms.tex,

(*) Minor change to HERA info in Sections 5 and 6

@@
 The typical horizon response of these beams is $\gtrsim$~30~dB lower than at zenith\footnote{SKA memo ``Station Response and Imaging Performance of LFAA: 100 MHz to 600 MHz'' by Razavi-Ghods et al.} but the randomness across different stations in the placement of dipoles is expected to reduce the response significantly further as pairs of station voltage beams are multiplied with each other.
-HERA will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA.
+HERA will be a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings.
+It will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA.
 Their precise beam responses and the resulting foreground contamination, especially near the horizon, will prove to be critical and timely inputs to their aperture designs which are in their final stages.
@@
 For future work, we plan to extend our analysis to HERA.
-It is a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings.
 Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint.

### 2015-05-28 ms.tex
Change "previous" and "earlier" study to Paper I
From acb28a1:
============

In ms.tex,

(*) Change "previous" and "earlier" study to Paper I
(*) Minor changes in Abstract

@@
 This wide-field effect can by mitigated by careful antenna design which suppresses sensitivity towards the horizon.
-With future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array, based on simple scaling relations, we estimate a suppression of $\gtrsim 40$~dB is required near the horizon for signal detection in cosmological H~{\sc i} modes in analyses that deploy the {\it foreground avoidance} technique.
+With future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array, based on simple scaling relations, we estimate a suppression of $\gtrsim 40$~dB is required near the horizon for signal detection in cosmological H~{\sc i} modes in analyses that employ {\it foreground avoidance} techniques.
 
@@
 
-In the single snapshot (top), similar to the one used in our earlier study, faint features associated with the {\it pitchfork} signature are visible near the horizon limits.
+In the single snapshot (top), similar to the one used in Paper~I, faint features associated with the {\it pitchfork} signature are visible near the horizon limits.
 But the high level of thermal fluctuations makes their significance marginal.
@@
 
-In our earlier study, we proposed a selective flagging of data on different baselines that can potentially mitigate foreground contamination by two orders of magnitude.
+In Paper~I, we proposed a selective flagging of data on different baselines that can potentially mitigate foreground contamination by two orders of magnitude.
 Following the confirmation presented here, efforts are underway to incorporate this proposed foreground mitigation technique into the MWA data analysis.
@@
 For future work, we plan to extend our analysis to HERA.
-Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint.
+Based on Paper~I, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint.
 One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.

### 2015-06-02 ms.tex
Modify Section 5
From f6de6ce:
============

In ms.tex,

(*) Modify Section 5 to emphasize the need for detailed study of
coupling between beam response near horizon and foreground
contamination

@@
 The delay spectrum for a baseline vector, $\boldsymbol{b}$, is \citep[][Paper~I]{par12a,par12b,thy13}: 
-\begin{align}
+\begin{align}\label{eqn:delay-spectrum}
   \widetilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
@@
 \begin{align} 
-  V_b(f) &= \iint\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,W_\textrm{i}(f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega \\
-         &= \iint\limits_\textrm{sky} \frac{A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)}{\sqrt{1-l^2-m^2}}\,W_\textrm{i}(f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif l\,\dif m,
+  V_b(f) &= \iint\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,W_\textrm{i}(f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega \label{eqn:vis1}\\
+         &= \iint\limits_\textrm{sky} \frac{A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)}{\sqrt{1-l^2-m^2}}\,W_\textrm{i}(f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif l\,\dif m, \label{eqn:vis2}
 \end{align}
@@
 Thus the directional power pattern of the antenna has a direct impact on the delay spectrum.
+In fact, from equations~\ref{eqn:delay-spectrum}, \ref{eqn:vis1} and \ref{eqn:delay-power-spectrum}, the delay power spectrum scales as the square of the directional power pattern of the antenna.
 Since the contamination in the {\it EoR window} is strongly dependent on sources of emission close to the horizon, design of antenna apertures that suppress their sensitivity towards the horizon is important.
@@
 We approached this issue in Paper~I via simulations of different antenna apertures, namely, a dipole, a phased array, and a dish.
-The relative foreground contamination in the {\it EoR window} was found to be roughly $10^4:10^2:1$ respectively.
+Among these, a dish provides the best quality as evaluated from a foreground contamination viewpoint.
+With new instruments such as HERA and SKA on the horizon, we extend this discussion to further emphasize the need to comprehensively study the effect of their antenna apertures on foreground contamination.
+
+% The relative foreground contamination in the {\it EoR window} was found to be roughly $10^4:10^2:1$ respectively.
 In addition, the foreground contamination inside the {\it foreground wedge} was found to be suppressed by a factor $10^4$ for a dish relative to an MWA-like phased array thus raising the possibility of accessing the EoR signal in $k$-modes inside the {\it foreground wedge}.
 
-The response of new instruments such as SKA and HERA to foreground contamination has to be investigated thoroughly.
-With the SKA at low frequencies, plans to deploy ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of 256 pseudo-randomly placed vertical log-periodic dipole antennas are being considered.
-The ``station beam'' will be obtained by a phased addition of the dipole responses.
-The typical horizon response of these beams is $\gtrsim$~30~dB lower than at zenith\footnote{SKA memo ``Station Response and Imaging Performance of LFAA: 100 MHz to 600 MHz'' by Razavi-Ghods et al.} but the randomness across different stations in the placement of dipoles is expected to reduce the response significantly further as pairs of station voltage beams are multiplied with each other.
-HERA will be a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings.
-It will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA.
-Their precise beam responses and the resulting foreground contamination, especially near the horizon, will prove to be critical and timely inputs to their aperture designs which are in their final stages.
+% The response of new instruments such as SKA and HERA to foreground contamination has to be investigated thoroughly.
+
+HERA will deploy 14~m dishes with 331 of them in a closely packed hexagonal array and another 21 as outliers.
+With the advantage of enormous redundancy and unprecedented sensitivity, it will address the following key questions -- what objects first lit up the Universe and reionized the neutral IGM?
+Over what redshift range did this occur?
+And how did the process proceed, leading to the large scale galaxy structure seen today?
+The fixed dishes will observe the sky drifting overhead.
+Based on simulations of uniformly illuminated circular disks, the response near the horizon is $\lesssim -40$~dB, $\gtrsim$~20~dB lower than that of the MWA.
+Tapering the reflectivity of the dish is being studied to further reduce this response.
+The responses of the actual dishes will be tested shortly.
+
+With the SKA at low frequencies, deploying ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of 256 pseudo-randomly placed vertical log-periodic dipole antennas is being considered\footnote{Documents at \url{https://www.skatelescope.org/key-documents/} on SKA re-baselining}$^,$\footnote{SKA memo ``Station Response and Imaging Performance of LFAA: 100 MHz to 600 MHz'' by Razavi-Ghods et al.}.
+The voltage beam of the station will be obtained by a phased addition of the dipole responses.
+Since the power pattern of a baseline consisting of two stations will be effectively a product of two voltage beams, it will tend to homogenize the fluctuations in the power patterns of individual stations.
+Even with unconstrained, and hence sub-optimal, realizations of these phased array stations, we estimate the typical horizon response of these beams to be $\gtrsim$~30--40~dB lower than at zenith, also $\sim 20$~dB lower than the MWA beam.
+Constrained optimization studies of antenna layouts in the stations are under active study and could yield even better responses.
+
+From these simple antenna aperture models, HERA and SKA should mitigate foreground contamination by $\gtrsim 40$~dB relative to the MWA.
+The precise beam responses and the resulting foreground contamination, especially near the horizon, will prove to be critical and timely inputs to the actual aperture designs of HERA dishes and SKA stations which are nearing their final stages.
 

### 2015-06-02 ms.tex
Modify Abstract
From bc89703:
============

In ms.tex,

(*) Modify Abstract

@@
 
-We confirm the recently predicted ``pitchfork'' foreground signature in power spectra of high-redshift 21~cm measurements, wherein the interferometer is sensitive to large-scale structure on all baselines.
+We confirm our recent prediction of the ``pitchfork'' foreground signature in power spectra of high-redshift 21~cm measurements, wherein the interferometer is sensitive to large-scale structure on all baselines.
 This is due to the inherent response of a wide-field instrument and is characterized by enhanced power from foreground emission in Fourier modes adjacent to those considered to be most sensitive to the cosmological H~{\sc i} signal.
-In our recent paper, many signatures in the simulation which predicted this feature were validated against Murchison Widefield Array data but this key element was at or below the noise level.
+In our recent paper, many signatures from the simulation which predicted this feature were validated against Murchison Widefield Array (MWA) data but this key element was at or below the noise level.
 In this paper, we improve the data sensitivity through coherent averaging of 12 independent snapshots with identical instrument settings, and provide the first confirmation of the prediction with a signal-noise ratio $>10$.
 This wide-field effect can by mitigated by careful antenna design which suppresses sensitivity towards the horizon.
-With future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array, based on simple scaling relations, we estimate a suppression of $\gtrsim 40$~dB is required near the horizon for signal detection in cosmological H~{\sc i} modes in analyses that employ {\it foreground avoidance} techniques.
+Simple models for antenna apertures proposed for future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array indicate they should suppress foreground contamination by $\sim 40$~dB relative to the MWA.
+However, detailed models are necessary to ensure the contamination stays below the expected cosmological signal.
 
@@
 
-We approached this issue in Paper~I via simulations of different antenna apertures, namely, a dipole, a phased array, and a dish.
+We approached this issue in Paper~I via simulations of different antenna apertures, namely, a dipole, a $4\times 4$ phased array, and a dish.
 Among these, a dish provides the best quality as evaluated from a foreground contamination viewpoint.
@@
 Even with unconstrained, and hence sub-optimal, realizations of these phased array stations, we estimate the typical horizon response of these beams to be $\gtrsim$~30--40~dB lower than at zenith, also $\sim 20$~dB lower than the MWA beam.
-Constrained optimization studies of antenna layouts in the stations are under active study and could yield even better responses.
+Constrained optimization studies of antenna layouts of stations are under active study and could yield even better responses.
 

### 2015-06-02 ms.tex
Make changes suggested by Judd, update references
From e734511:
============

In eor.bib,

(*) Add citation to Neben et al.(2015)
(*) Add citation to Wayth et al.(2015)

In ms.tex,

(*) Make changes suggested by Judd
(*) Make changes suggested by Danny
(*) Use updated contents of ms.bbl according to changes in eor.bib
above
(*) Emphasize increase in likelihood of signal detection in 3D k-space

@@
 This is due to the inherent response of a wide-field instrument and is characterized by enhanced power from foreground emission in Fourier modes adjacent to those considered to be most sensitive to the cosmological H~{\sc i} signal.
-In our recent paper, many signatures from the simulation which predicted this feature were validated against Murchison Widefield Array (MWA) data but this key element was at or below the noise level.
+In our recent paper, many signatures from the simulation which predicted this feature were validated against Murchison Widefield Array (MWA) data but this key {\it pitchfork} signature was close to the noise level.
 In this paper, we improve the data sensitivity through coherent averaging of 12 independent snapshots with identical instrument settings, and provide the first confirmation of the prediction with a signal-noise ratio $>10$.
-This wide-field effect can by mitigated by careful antenna design which suppresses sensitivity towards the horizon.
-Simple models for antenna apertures proposed for future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array indicate they should suppress foreground contamination by $\sim 40$~dB relative to the MWA.
-However, detailed models are necessary to ensure the contamination stays below the expected cosmological signal.
+This wide-field effect can by mitigated by careful antenna designs that suppress sensitivity near the horizon.
+Simple models for antenna apertures proposed for future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array indicate they should suppress foreground leakage from the {\it pitchfork} by $\sim 40$~dB relative to the MWA, and significantly increase the likelihood of cosmological signal detection in three-dimensional power spectrum.
 
@@
 
-Our recent study \citep[][hereafter referred to as Paper~I]{thy15} used all-sky foreground and instrument models for the first time in order to simulate actual EoR experiments more accurately than previous studies.
+Our recent study \citep[][hereafter referred to as Paper~I]{thy15} used instrument and foreground models, for the first time with full sky coverage, in order to simulate actual EoR experiments more accurately than previous studies.
 Surprisingly, we found that foreground emission outside the primary beam field of view caused the most significant contamination of Fourier modes considered most sensitive for detecting the cosmological H~{\sc i} signal in delay spectrum based analyses.
@@
 This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
-We confirm this key feature using deeper MWA data.
+In the following sections, we present an observational confirmation of this effect.
 
@@
 We attribute such differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in Paper~I which limit a more thorough quantitative comparison between the model and the data.
-In fact, this lays further emphasis on the need for extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Wayth et al.
-submitted) to cover the entire hemisphere, and a detailed characterization of the power pattern over the entire hemisphere.
+In fact, this lays further emphasis on the need for the following -- extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey \citep[GLEAM;][]{way15} to cover the entire hemisphere; and, a detailed characterization of the power pattern over the entire hemisphere comprehensively extending studies such as those in \citet{neb15}.
 
@@
 The fixed dishes will observe the sky drifting overhead.
-Based on simulations of uniformly illuminated circular disks, the response near the horizon is $\lesssim -40$~dB, $\gtrsim$~20~dB lower than that of the MWA.
+Based on simulations of uniformly illuminated circular disks, the response near the horizon is $\lesssim -40$~dB, which is over 20~dB lower than that of the MWA.
 Tapering the reflectivity of the dish is being studied to further reduce this response.
@@
 Since the power pattern of a baseline consisting of two stations will be effectively a product of two voltage beams, it will tend to homogenize the fluctuations in the power patterns of individual stations.
-Even with unconstrained, and hence sub-optimal, realizations of these phased array stations, we estimate the typical horizon response of these beams to be $\gtrsim$~30--40~dB lower than at zenith, also $\sim 20$~dB lower than the MWA beam.
-Constrained optimization studies of antenna layouts of stations are under active study and could yield even better responses.
+Even with unconstrained, and hence sub-optimal, realizations of these phased array stations, we estimate the typical horizon response of these beams to be $-30$~dB to $-40$~dB compared to zenith, yielding a response that is at least 10~dB better than the MWA.
+Constrained optimization of antenna layouts of stations is under active study and could yield even better responses.
 
-From these simple antenna aperture models, HERA and SKA should mitigate foreground contamination by $\gtrsim 40$~dB relative to the MWA.
-The precise beam responses and the resulting foreground contamination, especially near the horizon, will prove to be critical and timely inputs to the actual aperture designs of HERA dishes and SKA stations which are nearing their final stages.
+From these simple antenna aperture models, HERA and SKA should mitigate leakage from the {\it pitchfork} into the {\it EoR window} by $\sim 40$~dB relative to the MWA when expressed in units of delay power spectrum.
+This will significantly increase the likelihood of detecting the cosmological H~{\sc i} power spectrum in {\it voxels} in three-dimensional $k$-space.
+The precise beam responses and the resulting foreground leakage, especially from near the horizon, will prove to be critical and timely inputs to the actual aperture designs of HERA dishes and SKA stations which are nearing their final stages.
 
@@
 This has important implications for instrument design and data analysis of future instruments such as HERA and SKA.
+Careful aperture designs that suppress the response near the horizon will significantly enhance the likelihood of detecting the cosmological signal in three-dimensional power spectrum.
 Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.
@@
 For future work, we plan to extend our analysis to HERA.
-Based on Paper~I, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint.
+Based on Paper~I, a dish will have a much desirable Fourier response from a foreground contamination viewpoint.
 One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.
@@
 
+\bibitem[{{Neben} {et~al.}(2015){Neben}, {Bradley}, {Hewitt}, {Bernardi},
+  {Bowman}, {Briggs}, {Cappallo}, {Deshpande}, {Goeke}, {Greenhill},
+  {Hazelton}, {Johnston-Hollitt}, {Kaplan}, {Lonsdale}, {McWhirter},
+  {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Prabu}, {Udaya Shankar},
+  {Srivani}, {Subrahmanyan}, {Tingay}, {Wayth}, {Webster}, {Williams}, \&
+  {Williams}}]{neb15}
+{Neben}, A.~R., {Bradley}, R.~F., {Hewitt}, J.~N., {et~al.} 2015, ArXiv
+  e-prints, arXiv:1505.07114
+
 \bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
@@
 
+\bibitem[{{Wayth} {et~al.}(2015){Wayth}, {Lenc}, {Bell}, {Callingham},
+  {Dwarakanath}, {Franzen}, {For}, {Gaensler}, {Hancock}, {Hindson},
+  {Hurley-Walker}, {Jackson}, {Johnston-Hollitt}, {Kapinska}, {McKinley},
+  {Morgan}, {Offringa}, {Procopio}, {Staveley-Smith}, {Wu}, {Zheng}, {Trott},
+  {Bernardi}, {Bowman}, {Briggs}, {Cappallo}, {Corey}, {Deshpande}, {Emrich},
+  {Goeke}, {Greenhill}, {Hazelton}, {Kaplan}, {Kasper}, {Kratzenberg},
+  {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Oberoi},
+  {Ord}, {Prabu}, {Rogers}, {Roshi}, {Udaya Shankar}, {Srivani},
+  {Subrahmanyan}, {Tingay}, {Waterson}, {Webster}, {Whitney}, {Williams}, \&
+  {Williams}}]{way15}
+{Wayth}, R.~B., {Lenc}, E., {Bell}, M.~E., {et~al.} 2015, ArXiv e-prints,
+  arXiv:1505.06041
+
 \bibitem[{{Zaldarriaga} {et~al.}(2004){Zaldarriaga}, {Furlanetto}, \&

### 2015-06-04 ms.tex
Emphasize usefulness for power spectrum estimators
From 2fd11fe:
============

In eor.bib,

(*) Add reference to Dillon et al.(2015)

In ms.tex,

(*) Modify Abstract and Sections 5 and 6 to be specific about
implications for antenna design
(*) Add a paragraph to emphasize optimum power spectrum estimation
techniques must take the wide-field "pitchfork" into account
(*) Insert updated .bbl file contents in bibliography

@@
 This wide-field effect can by mitigated by careful antenna designs that suppress sensitivity near the horizon.
-Simple models for antenna apertures proposed for future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array indicate they should suppress foreground leakage from the {\it pitchfork} by $\sim 40$~dB relative to the MWA, and significantly increase the likelihood of cosmological signal detection in three-dimensional power spectrum.
+Simple models for antenna apertures proposed for future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array indicate they should suppress foreground leakage from the {\it pitchfork} by $\sim 40$~dB relative to the MWA, and significantly increase the likelihood of cosmological signal detection in these critical Fourier modes in the three-dimensional power spectrum.
 
@@
 However, the effects giving rise to this signature are generic to all wide-field measurements.
-Thus, the extremely high significance detection of foreground emission near the horizon limits is a robust confirmation of the predicted wide-field measurement phenomenon.
+Thus, the extremely high significance detection of foreground emission near the horizon limits is a robust confirmation of the predicted effects of wide-field measurements.
 
@@
 Since the power pattern of a baseline consisting of two stations will be effectively a product of two voltage beams, it will tend to homogenize the fluctuations in the power patterns of individual stations.
-Even with unconstrained, and hence sub-optimal, realizations of these phased array stations, we estimate the typical horizon response of these beams to be $-30$~dB to $-40$~dB compared to zenith, yielding a response that is at least 10~dB better than the MWA.
-Constrained optimization of antenna layouts of stations is under active study and could yield even better responses.
+Even with simple models of such phased array stations, we estimate the typical horizon response of these beams to be $-30$~dB to $-40$~dB compared to zenith, yielding a response that is at least 10~dB better than the MWA.
+Targeted optimization of antenna layouts of stations is under active study and could yield even better responses.
 
 From these simple antenna aperture models, HERA and SKA should mitigate leakage from the {\it pitchfork} into the {\it EoR window} by $\sim 40$~dB relative to the MWA when expressed in units of delay power spectrum.
-This will significantly increase the likelihood of detecting the cosmological H~{\sc i} power spectrum in {\it voxels} in three-dimensional $k$-space.
+This will significantly increase the likelihood of detecting the cosmological H~{\sc i} power spectrum in sensitive three-dimensional $k$-modes adjacent to the {\it pitchfork}.
 The precise beam responses and the resulting foreground leakage, especially from near the horizon, will prove to be critical and timely inputs to the actual aperture designs of HERA dishes and SKA stations which are nearing their final stages.
@@
 
-Using deeper MWA data, we have confirmed with high significance the earlier prediction that wide-field EoR measurements suffer significant foreground contamination from near the horizon.
+Using deeper MWA data, we have confirmed with high significance the earlier prediction of a characteristic {\it pitchfork} morphology wherein wide-field EoR measurements suffer from significant foreground contamination from near the horizon.
 This has important implications for instrument design and data analysis of future instruments such as HERA and SKA.
-Careful aperture designs that suppress the response near the horizon will significantly enhance the likelihood of detecting the cosmological signal in three-dimensional power spectrum.
+
+Careful aperture designs that suppress the response near the horizon, and hence also the leakage from the {\it pitchfork}, will significantly avoid contamination in $k$-modes considered critical for cosmological signal detection.
 Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.
+
+Foreground and instrument models serve as inputs for power spectrum estimation techniques \citep[for e.g.,][]{liu14a,liu14b,dil15}.
+Input models which ignore wide-field effects will provide over-valued weights in and around the {\it pitchfork} modes, and hence result in sub-optimal results.
+Thus, confirmation of the {\it pitchfork} effect has important implications for power spectrum estimation.
 
@@
 {Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002
+
+\bibitem[{{Dillon} {et~al.}(2015){Dillon}, {Neben}, {Hewitt}, {Tegmark},
+  {Barry}, {Beardsley}, {Bowman}, {Briggs}, {Carroll}, {de Oliveira-Costa},
+  {Ewall-Wice}, {Feng}, {Greenhill}, {Hazelton}, {Hernquist}, {Hurley-Walker},
+  {Jacobs}, {Kim}, {Kittiwisit}, {Lenc}, {Line}, {Loeb}, {McKinley},
+  {Mitchell}, {Morales}, {Offringa}, {Paul}, {Pindor}, {Pober}, {Procopio},
+  {Riding}, {Sethi}, {Udaya Shankar}, {Subrahmanyan}, {Sullivan},
+  {Thyagarajan}, {Tingay}, {Trott}, {Wayth}, {Webster}, {Wyithe}, {Bernardi},
+  {Cappallo}, {Deshpande}, {Johnston-Hollitt}, {Kaplan}, {Lonsdale},
+  {McWhirter}, {Morgan}, {Oberoi}, {Ord}, {Prabu}, {Srivani}, {Williams}, \&
+  {Williams}}]{dil15}
+{Dillon}, J.~S., {Neben}, A.~R., {Hewitt}, J.~N., {et~al.} 2015, ArXiv
+  e-prints, arXiv:1506.01026
 
@@
 \end{thebibliography}
-
 \end{document}

### 2015-06-05 ms.tex
Modify sentence on power spectrum estimation
From eea4f3e:
============

In ms.tex,

(*) Modify sentence on optimum power spectrum estimation in Section 6
Minor changes throughout
From 29fc971:
============

In ms.tex,

(*) Minor changes in Introduction
(*) Minor changes to Section 3
(*) Minor changes to Section 5

@@
 
-A careful design of antenna aperture can significantly mitigate this contamination.
-Optimal weighting of foreground-contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
-Thus, knowledge of such detailed foreground signatures is key for design and analysis choices of future instruments such as HERA and SKA.
+Careful antenna aperture design can significantly mitigate this contamination.
+Optimal weighting of contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
+Thus, detailed knowledge of foreground signatures is key for design and analysis choices of future instruments such as HERA and SKA.
 
@@
 To reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical instrument settings.
-Hence, we select a subset of MWA snapshots each of duration 112~seconds obtained over different nights which are aligned to within 72~seconds of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hours with the MWA tile beam pointed at zenith.
+Hence, we select a subset of MWA snapshots pointed at zenith each of duration 112~seconds obtained over different nights which are aligned to within 72~seconds of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hours.
 The database contains 14 snapshots satisfying these criteria.
@@
 
-We approached this issue in Paper~I via simulations of different antenna apertures, namely, a dipole, a $4\times 4$ phased array, and a dish.
+We approached this issue in Paper~I via simulations of different antenna apertures -- a dipole, a $4\times 4$ phased array, and a dish.
 Among these, a dish provides the best quality as evaluated from a foreground contamination viewpoint.
@@
 The voltage beam of the station will be obtained by a phased addition of the dipole responses.
-Since the power pattern of a baseline consisting of two stations will be effectively a product of two voltage beams, it will tend to homogenize the fluctuations in the power patterns of individual stations.
+Since the power pattern of a baseline consisting of two stations will be effectively a product of two voltage beams, it will homogenize the fluctuations in the power patterns of individual stations.
 Even with simple models of such phased array stations, we estimate the typical horizon response of these beams to be $-30$~dB to $-40$~dB compared to zenith, yielding a response that is at least 10~dB better than the MWA.
@@
 
-From these simple antenna aperture models, HERA and SKA should mitigate leakage from the {\it pitchfork} into the {\it EoR window} by $\sim 40$~dB relative to the MWA when expressed in units of delay power spectrum.
+From these simple antenna aperture models, HERA and SKA should mitigate leakage from the {\it pitchfork} into the {\it EoR window} by $\sim 40$~dB relative to the MWA when expressed in units of power spectrum.
 This will significantly increase the likelihood of detecting the cosmological H~{\sc i} power spectrum in sensitive three-dimensional $k$-modes adjacent to the {\it pitchfork}.
@@
 Input models which ignore wide-field effects will provide over-valued weights in and around the {\it pitchfork} modes, and hence result in sub-optimal results.
-Thus, confirmation of the {\it pitchfork} effect has important implications for power spectrum estimation.
+Thus, confirmation of the {\it pitchfork} effect has important implications for optimum power spectrum estimation.
 

### 2015-06-05 ms.tex
Update response to referee, minor changes to draft
From 7e21d9e:
============

In response_to_ApJL_referee_report_1.txt,

(*) Update overall and specific responses to the referee report

In ms.tex,

(*) Fix minor typo in Abstract
(*) Minor change in wording in Introduction
(*) Minor change in hyphenation in Section 4
(*) Minor change in wording in Section 4

@@
 In this paper, we improve the data sensitivity through coherent averaging of 12 independent snapshots with identical instrument settings, and provide the first confirmation of the prediction with a signal-noise ratio $>10$.
-This wide-field effect can by mitigated by careful antenna designs that suppress sensitivity near the horizon.
+This wide-field effect can be mitigated by careful antenna designs that suppress sensitivity near the horizon.
 Simple models for antenna apertures proposed for future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array indicate they should suppress foreground leakage from the {\it pitchfork} by $\sim 40$~dB relative to the MWA, and significantly increase the likelihood of cosmological signal detection in these critical Fourier modes in the three-dimensional power spectrum.
@@
 Surprisingly, we found that foreground emission outside the primary beam field of view caused the most significant contamination of Fourier modes considered most sensitive for detecting the cosmological H~{\sc i} signal in delay spectrum based analyses.
-This contamination is the result of the interplay between foreground emission, particularly diffuse Galactic emission, and the wide-field properties typical of EoR instruments.
+This is the result of the interplay between foreground emission, particularly diffuse Galactic emission, and the wide-field properties typical of EoR instruments.
 Our simulations predicted that delay spectra from the MWA and other experiments should exhibit a characteristic ``pitchfork'' appearance with local maxima near the horizon delay limits, in addition to at the primary lobe region.
@@
 The vertical dotted-dashed lines at $\tau = \pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz.
-The peaks close to the horizon delay limits are distinctly visible at $\sim 10$-1000~$\sigma$ levels.
+The peaks close to the horizon delay limits are distinctly visible at $\sim 10$--1000~$\sigma$ levels.
 Differences between model and data are primarily attributed to uncertainties in the foreground model and the MWA tile power pattern.
@@
 We focus on the prominent peaks in data near the horizon limits.
-Typically, the power near the negative horizon limit is seen with a signal-noise ratio $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000.
+Typically, the power near the negative horizon limit is seen with a signal-noise ratio $\sim$~10--100, while that around the positive horizon limit is $\sim$~100--1000.
 
@@
 However, the effects giving rise to this signature are generic to all wide-field measurements.
-Thus, the extremely high significance detection of foreground emission near the horizon limits is a robust confirmation of the predicted effects of wide-field measurements.
+Thus, the extremely high-significance detection of foreground emission near the horizon limits is a robust confirmation of the predicted effects of wide-field measurements.
 

### 2015-06-19 ms.tex
Remove some commented content from TeX file
From 818eb76:
============

In ms.tex,

(*) Remove some commented blocks
(*) Remove commented authors

@@
 P.~Carroll\UW,
-% B.~E.~Corey\Haystack, 
 A.~A.~Deshpande\RRI, 
@@
 Joshua~S.~Dillon\MIT,
-% D.~Emrich\Curtin,
-% B.~M.~Gaensler\USydney$^,$\CAASTRO, 
 A.~Ewall-Wice\MIT,
 L.~Feng\MIT,
-% R.~Goeke\MIT,
 L.~J.~Greenhill\CfA,
@@
 D.~L.~Kaplan\UWisc, 
-% J.~C.~Kasper\UMichigan$^,$\CfA, 
 Han-Seek~Kim\UMelbourne$^,$\CAASTRO,
 P.~Kittiwisit\ASU,
-% E.~Kratzenberg\Haystack, 
 E.~Lenc\USydney$^,$\CAASTRO,
@@
 C.~J.~Lonsdale\Haystack, 
-% M.~J.~Lynch\Curtin, 
 B.~McKinley\UMelbourne$^,$\CAASTRO,
@@
 J.~Riding\UMelbourne$^,$\CAASTRO,
-% A.~E.~E.~Rogers\Haystack, 
-% A.~Roshi\NRAO, 
 N.~Udaya~Shankar\RRI, 
@@
 C.~M.~Trott\Curtin$^,$\CAASTRO,
-% M.~Waterson\Curtin$^,$\ANU,
 R.~B.~Wayth\Curtin$^,$\CAASTRO, 
 R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
-% A.~R.~Whitney\Haystack, 
 A.~Williams\Curtin, 
 C.~L.~Williams\MIT,
-% C.~Wu\UWA,
 J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
@@
 \myemailtxt
-% \NRAOtxt
-% \UMichigantxt
-% \UWAtxt
-
-%% \email{t\_nithyanandan@rri.res.in}
 
@@
 With new instruments such as HERA and SKA on the horizon, we extend this discussion to further emphasize the need to comprehensively study the effect of their antenna apertures on foreground contamination.
-
-% The relative foreground contamination in the {\it EoR window} was found to be roughly $10^4:10^2:1$ respectively.
-In addition, the foreground contamination inside the {\it foreground wedge} was found to be suppressed by a factor $10^4$ for a dish relative to an MWA-like phased array thus raising the possibility of accessing the EoR signal in $k$-modes inside the {\it foreground wedge}.
-
-% The response of new instruments such as SKA and HERA to foreground contamination has to be investigated thoroughly.
 

### 2015-07-02 ms.tex
Make proof corrections
From 818eb76:
============

Add ApJL_proof_corrections.txt containing proof corrections to git

In ms.tex,

(*) Make proof corrections

@@
 
-We confirm our recent prediction of the ``pitchfork'' foreground signature in power spectra of high-redshift 21~cm measurements, wherein the interferometer is sensitive to large-scale structure on all baselines.
-This is due to the inherent response of a wide-field instrument and is characterized by enhanced power from foreground emission in Fourier modes adjacent to those considered to be most sensitive to the cosmological H~{\sc i} signal.
-In our recent paper, many signatures from the simulation which predicted this feature were validated against Murchison Widefield Array (MWA) data but this key {\it pitchfork} signature was close to the noise level.
-In this paper, we improve the data sensitivity through coherent averaging of 12 independent snapshots with identical instrument settings, and provide the first confirmation of the prediction with a signal-noise ratio $>10$.
+We confirm our recent prediction of the ``pitchfork'' foreground signature in power spectra of high-redshift 21~cm measurements where the interferometer is sensitive to large-scale structure on all baselines.
+This is due to the inherent response of a wide-field instrument and is characterized by enhanced power from foreground emission in Fourier modes adjacent to those considered to be the most sensitive to the cosmological H~{\sc i} signal.
+In our recent paper, many signatures from the simulation that predicted this feature were validated against Murchison Widefield Array (MWA) data, but this key {\it pitchfork} signature was close to the noise level.
+In this paper, we improve the data sensitivity through the coherent averaging of 12 independent snapshots with identical instrument settings and provide the first confirmation of the prediction with a signal-to-noise ratio $>10$.
 This wide-field effect can be mitigated by careful antenna designs that suppress sensitivity near the horizon.
-Simple models for antenna apertures proposed for future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array indicate they should suppress foreground leakage from the {\it pitchfork} by $\sim 40$~dB relative to the MWA, and significantly increase the likelihood of cosmological signal detection in these critical Fourier modes in the three-dimensional power spectrum.
+Simple models for antenna apertures that have been proposed for future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array indicate they should suppress foreground leakage from the {\it pitchfork} by $\sim 40$~dB relative to the MWA and significantly increase the likelihood of cosmological signal detection in these critical Fourier modes in the three-dimensional power spectrum.
 
@@
 The epoch of reionization (EoR) commenced following the formation of the first stars and galaxies.
-It is characterized by a period of non-linear growth of matter density perturbations and astrophysical evolution in the Universe's history.
-Detection of redshifted 21~cm radiation of H~{\sc i} from this epoch is one of the most promising probes of the evolution of large scale structure during this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
+It is characterized by a period of non-linear growth of matter density perturbations and astrophysical evolution in the universe's history.
+The detection of redshifted 21~cm radiation of H~{\sc i} from this epoch is one of the most promising probes of the evolution of large-scale structure during this epoch \citep{sun72,sco90,mad97,toz00,ili02}.
 
-Sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} are yet to become operational.
-In the meanwhile, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA), currently under development, will be much more advanced in its capability to detect and place definitive constraints on the reionization epoch relative to current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have only enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.
+Sensitive instruments such as the Square Kilometre Array (SKA), which will be capable of providing direct imaging of redshifted H~{\sc i}, are yet to become operational.
+In the meantime, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA), currently under development, will be much more advanced in its capability to detect and place definitive constraints on the reionization epoch relative to current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have only enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.
 
-The primary challenge to detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, which is $\sim 10^4$ stronger than the desired signal.
-However, the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08}.
-Thus, a detailed characterization of foreground emission has become essential \citep{ali08,bow09,liu09,ber09,ber10,dat10,liu11,gho12,mor12,par12b,tro12,pob13,dil13,dil14,liu14a,liu14b,thy13,thy15}.
+The primary challenge to the detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, which is $\sim 10^4$ stronger than the desired signal.
+However, the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,fur04,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
+Thus, a detailed characterization of foreground emission has become essential \citep{ali08,ber09,ber10,bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,dil13,dil14,pob13,thy13,thy15}.
 
 Our recent study \citep[][hereafter referred to as Paper~I]{thy15} used instrument and foreground models, for the first time with full sky coverage, in order to simulate actual EoR experiments more accurately than previous studies.
-Surprisingly, we found that foreground emission outside the primary beam field of view caused the most significant contamination of Fourier modes considered most sensitive for detecting the cosmological H~{\sc i} signal in delay spectrum based analyses.
+Surprisingly, we found that foreground emission outside the primary beam field of view caused the most significant contamination of the Fourier modes considered the most sensitive for detecting the cosmological H~{\sc i} signal in delay spectrum based analyses.
 This is the result of the interplay between foreground emission, particularly diffuse Galactic emission, and the wide-field properties typical of EoR instruments.
-Our simulations predicted that delay spectra from the MWA and other experiments should exhibit a characteristic ``pitchfork'' appearance with local maxima near the horizon delay limits, in addition to at the primary lobe region.
+Our simulations predicted that the delay spectra from the MWA and other experiments should exhibit a characteristic ``pitchfork'' appearance, with local maxima near the horizon delay limits, in addition to at the primary lobe region.
 
@@
 Optimal weighting of contaminated Fourier modes may be required to extract the signal with maximum sensitivity.
-Thus, detailed knowledge of foreground signatures is key for design and analysis choices of future instruments such as HERA and SKA.
+Thus, detailed knowledge of foreground signatures is key for the design and analysis choices of future instruments such as HERA and SKA.
 
-In Paper~I, we verified the general features of our simulations against MWA observations, but were unable to confirm the {\it pitchfork} prediction due to insufficient sensitivity in the small amount of data analyzed.
-Here, we use deeper MWA data to confirm with high significance the presence of key {\it pitchfork} characteristics of wide-field measurements predicted in the preceding study.
+In Paper~I, we verified the general features of our simulations against MWA observations, but were unable to confirm the {\it pitchfork} prediction due to an insufficient sensitivity in the small amount of data analyzed.
+Here, we use deeper MWA data to confirm with a high significance the presence of key {\it pitchfork} characteristics of wide-field measurements predicted in the preceding study.
 
-\S\ref{sec:wide-field} is an overview of the role of wide-field measurements in the delay spectral domain and the predicted {\it pitchfork} signature.
-\S\ref{sec:MWA} describes the analysis of MWA data used to improve the dynamic range of the delay spectra.
-\S\ref{sec:results} describes the results and confirms the presence of the predicted wide-field effects.
-\S\ref{sec:impact} underscores their impact on aperture design.
-\S\ref{sec:summary} summarizes our findings.
+Section~\ref{sec:wide-field} is an overview of the role of wide-field measurements in the delay spectral domain and the predicted {\it pitchfork} signature.
+Section~\ref{sec:MWA} describes the analysis of MWA data used to improve the dynamic range of the delay spectra.
+Section~\ref{sec:results} describes the results and confirms the presence of the predicted wide-field effects.
+Section~\ref{sec:impact} underscores their impact on aperture design.
+Section~\ref{sec:summary} summarizes our findings.
 
@@
 The steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits in wide-field measurements.
-This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
+This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening toward the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.
 In the following sections, we present an observational confirmation of this effect.
@@
 
-The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in Paper~I and references therein.
+The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in Paper~I and the references therein.
 In that paper, we analyzed two observations -- an {\it off-zenith} pointing that included significant Galactic plane contributions and a {\it zenith} pointing in which the Galactic plane was significantly absent.
-The {\it off-zenith} snapshot was useful in demonstrating the mapping between delay spectra and sky locations, establishing primary causes of foreground contamination, and devising a technique for mitigating foreground contamination.
-{\it Pitchfork} signatures which result from low-level ubiquitous diffuse emission are fainter.
-Since Galactic plane emission, even from directions far away from the primary field of view, can potentially swamp the fainter {\it pitchfork} signatures, zenith pointings which have a maximum avoidance of the Galactic plane are preferred for this study.
+The {\it off-zenith} snapshot was useful for demonstrating the mapping between delay spectra and sky locations, establishing primary causes of foreground contamination, and devising a technique for mitigating foreground contamination.
+{\it Pitchfork} signatures that result from low-level ubiquitous diffuse emission are fainter.
+Since Galactic plane emission, even from directions far away from the primary field of view, can potentially swamp the fainter {\it pitchfork} signatures, zenith pointings that have a maximum avoidance of the Galactic plane are preferred for this study.
 
 To reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical instrument settings.
-Hence, we select a subset of MWA snapshots pointed at zenith each of duration 112~seconds obtained over different nights which are aligned to within 72~seconds of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hours.
+Hence, we select a subset of MWA snapshots pointed at zenith, each with a duration of 112~s, obtained over different nights which are aligned to within 72~s of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hr.
 The database contains 14 snapshots satisfying these criteria.
 Two of these snapshots, which contained amplitude and phase artifacts for a significant duration across different baselines, are excluded from our analysis.
-Results of this coherent averaging are discussed below.
+The results of this coherent averaging are discussed below.
 
@@
 
-Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling with no thermal noise fluctuations shown for reference (bottom).
+Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle) and from modeling with no thermal noise fluctuations shown for reference (bottom).
 In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent.
@@
 Dynamic range in the delay power spectra of MWA data has increased by a factor $\sim 10$ after averaging (middle) relative to that in a single snapshot (top).
-Power near the horizon limits caused by wide-field effects are prominent.
-Faint horizontal features at $\tau\simeq\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz.
+Power near the horizon limits caused by wide-field effects is prominent.
+Faint horizontal features at $\tau\simeq\pm 0.78\,\mu$s are visible due to the effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz.
 \label{fig:delay-spectra}}
@@
 But the high level of thermal fluctuations makes their significance marginal.
-In contrast, the dynamic range in the averaged data (middle) is a factor $\gtrsim 10$ higher (in delay power spectrum) relative to that in a single snapshot, and is consistent with the improvement expected from averaging 12 independent snapshots.
+In contrast, the dynamic range in the averaged data (middle) is a factor $\gtrsim 10$ higher (in the delay power spectrum) relative to that in a single snapshot and is consistent with the improvement expected from averaging 12 independent snapshots.
 Hence, the foreground power near the horizon limits appears $\gtrsim 10$ times more prominent.
-Also, faint horizontal features, not seen in the single snapshot, appear at $\tau \simeq \pm 0.78\,\mu$s thus confirming the improvement in sensitivity.
+Also, faint horizontal features that are not seen in the single snapshot appear at $\tau \simeq \pm 0.78\,\mu$s thus confirming the improvement in sensitivity.
 We identify these faint features as the response of the MWA coarse band edges flagged periodically every 1.28~MHz.
@@
 Its signature on eastward baselines is seen in the modeled delay spectra (bottom panel) as a marginal brightening of the arm near the negative horizon limit for $|\boldsymbol{b}| < 125$~m, consistent with our findings in Paper~I.
-This spills over into higher delay modes resulting in the faint ($\lesssim 10^2$~K$^2$~$($Mpc$/h)^3$) vertical stripes at $|\boldsymbol{b}| < 50$~m.
+This spills over into higher delay modes, resulting in the faint ($\lesssim 10^2$~K$^2$~$($Mpc$/h)^3$) vertical stripes at $|\boldsymbol{b}| < 50$~m.
 The corresponding vertical feature is identified in the averaged data as well.
@@
 In order to show that low-level ubiquitous diffuse emission is a significant contributor to the {\it pitchfork} signature, contribution from any strong emission from near the Galactic center needs to be minimized.
-This is best illustrated with northward antenna spacings which map any residual emission from this region to $\tau\simeq 0$ and thus reduce the impact on higher delay modes (Paper~I).
+This is best illustrated with northward antenna spacings that map any residual emission from this region to $\tau\simeq 0$ and thus reduce the impact on higher delay modes (Paper~I).
 Figure~\ref{fig:3-baseline-comparison-delay-spectra} shows the averaged delay power spectra on three selected baseline vectors oriented northward.
-Data and noiseless models are shown in black and red respectively.
-The horizontal dotted black line denotes {\it rms} of thermal fluctuations estimated from data.
-The vertical dashed line denotes horizon delay limits, and the vertical dotted-dashed lines denote delays at which the responses to coarse band edge flagging are expected.
+Data and noiseless models are shown in black and red, respectively.
+The horizontal dotted black line denotes the {\it rms} of thermal fluctuations estimated from data.
+The vertical dashed line denotes horizon delay limits, and the vertical dotted--dashed lines denote delays at which the responses to coarse band edge flagging are expected.
 
@@
 \includegraphics[width=\linewidth]{f2.eps}
-\caption{Delay power spectra on three antenna spacings oriented northward, obtained by coherent averaging of 12 snapshots aligned in LST.
-The averaged data and models are shown in black and red respectively.
+\caption{Delay power spectra on three antenna spacings oriented northward, obtained by the coherent averaging of 12 snapshots aligned in LST.
+The averaged data and models are shown in black and red, respectively.
 The antenna spacings are 83.5~m ({\it top}), 104.2~m ({\it middle}), and 171~m ({\it bottom}).
@@
 The vertical dashed lines denote the horizon delay limits.
-The vertical dotted-dashed lines at $\tau = \pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz.
+The vertical dotted--dashed lines at $\tau = \pm 0.78\,\mu$s correspond to the grating responses of the periodic flagging of bandpass at intervals of 1.28~MHz.
 The peaks close to the horizon delay limits are distinctly visible at $\sim 10$--1000~$\sigma$ levels.
-Differences between model and data are primarily attributed to uncertainties in the foreground model and the MWA tile power pattern.
+Differences between the model and the data are primarily attributed to uncertainties in the foreground model and the MWA tile power pattern.
 \label{fig:3-baseline-comparison-delay-spectra}}
@@
 We focus on the prominent peaks in data near the horizon limits.
-Typically, the power near the negative horizon limit is seen with a signal-noise ratio $\sim$~10--100, while that around the positive horizon limit is $\sim$~100--1000.
+Typically, the power near the negative horizon limit is seen with a signal-to-noise ratio $\sim$~10--100, while that around the positive horizon limit is $\sim$~100--1000.
 
@@
 We attribute such differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in Paper~I which limit a more thorough quantitative comparison between the model and the data.
-In fact, this lays further emphasis on the need for the following -- extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey \citep[GLEAM;][]{way15} to cover the entire hemisphere; and, a detailed characterization of the power pattern over the entire hemisphere comprehensively extending studies such as those in \citet{neb15}.
+In fact, this lays further emphasis on the need for the following -- extending the footprint of surveys matching the frequency and angular resolution of observations such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey \citep[GLEAM;][]{way15} to cover the entire hemisphere, and a detailed characterization of the power pattern over the entire hemisphere comprehensively extending studies such as those in \citet{neb15}.
 
@@
 However, the effects giving rise to this signature are generic to all wide-field measurements.
-Thus, the extremely high-significance detection of foreground emission near the horizon limits is a robust confirmation of the predicted effects of wide-field measurements.
+Thus, the extremely high significance detection of foreground emission near the horizon limits is a robust confirmation of the predicted effects of wide-field measurements.
 
@@
 
-Delay spectrum maps the geometric delays to positions of foreground objects on the sky.
+The delay spectrum maps the geometric delays to positions of foreground objects on the sky.
 Thus the directional power pattern of the antenna has a direct impact on the delay spectrum.
-In fact, from equations~\ref{eqn:delay-spectrum}, \ref{eqn:vis1} and \ref{eqn:delay-power-spectrum}, the delay power spectrum scales as the square of the directional power pattern of the antenna.
-Since the contamination in the {\it EoR window} is strongly dependent on sources of emission close to the horizon, design of antenna apertures that suppress their sensitivity towards the horizon is important.
+In fact, from equations~\ref{eqn:delay-spectrum}, \ref{eqn:vis1}, and \ref{eqn:delay-power-spectrum}, the delay power spectrum scales as the square of the directional power pattern of the antenna.
+Since the contamination in the {\it EoR window} is strongly dependent on sources of emission close to the horizon, the design of antenna apertures that suppress their sensitivity toward the horizon is important.
 
 We approached this issue in Paper~I via simulations of different antenna apertures -- a dipole, a $4\times 4$ phased array, and a dish.
-Among these, a dish provides the best quality as evaluated from a foreground contamination viewpoint.
+Among these, a dish provides the best quality, as evaluated from a foreground contamination viewpoint.
 With new instruments such as HERA and SKA on the horizon, we extend this discussion to further emphasize the need to comprehensively study the effect of their antenna apertures on foreground contamination.
 
-HERA will deploy 14~m dishes with 331 of them in a closely packed hexagonal array and another 21 as outliers.
+HERA will deploy 14~m dishes, with 331 of them in a closely packed hexagonal array and another 21 as outliers.
 With the advantage of enormous redundancy and unprecedented sensitivity, it will address the following key questions -- what objects first lit up the Universe and reionized the neutral IGM?
 Over what redshift range did this occur?
-And how did the process proceed, leading to the large scale galaxy structure seen today?
+And how did the process proceed, leading to the large-scale galaxy structure seen today?
 The fixed dishes will observe the sky drifting overhead.
@@
 
-With the SKA at low frequencies, deploying ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of 256 pseudo-randomly placed vertical log-periodic dipole antennas is being considered\footnote{Documents at \url{https://www.skatelescope.org/key-documents/} on SKA re-baselining}$^,$\footnote{SKA memo ``Station Response and Imaging Performance of LFAA: 100 MHz to 600 MHz'' by Razavi-Ghods et al.}.
-The voltage beam of the station will be obtained by a phased addition of the dipole responses.
-Since the power pattern of a baseline consisting of two stations will be effectively a product of two voltage beams, it will homogenize the fluctuations in the power patterns of individual stations.
-Even with simple models of such phased array stations, we estimate the typical horizon response of these beams to be $-30$~dB to $-40$~dB compared to zenith, yielding a response that is at least 10~dB better than the MWA.
-Targeted optimization of antenna layouts of stations is under active study and could yield even better responses.
+With the SKA at low frequencies, deploying ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of 256 pseudo-randomly placed vertical log-periodic dipole antennas is being considered.\footnote{Documents at \url{https://www.skatelescope.org/key-documents/} on SKA re-baselining}$^,$\footnote{SKA memo ``Station Response and Imaging Performance of LFAA: 100 MHz to 600 MHz'' by Razavi-Ghods et al.} The voltage beam of the station will be obtained by a phased addition of the dipole responses.
+Since the power pattern of a baseline consisting of two stations will be effectively be a product of two voltage beams, it will homogenize the fluctuations in the power patterns of individual stations.
+Even with simple models of such phased array stations, we estimate the typical horizon response of these beams to be $-30$~dB to $-40$~dB compared to the zenith, yielding a response that is at least 10~dB better than the MWA.
+A targeted optimization of the antenna layouts of stations is under active study and could yield even better responses.
 
@@
 This will significantly increase the likelihood of detecting the cosmological H~{\sc i} power spectrum in sensitive three-dimensional $k$-modes adjacent to the {\it pitchfork}.
-The precise beam responses and the resulting foreground leakage, especially from near the horizon, will prove to be critical and timely inputs to the actual aperture designs of HERA dishes and SKA stations which are nearing their final stages.
+The precise beam responses and the resulting foreground leakage, especially from near the horizon, will prove to be critical and timely inputs to the actual aperture designs of HERA dishes and SKA stations, which are currently nearing their final stages.
 
@@
 
-Using deeper MWA data, we have confirmed with high significance the earlier prediction of a characteristic {\it pitchfork} morphology wherein wide-field EoR measurements suffer from significant foreground contamination from near the horizon.
-This has important implications for instrument design and data analysis of future instruments such as HERA and SKA.
+Using deeper MWA data, we have confirmed with a high significance the earlier prediction of a characteristic {\it pitchfork} morphology where wide-field EoR measurements suffer from significant foreground contamination from near the horizon.
+This has important implications for the instrument design and data analysis of future instruments such as HERA and SKA.
 
@@
 
-Foreground and instrument models serve as inputs for power spectrum estimation techniques \citep[for e.g.,][]{liu14a,liu14b,dil15}.
-Input models which ignore wide-field effects will provide over-valued weights in and around the {\it pitchfork} modes, and hence result in sub-optimal results.
+Foreground and instrument models serve as inputs for power spectrum estimation techniques \citep[see, e.g.,][]{liu14a,liu14b,dil15}.
+Input models that ignore wide-field effects will provide over-valued weights in and around the {\it pitchfork} modes, and hence result in sub-optimal results.
 Thus, confirmation of the {\it pitchfork} effect has important implications for optimum power spectrum estimation.
@@
 Based on Paper~I, a dish will have a much desirable Fourier response from a foreground contamination viewpoint.
-One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.
+One of our objectives is to forecast the per-baseline foreground contamination as a function of LST in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.
 
@@
 National Science Foundation (NSF) through award AST-1109257.
-DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-1401708.
-JCP is supported by an NSF Astronomy and Astrophysics Fellowship under award AST-1302774.
+D.C.J.
+is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-1401708.
+J.C.P.
+is supported by an NSF Astronomy and Astrophysics Fellowship under award AST-1302774.
 This work makes use of the Murchison Radio-astronomy Observatory, operated by CSIRO.
-We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site.
+We acknowledge the Wajarri Yamatji people as the traditional owners of the observatory site.
 Support for the MWA comes from the NSF (awards: AST-0457585, PHY-0835713, CAREER-0847753, and AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), the U.S.
